### 2018-08-23 doc/paper.tex
Basic skeleton of project.

\documentclass[letterpaper,10pt]{article}

\usepackage[margin=1in]{geometry}

\usepackage{amsthm,amssymb,amsmath}
%% https://tex.stackexchange.com/a/396829/32270
\allowdisplaybreaks
%% H/T: https://tex.stackexchange.com/a/71153/32270
\usepackage[nottoc,notlot,notlof]{tocbibind}

\usepackage[usenames, dvipsnames]{color}
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  urlcolor=blue,
  linkcolor=MidnightBlue,
  citecolor=ForestGreen,
  pdfinfo={
    CreationDate={D:20180822233421},
    ModDate={D:20180822233421},
  },
}

\usepackage{embedfile}
\embedfile{\jobname.tex}

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{High-order Solution Transfer between Curved Meshes}
\rhead{Danny Hermes}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\qed}{\(\blacksquare\)}

\begin{document}

\begin{abstract}
\noindent The problem of solution transfer between meshes arises frequently in
computational physics, e.g. in Lagrangian methods where remeshing
occurs. The interpolation process must be conservative, i.e. it
must conserve physical properties, such as mass. We extend previous
works --- which described the solution transfer process for straight sided
unstructured meshes --- by considering high-order isoparametric meshes
with curved elements. The implementation is highly reliant on accurate
computational geometry routines for evaluating points on and
intersecting B\'{e}zier curves and triangles.
\\ \\
\noindent \emph{Keywords}: Remapping, Curved Meshes, Lagrangian,
Solution Transfer, Numerical analysis
\end{abstract}

\tableofcontents

\section{Introduction}

I will definitely cite this: \cite{Jiao2004}.

\bibliography{paper}
\bibliographystyle{alpha}

\end{document}

### 2018-08-23 nox.py

@@ -1,0 +1,82 @@
+# Licensed under the Apache License, Version 2.0 (the "License");
+# you may not use this file except in compliance with the License.
+# You may obtain a copy of the License at
+#
+#     https://www.apache.org/licenses/LICENSE-2.0
+#
+# Unless required by applicable law or agreed to in writing, software
+# distributed under the License is distributed on an "AS IS" BASIS,
+# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+# See the License for the specific language governing permissions and
+# limitations under the License.
+
+"""This is a configuration file for running ``nox`` on this project.
+
+To determine the supported actions run ``nox --list-sessions`` from the
+project root.
+"""
+
+import os
+
+import nox
+import py.path
+
+
+NOX_DIR = os.path.abspath(os.path.dirname(__file__))
+SINGLE_INTERP = "python3.7"
+
+
+def get_path(*names):
+    return os.path.join(NOX_DIR, *names)
+
+
+class Remove(object):
+    def __init__(self, prefix, extensions):
+        self.prefix = prefix
+        self.extensions = extensions
+
+    def __call__(self):
+        for extension in self.extensions:
+            path = "{}.{}".format(self.prefix, extension)
+            os.remove(path)
+
+
+def build_tex_file(session, base, new_id, extensions=()):
+    # NOTE: This assumes that ``session.chdir(get_path('doc'))``
+    #       has been called.
+    modify_id = get_path("scripts", "modify_pdf_id.py")
+
+    session.run("pdflatex", base)
+    session.run("bibtex", base)
+    session.run("pdflatex", base)
+    session.run("bibtex", base)
+    session.run("pdflatex", base)
+    session.run("pdflatex", base)
+
+    path = get_path("doc", base)
+    remove = Remove(path, extensions)
+    session.run(remove)
+    session.run("python", modify_id, "--base", path, "--id", new_id)
+
+
+@nox.session
+def build_tex(session):
+    session.interpreter = SINGLE_INTERP
+
+    if py.path.local.sysfind("pdflatex") is None:
+        session.skip("`pdflatex` must be installed")
+
+    if py.path.local.sysfind("bibtex") is None:
+        session.skip("`bibtex` must be installed")
+
+    # No need to create a virtualenv.
+    session.virtualenv = False
+
+    session.chdir(get_path("doc"))
+
+    build_tex_file(
+        session,
[…]

### 2018-08-23 doc/paper.tex
Bring in the content from `introduction.tex`.

@@
 
-I will definitely cite this: \cite{Jiao2004}.
+The first part is a general-purpose tool for computational physics problems.
+The tool enables solution transfer across two curved meshes.
+Since the tool requires a significant amount of computational geometry, the
+second half focuses on computational geometry. In particular, it considers
+cases where the geometric methods used have seriously degraded accuracy due to
+ill-conditioning.
+
+In computational physics, the problem of solution transfer between meshes
+occurs in several applications. For example, by allowing the underyling
+computational domain to change during a simulation, computational
+effort can be focused dynamically to resolve sensitive features
+of a numerical solution. Mesh adaptivity (see, for example,
+\cite{Babuska1978, Peraire1987, Pain2001}), this in-flight change in the mesh,
+requires translating the numerical solution from the old mesh to the new,
+i.e. solution transfer. As another example, Lagrangian or particle-based
+methods treat each node in the mesh as a particle and so with each timestep the
+mesh travels \emph{with} the fluid (see, for example, \cite{Hirt1974}).
+However, over (typically limited) time the mesh
+becomes distorted and suffers a loss in element quality which causes
+catastrophic loss in the accuracy of computation. To overcome this, the
+domain must be remeshed or rezoned and the solution must be
+transferred (remapped) onto the new mesh configuration.
+
+When pointwise interpolation is used to transfer a solution, quantities with
+physical meaning (e.g. mass, concentration, energy) may not be conserved.
+To address this, there have been many explorations (for example,
+\cite{Jiao2004, Farrell2009, Farrell2011}) of
+\emph{conservative interpolation} (typically using Galerkin or
+\(L_2\)-minimizing methods). In this work, the author introduces a
+conservative interpolation method for solution transfer between high-order
+meshes. These high-order meshes are typically curved, but not necessarily
+all elements or at all timesteps.
+
+The existing work on solution transfer has considered straight sided meshes,
+which use shape functions that have degree \(p = 1\) to represent solutions
+on each element or so-called superparametric elements (i.e. a linear mesh
+with degree \(p > 1\) shape functions on a regular grid of points).
+However, both to allow for greater geometric flexibility
+and for high order of convergence, this work will consider the case
+of curved isoparametric\footnote{I.e. the degree of the discrete field on the
+mesh is same as the degree of the shape functions that determine the
+mesh.} meshes. Allowing curved geometries is useful since many practical
+problems involve geometries that change over time, such as flapping flight
+or fluid-structure interactions. In addition, high-order CFD methods
+(\cite{Wang2013}) have the ability to produce highly accurate solutions
+with low dissipation and low dispersion error.
+
+\subsection{Overview}
+
+This work is organized as follows. Section~\ref{sec:preliminaries}
+establishes common notation and reviews basic results relevant to the
+topics at hand. Section~\ref{sec:bezier-intersection} is an
+in-depth discussion of the computational geometry methods needed
+to implement to enable solution transfer. Section~\ref{sec:solution-transfer}
+describes the solution transfer process and gives results of some
+numerical experiments confirming the rate of convergence.
+
+\section{Preliminaries}\label{sec:preliminaries}
+
+Placeholder.
+
+\section{B\'{e}zier Intersection Problems}\label{sec:bezier-intersection}
+
+Placeholder.
+
+\section{Solution Transfer}\label{sec:solution-transfer}
+
+Placeholder.
 

### 2018-08-23 doc/paper.tex
Adding in content from `preliminaries.tex` in thesis.
I deleted some parts that were related to compensated
algorithms.

@@
 
-\usepackage{amsthm,amssymb,amsmath}
+\usepackage{amsthm,amssymb,amsmath,graphicx}
+\usepackage{bm}
 %% https://tex.stackexchange.com/a/396829/32270
@@
 
+%% H/T: https://tex.stackexchange.com/a/202047/32270
+%%      https://tex.stackexchange.com/a/32463/32270
+\usepackage[labelfont=bf]{caption}
+
 \renewcommand{\headrulewidth}{0pt}
 \renewcommand{\qed}{\(\blacksquare\)}
+\newcommand{\reals}{\mathbf{R}}
+\newcommand{\utri}{\mathcal{U}}
 
@@
 
-Placeholder.
+\subsection{General Notation}
+
+We'll refer to \(\reals\) for the reals, \(\utri\) represents
+the unit triangle (or unit simplex) in \(\reals^2\):
+\(\utri = \left\{(s, t) \mid 0 \leq s, t, s + t \leq 1\right\}\).
+When dealing with sequences with multiple indices, e.g.
+\(s_{m, n} = m + n\), we'll use bold symbols to represent
+a multi-index: \(\bm{i} = (m, n)\). We'll use \(\left|\bm{i}\right|\) to
+represent the sum of the components in a multi-index.
+The binomial coefficient
+\(\binom{n}{k}\) is equal to \(\frac{n!}{k! (n - k)!}\) and the trinomial
+coefficient \(\binom{n}{i, j, k}\) is equal to \(\frac{n!}{i! j! k!}\)
+(where \(i + j + k = n\)). The notation \(\delta_{ij}\) represents the
+Kronecker delta, a value which is \(1\) when \(i = j\) and \(0\)
+otherwise.
+
+\subsection{B\'{e}zier Curves}
+
+A \emph{B\'{e}zier curve} is a mapping from the unit interval
+that is determined by a set of control points
+\(\left\{\bm{p}_j\right\}_{j = 0}^n \subset \reals^d\).
+For a parameter \(s \in \left[0, 1\right]\), there is a corresponding
+point on the curve:
+\begin{equation}
+b(s) = \sum_{j = 0}^n \binom{n}{j} (1 - s)^{n - j} s^j \bm{p}_j \in
+  \reals^d.
+\end{equation}
+This is a combination of the control points weighted by
+each Bernstein basis function
+\(B_{j, n}(s) = \binom{n}{j} (1 - s)^{n - j} s^j\).
+Due to the binomial expansion
+\(1 = (s + (1 - s))^n = \sum_{j = 0}^n B_{j, n}(s)\),
+a Bernstein basis function is in
+\(\left[0, 1\right]\) when \(s\) is as well. Due to this fact, the
+curve must be contained in the convex hull of it's control points.
+
+\subsection{B\'{e}zier Triangles}
+
+A \emph{B\'{e}zier triangle} (\cite[Chapter~17]{Farin2001}) is a
+mapping from the unit triangle
+\(\utri\) and is determined by a control net
+\(\left\{\bm{p}_{i, j, k}\right\}_{i + j + k = n} \subset \reals^d\).
+A B\'{e}zier triangle is a particular kind of B\'{e}zier surface, i.e. one
+in which there are two cartesian or three barycentric input parameters.
+Often the term B\'{e}zier surface is used to refer to a tensor product or
+rectangular patch.
+For \((s, t) \in \utri\) we can define barycentric weights
+\(\lambda_1 = 1 - s - t, \lambda_2 = s, \lambda_3 = t\) so that
+\begin{equation}
+1 = \left(\lambda_1 + \lambda_2 + \lambda_3\right)^n =
+  \sum_{\substack{i + j + k = n \\ i, j, k \geq 0}} \binom{n}{i, j, k}
+  \lambda_1^i \lambda_2^j \lambda_3^k.
+\end{equation}
+Using this we can similarly define a (triangular) Bernstein basis
+\begin{equation}
+B_{i, j, k}(s, t) = \binom{n}{i, j, k} (1 - s - t)^i s^j t^k
+  = \binom{n}{i, j, k} \lambda_1^i \lambda_2^j \lambda_3^k
+\end{equation}
+that is in \(\left[0, 1\right]\) when \((s, t)\) is in \(\utri\).
+Using this, we define points on the B\'{e}zier triangle as a
+convex combination of the control net:
+\begin{equation}
+b(s, t) = \sum_{i + j + k = n} \binom{n}{i, j, k}
+  \lambda_1^i \lambda_2^j \lambda_3^k
+  \bm{p}_{i, j, k} \in \reals^d.
+\end{equation}
+
+\begin{figure}
+  \includegraphics{main_figure01.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Cubic B\'{e}zier triangle}
+  \label{fig:cubic-bezier-example}
+\end{figure}
+
+\noindent Rather than defining a B\'{e}zier triangle by the control net, it can
+also be uniquely determined by the image of a standard lattice of
+points in \(\utri\): \(b\left(j/n, k/n\right) = \bm{n}_{i, j, k}\);
+we'll refer to these as \emph{standard nodes}.
+Figure~\ref{fig:cubic-bezier-example} shows these standard nodes for
+a cubic triangle in \(\reals^2\). To see the correspondence,
+when \(p = 1\) the standard nodes \emph{are} the control net
+\begin{equation}
+b(s, t) = \lambda_1 \bm{n}_{1, 0, 0} +
+\lambda_2 \bm{n}_{0, 1, 0} + \lambda_3 \bm{n}_{0, 0, 1}
+\end{equation}
+and when \(p = 2\)
+\begin{multline}
+b(s, t) = \lambda_1\left(2 \lambda_1 - 1\right) \bm{n}_{2, 0, 0} +
+\lambda_2\left(2 \lambda_2 - 1\right) \bm{n}_{0, 2, 0} +
+\lambda_3\left(2 \lambda_3 - 1\right) \bm{n}_{0, 0, 2} + \\
+4 \lambda_1 \lambda_2 \bm{n}_{1, 1, 0} +
+4 \lambda_2 \lambda_3 \bm{n}_{0, 1, 1} +
+4 \lambda_3 \lambda_1 \bm{n}_{1, 0, 1}.
+\end{multline}
+However, it's worth noting that the transformation between
+the control net and the standard nodes has condition
+number that grows exponentially with \(n\) (see \cite{Farouki1991}, which
+is related but does not directly show this).
+This may make working with
+higher degree triangles prohibitively unstable.
+
+A \emph{valid} B\'{e}zier triangle is one which is
+diffeomorphic to \(\utri\), i.e. \(b(s, t)\) is bijective and has
+an everywhere invertible Jacobian. We must also have the orientation
+preserved, i.e. the Jacobian must have positive determinant. For example, in
+Figure~\ref{fig:inverted-element}, the image of \(\utri\) under
+the map \(b(s, t) = \left[\begin{array}{c c} (1 - s - t)^2 + s^2 & s^2 + t^2
+\end{array}\right]^T\) is not valid because the Jacobian is zero along
+the curve \(s^2 - st - t^2 - s + t = 0\) (the dashed line). Elements that
+are not valid are called \emph{inverted} because they have regions with
+``negative area''. For the example, the image \(b\left(\utri\right)\)
+leaves the boundary determined by the edge curves: \(b(r, 0)\),
+\(b(1 - r, r)\) and \(b(0, 1 - r)\) when \(r \in \left[0, 1\right]\).
+This region outside the boundary is traced twice, once with
+a positive Jacobian and once with a negative Jacobian.
+\begin{figure}
+  \includegraphics{inverted_element.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{The B\'{e}zier triangle given by \(b(s, t) = \left[
+    (1 - s - t)^2 + s^2 \; \; s^2 + t^2 \right]^T\) produces an
+    inverted element. It traces the same region twice, once with
+    a positive Jacobian (the middle column) and once with a negative
+    Jacobian (the right column).}
+  \label{fig:inverted-element}
+\end{figure}
+
+\subsection{Curved Elements}\label{sec:curved-elements}
+
+We define a curved mesh element \(\mathcal{T}\) of degree \(p\)
+to be a B\'{e}zier triangle in \(\reals^2\) of the same degree.
+We refer to the component functions of \(b(s, t)\) (the map that
+gives \(\mathcal{T} = b\left(\utri\right)\)) as \(x(s, t)\) and \(y(s, t)\).
+
+This fits a typical definition (\cite[Chapter~12]{FEM-ClaesJohnson})
+of a curved element, but gives a special meaning to the mapping from
+the reference triangle. Interpreting elements as B\'{e}zier triangles
+has been used for Lagrangian methods where
+mesh adaptivity is needed (e.g. \cite{CardozeMOP04}). Typically curved
+elements only have one curved side (\cite{McLeod1972}) since they are used
+to resolve geometric features of a boundary. See also
+\cite{Zlmal1973, Zlmal1974}.
+B\'{e}zier curves and triangles have a number of mathematical properties
+(e.g. the convex hull property) that lead to elegant geometric
+descriptions and algorithms.
+
+Note that a B\'{e}zier triangle can be
+determined from many different sources of data (for example the control net
+or the standard nodes). The choice of this data may be changed to suit the
+underlying physical problem without changing the actual mapping. Conversely,
+the data can be fixed (e.g. as the control net) to avoid costly basis
+conversion; once fixed, the equations of motion and other PDE terms can
+be recast relative to the new basis (for an example, see \cite{Persson2009},
+where the domain varies with time but the problem is reduced to
+solving a transformed conservation law in a fixed reference configuration).
+
+\subsection{Shape Functions}\label{subsec:shape-functions}
+
+When defining shape functions (i.e. a basis with geometric meaning) on a
+curved element there are (at least) two choices. When the degree of the
+shape functions is the same as the degree of the function being
+represented on the B\'{e}zier triangle,
+we say the element \(\mathcal{T}\) is \emph{isoparametric}.
+For the multi-index
+\(\bm{i} = (i, j , k)\), we define \(\bm{u}_{\bm{i}} =
+\left(j/n, k/n\right)\) and the corresponding standard node
+\(\bm{n}_{\bm{i}} = b\left(\bm{u}_{\bm{i}}\right)\).
+Given these points, two choices for shape functions present
+themselves:
+\begin{itemize}
+  \itemsep 0em
+  \item \emph{Pre-Image Basis}:
+    \(\phi_{\bm{j}}\left(\bm{n}_{\bm{i}}\right) =
+      \widehat{\phi}_{\bm{j}}\left(\bm{u}_{\bm{i}}\right) =
+      \widehat{\phi}_{\bm{j}}\left(b^{-1}\left(
+      \bm{n}_{\bm{i}}\right)\right)\)
+    where \(\widehat{\phi}_{\bm{j}}\) is a canonical basis function
+    on \(\utri\), i.e.
+    \(\widehat{\phi}_{\bm{j}}\) a degree \(p\) bivariate polynomial and
+    \(\widehat{\phi}_{\bm{j}}\left(\bm{u}_{\bm{i}}\right) =
+    \delta_{\bm{i} \bm{j}}\)
+  \item \emph{Global Coordinates Basis}:
+    \(\phi_{\bm{j}}\left(\bm{n}_{\bm{i}}\right) =
+    \delta_{\bm{i} \bm{j}}\), i.e. a canonical basis function
+    on the standard nodes \(\left\{\bm{n}_{\bm{i}}\right\}\).
+\end{itemize}
+
+\noindent For example, consider a quadratic B\'{e}zier triangle:
+\begin{gather}
+b(s, t) = \left[ \begin{array}{c c}
+    4 (s t + s + t) & 4 (s t + t + 1)
+  \end{array}\right]^T \\
+\Longrightarrow
+\left[ \begin{array}{c c c c c c}
+    \bm{n}_{2, 0, 0} &
+    \bm{n}_{1, 1, 0} &
+    \bm{n}_{0, 2, 0} &
+    \bm{n}_{1, 0, 1} &
+    \bm{n}_{0, 1, 1} &
+    \bm{n}_{0, 0, 2}
+  \end{array}\right] = \left[ \begin{array}{c c c c c c}
+    0 & 2 & 4 & 2 & 5 & 4 \\
+    4 & 4 & 4 & 6 & 7 & 8
+  \end{array}\right].
+\end{gather}
+In the \emph{Global Coordinates Basis}, we have
+\begin{equation}
+\phi^{G}_{0, 1, 1}(x, y) = \frac{(y - 4) (x - y + 4)}{6}.
+\end{equation}
+For the \emph{Pre-Image Basis}, we need the inverse
+and the canonical basis
+\begin{equation}
+b^{-1}(x, y) = \left[ \begin{array}{c c}
+    \frac{x - y + 4}{4} & \frac{y - 4}{x - y + 8}
+  \end{array}\right] \quad \text{and} \quad
+\widehat{\phi}_{0, 1, 1}(s, t) = 4 s t
+\end{equation}
+and together they give
+\begin{equation}
+\phi^{P}_{0, 1, 1}(x, y) = \frac{(y - 4) (x - y + 4)}{x - y + 8}.
+\end{equation}
+In general \(\phi_{\bm{j}}^P\) may not even be a rational bivariate
+function; due to composition with \(b^{-1}\) we can only guarantee that
+it is algebraic (i.e. it can be defined as the zero set of polynomials).
+
+\subsection{Curved Polygons}\label{subsec:curved-polygons}
+
+\begin{figure}
+  \includegraphics{main_figure26.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Intersection of B\'{e}zier triangles form a curved polygon.}
+  \label{fig:bezier-triangle-intersect}
+\end{figure}
+
+When intersecting two curved elements, the resulting surface(s) will
+be defined by the boundary, alternating between edges of each
+element.
+For example, in Figure~\ref{fig:bezier-triangle-intersect}, a
+``curved quadrilateral'' is formed when two B\'{e}zier triangles
+\(\mathcal{T}_0\) and \(\mathcal{T}_1\) are intersected.
+
+A \emph{curved polygon} is defined by a collection of B\'{e}zier curves
+in \(\reals^2\) that determine the boundary. In order to be
+a valid polygon, none of the boundary curves may cross, the
+ends of consecutive edge curves must meet and the curves must be right-hand
+oriented. For our example in
+Figure~\ref{fig:bezier-triangle-intersect}, the triangles
+have boundaries formed by three B\'{e}zier curves:
+\(\partial \mathcal{T}_0 = b_{0, 0} \cup b_{0, 1} \cup b_{0, 2}\) and
+\(\partial \mathcal{T}_1 = b_{1, 0} \cup b_{1, 1} \cup b_{1, 2}\).
+The intersection \(\mathcal{P}\) is defined by four boundary
+curves: \(\partial \mathcal{P} =
+C_1 \cup C_2 \cup C_3 \cup C_4\). Each boundary
+curve is itself a B\'{e}zier curve\footnote{A specialization of a
+B\'{e}zier curve \(b\left(\left[a_1, a_2\right]\right)\)
+is also a B\'{e}zier curve.}:
+\(C_1 = b_{0, 0}\left(\left[0, 1/8\right]\right)\),
+\(C_2 = b_{1, 2}\left(\left[7/8, 1\right]\right)\),
+\(C_3 = b_{1, 0}\left(\left[0, 1/7\right]\right)\) and
+\(C_4 = b_{0, 2}\left(\left[6/7, 1\right]\right)\).
+
+Though an intersection can be described in terms of the B\'{e}zier triangles,
+the structure of the control net will be lost. The region will not in general
+be able to be described by a mapping from a simple space like
+\(\utri\).
 

### 2018-08-23 doc/paper.tex
Adding in content from `bezier-intersection.tex` in thesis.

@@
 
-Placeholder.
+\subsection{Intersecting B\'{e}zier Curves}
+
+The problem of intersecting two B\'{e}zier curves is a core building
+block for intersecting two B\'{e}zier triangles in \(\reals^2\)
+Since a curve is an algebraic variety of dimension one,
+the intersections will either be a curve segment common to both curves (if
+they coincide) or a finite set of points (i.e. dimension zero).
+Many algorithms have been described in the literature, both
+geometric (\cite{Sederberg1986, Sederberg1990, Kim1998}) and
+algebraic (\cite{Manocha:CSD-92-698}).
+
+In the implementation for this work, the B\'{e}zier subdivision
+algorithm is used.
+In the case of a transversal intersection (i.e. one where the
+tangents to each curve are not parallel and both are non-zero),
+this algorithm performs very well. However, when curves are tangent,
+a large number of (false) candidate intersections are detected and
+convergence of Newton's method slows once in a neighborhood of an
+actual intersection. Non-transversal intersections
+have infinite condition number, but transversal intersections with
+very high condition number can also cause convergence problems.
+
+\begin{figure}
+  \includegraphics{bbox_check.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Bounding box intersection predicate. This is a cheap way to
+    conclude that two curves don't intersect, though it inherently is
+    susceptible to false positives.}
+  \label{fig:bounding-box-check}
+\end{figure}
+
+In the B\'{e}zier subdivision algorithm, we first check if the
+bounding boxes for the curves are disjoint
+(Figure~\ref{fig:bounding-box-check}).
+We use the bounding boxes
+rather than the convex hulls since they are easier to compute and
+the intersections of boxes are easier to check.
+If they are disjoint, the pair can be rejected. If not, each curve
+\(\mathcal{C} = b\left(\left[0, 1\right]\right)\) is split into two halves
+by splitting the unit interval: \(b\left(\left[0, \frac{1}{2}\right]\right)\)
+and \(b\left(\left[\frac{1}{2}, 1\right]\right)\)
+(Figure~\ref{fig:bezier-curve-subdivision}).
+
+\begin{figure}
+  \includegraphics{subdivide_curve.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{B\'{e}zier curve subdivision.}
+  \label{fig:bezier-curve-subdivision}
+\end{figure}
+
+\begin{figure}
+  \includegraphics{subdivision_process.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{B\'{e}zier subdivision algorithm.}
+  \label{fig:bezier-subdivision-process}
+\end{figure}
+
+As the subdivision continues,
+some pairs of curve segments may be kept around that won't lead to an
+intersection (Figure~\ref{fig:bezier-subdivision-process}).
+Once the curve segments are close to linear within a given tolerance
+(Figure~\ref{fig:bezier-subdivision-linearized}), the process
+terminates.
+
+\begin{figure}
+  \includegraphics{subdivision_linearized.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Subdividing until linear within tolerance.}
+  \label{fig:bezier-subdivision-linearized}
+\end{figure}
+
+Once both curve segments are linear (to tolerance), the intersection is
+approximated by intersecting the lines connecting the endpoints of each
+curve segment. This approximation is used as a starting point for Newton's
+method, to find a root of \(F(s, t) = b_0(s) - b_1(t)\). Since
+\(b_0(s), b_1(t) \in \reals^2\) we have Jacobian \(J =
+\left[ \begin{array}{c c} b_0'(s) & -b_1'(t) \end{array}\right]\).
+With these, Newton's method is
+\begin{equation}
+\left[ \begin{array}{c c} s_{n + 1} & t_{n + 1} \end{array}\right]^T =
+\left[ \begin{array}{c c} s_n & t_n \end{array}\right]^T -
+J_n^{-1} F_n.
+\end{equation}
+This also gives an indication why convergence issues occur at non-transveral
+intersections: they are exactly the intersections where the Jacobian is
+singular.
+
+\subsection{Intersecting B\'{e}zier Triangles}\label{subsec:intersect-bez-tri}
+
+The chief difficulty in intersecting two surfaces is intersecting their edges,
+which are B\'{e}zier curves.
+Though this is just a part of the overall algorithm, it proved to be the
+\emph{most difficult} to implement (\cite{Hermes2017}). So the first part
+of the algorithm is to find all points
+where the edges intersect (Figure~\ref{fig:edge-intersections}).
+
+\begin{figure}
+  \includegraphics{main_figure21.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Edge intersections during B\'{e}zier triangle intersection.}
+  \label{fig:edge-intersections}
+\end{figure}
+
+To determine the curve segments that bound the curved polygon region(s)
+(see Section~\ref{subsec:curved-polygons} for more about curved polygons) of
+intersection, we not only need to keep track
+of the coordinates of intersection, we also need to keep note of
+\emph{which} edges the intersection occurred on and the parameters along
+each curve.
+With this information, we can classify each point of intersection
+according to which of the two curves forms the boundary of the
+curved polygon (Figure~\ref{fig:intersection-classification}).
+Using the right-hand rule we can compare the tangent
+vectors on each curve to determine which one is on the interior.
+
+\begin{figure}
+  \includegraphics{main_figure22.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Classified intersections during B\'{e}zier triangle intersection.}
+  \label{fig:intersection-classification}
+\end{figure}
+
+This classification becomes more difficult when the curves
+are tangent at an intersection, when the intersection occurs at a corner
+of one of the surfaces or when two intersecting edges are coincident
+on the same algebraic curve (Figure~\ref{fig:intersection-difficulties}).
+
+\begin{figure}
+  \includegraphics{main_figure23.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{B\'{e}zier triangle intersection difficulties.}
+  \label{fig:intersection-difficulties}
+\end{figure}
+
+In the case of tangency, the intersection is non-transversal, hence has
+infinite condition number. In the case of coincident curves, there are
+infinitely many intersections (along the segment when the curves
+coincide) so the subdivision process breaks down.
+
+\subsubsection{Example}
+
+Consider two B\'{e}zier surfaces
+(Figure~\ref{fig:surface-surface-example})
+
+\begin{equation}
+b_0(s, t) =
+\left[ \begin{array}{c}
+    8 s \\ 8 t \end{array}\right] \qquad
+b_1(s, t) =
+\left[ \begin{array}{c}
+    2 (6 s + t - 1) \\
+    2 (8 s^2 + 8 s t - 8 s + 3 t + 2) \end{array}\right]
+\end{equation}
+\begin{figure}
+  \includegraphics{main_figure24.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Surface Intersection Example}
+  \label{fig:surface-surface-example}
+\end{figure}
+
+In the \emph{first step} we find all intersections of the
+edge curves
+\begin{multline}
+E_0(r) = \left[ \begin{array}{c} 8 r \\ 0 \end{array}\right],
+E_1(r) = \left[ \begin{array}{c} 8 (1 - r) \\ 8 r \end{array}\right],
+E_2(r) = \left[ \begin{array}{c} 0 \\ 8 (1 - r) \end{array}\right], \\
+E_3(r) = \left[ \begin{array}{c} 2 (6 r - 1) \\ 4 (2 r - 1)^2
+  \end{array}\right],
+E_4(r) = \left[ \begin{array}{c} 10 (1 - r) \\ 2 (3 r + 2) \end{array}\right],
+E_5(r) = \left[ \begin{array}{c} - 2 r \\ 2 (5 - 3 r) \end{array}\right].
+\end{multline}
+We find three intersections
+and we classify each of them by comparing the tangent vectors
+\begin{gather}
+  I_1:
+  E_2\left(\frac{7}{9}\right) =
+E_3\left(\frac{1}{6}\right) = \frac{16}{9}
+\left[ \begin{array}{c} 0 \\ 1 \end{array}\right] \Longrightarrow
+E_2'\left(\frac{7}{9}\right) \times
+E_3'\left(\frac{1}{6}\right) = 96 \\
+I_2:
+E_0\left(\frac{1}{2}\right) =
+E_3\left(\frac{1}{2}\right) =
+\left[ \begin{array}{c} 4 \\ 0 \end{array}\right] \Longrightarrow
+E_0'\left(\frac{1}{2}\right) \times
+E_3'\left(\frac{1}{2}\right) = 0 \\
+  I_3:
+E_1\left(\frac{1}{8}\right) =
+E_3\left(\frac{3}{4}\right) =
+\left[ \begin{array}{c} 7 \\ 1 \end{array}\right] \Longrightarrow
+E_1'\left(\frac{1}{8}\right) \times
+E_3'\left(\frac{3}{4}\right) = -160.
+\end{gather}
+From here, we construct our curved polygon intersection by drawing
+from our list of intersections until none remain.
+
+\begin{itemize}
+\itemsep 0em
+\item First consider \(I_1\). Since
+  \(E_2' \times
+  E_3' > 0\)
+  at this point, then we consider the curve
+  \(E_3\) to be
+  \emph{interior}.
+\item After classification, we move along
+  \(E_3\) until we
+  encounter another intersection: \(I_2\)
+\item \(I_2\) is a point of tangency since
+  \(E_0'\left(\frac{1}{2}\right) \times
+  E_3'\left(\frac{1}{2}\right) = 0\).
+  Since a tangency has no impact on
+  the underlying intersection geometry, we ignore it and
+  keep moving.
+\item Continuing to move along
+  \(E_3\), we
+  encounter another intersection: \(I_3\).
+  Since
+  \(E_1' \times
+  E_3' < 0\)
+  at this point, we consider the curve
+  \(E_1\) to be
+  \emph{interior} at the intersection. Thus we stop moving
+  along \(E_3\)
+  and we have our first curved segment:
+  \(E_3\left(\left[
+    \frac{1}{6}, \frac{3}{4}\right]\right)\)
+\item Finding no other intersections on \(E_1\)
+  we continue until the end of the edge.
+  Now our (ordered) curved segments are:
+  \begin{equation}
+  E_3\left(\left[
+    \frac{1}{6}, \frac{3}{4}\right]\right) \longrightarrow
+  E_1\left(\left[
+    \frac{1}{8}, 1\right]\right).
+  \end{equation}
+\item Next we stay at the corner and switch to the next curve
+  \(E_2\), moving along that curve
+  until we hit the next intersecton \(I_1\).
+  Now our (ordered) curved segments are:
+  \begin{equation}
+  E_3\left(\left[
+    \frac{1}{6}, \frac{3}{4}\right]\right) \longrightarrow
+  E_1\left(\left[
+    \frac{1}{8}, 1\right]\right) \longrightarrow
+  E_2\left(\left[
+    0, \frac{7}{9}\right]\right).
+  \end{equation}
+  Since we are now back where we started (at \(I_1\))
+  the process stops
+\end{itemize}
+We represent the boundary of the curved polygon as B\'{e}zier curves, so
+to complete the process we reparameterize (\cite[Ch.~5.4]{Farin2001}) each
+curve onto the relevant interval. For example,
+\(E_3\) has control points
+\(p_0 = \left[ \begin{array}{c} -2 \\ 4 \end{array}\right]\),
+\(p_1 = \left[ \begin{array}{c} 4 \\ -4 \end{array}\right]\),
+\(p_2 = \left[ \begin{array}{c} 10 \\ 4 \end{array}\right]\)
+and we reparameterize on \(\alpha = \frac{1}{6}, \beta = \frac{3}{4}\) to
+control points
+\begin{align}
+  q_0 &= E_3\left(\frac{1}{6}\right) =
+  \frac{16}{9} \left[ \begin{array}{c} 0 \\ 1 \end{array}\right] \\
+  q_1 &= (1 - \alpha) \left[(1 - \beta) p_0 + \beta p_1\right] +
+   \alpha \left[(1 - \beta) p_1 + \beta p_2\right] = \frac{1}{6} \left[
+    \begin{array}{c} 21 \\ -8 \end{array}\right] \\
+  q_2 &= E_3\left(\frac{3}{4}\right) = \left[
+    \begin{array}{c} 7 \\ 1 \end{array}\right].
+\end{align}
+
+\subsection{B\'{e}zier Triangle Inverse}
+
+The problem of determining the parameters \((s, t)\) given a point
+\(\bm{p} = \left[\begin{array}{c c} x & y\end{array}\right]^T\)
+in a B\'{e}zier triangle can also be solved by using
+subdivision with a bounding box predicate and then Newton's method
+at the end.
+
+\begin{figure}
+  \includegraphics{locate_in_triangle.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Checking for a point \(\bm{p}\) in each of four subregions
+    when subdividing a B\'{e}zier triangle.}
+  \label{fig:locate-in-triangle}
+\end{figure}
+
+For example, Figure~\ref{fig:locate-in-triangle} shows
+how regions of \(\utri\) can be discarded recursively until the
+suitable region for \((s, t)\) has a sufficiently small area. At
+this point, we can apply Newton's method to the map \(F(s, t) =
+b(s, t) - \bm{p}\). It's very helpful (for Newton's method) that
+\(F: \reals^2 \longrightarrow \reals^2\) since the Jacobian will
+always be invertible
+when the B\'{e}zier triangle is valid. If \(\bm{p} \in \reals^3\)
+then the system would be underdetermined. Similarly, if
+\(\bm{p} \in \reals^2\) but \(b(s)\) is a B\'{e}zier curve then the
+system would be overdetermined.
 

### 2018-08-23 doc/paper.tex
Adding in content from `conclusion.tex` in thesis.

@@
 
+\section{Conclusion}
+
+This work has described a method for conservative interpolation
+between curved meshes. The transfer process conserves globally
+to machine precision since we can use exact quadratures for all
+integrals. The primary source of error comes from solving the linear
+system with the mass matrix for the target mesh. This allows
+less restrictive usage of mesh adaptivity, which can make computations
+more efficient. Additionally, having a global transfer algorithm
+allows for remeshing to be done less frequently.
+
+The algorithm breaks down into three core subproblems: B\'{e}zier triangle
+intersection, an advancing front for intersecting elements and
+integration on curved polygons. The inherently local nature of the
+advancing front allows the algorithm to be parallelized via domain
+decomposition with little data shared between processes. By
+restricting integration to the intersection of elements from the
+target and donor meshes, the algorithm can accurately transfer
+both continuous and discontinuous fields.
+
+\subsection{Future Work}
+
+As mentioned in the preceding chapters, there are several research
+directions possible to build upon the solution transfer algorithm.
+The usage of Green's theorem nicely extends to \(\reals^3\) via
+Stoke's theorem, but the B\'{e}zier triangle intersection algorithm
+is specific to \(\reals^2\). The equivalent B\'{e}zier tetrahedron
+intersection algorithm is significantly more challenging.
+
+The restriction to shape functions from the global coordinates basis
+is a symptom of the method and not of the inherent problem. The
+pre-image basis has several appealing properties, for example
+this basis can be precomputed on \(\utri\). The problem of a
+valid tessellation of a curved polygon warrants more exploration.
+Such a tessellation algorithm would enable usage of the pre-image
+basis.
+
+The usage of the global coordinates basis does have some benefits.
+In particular, the product of shape functions from different meshes
+is still a polynomial in \(\reals^2\). This means that we could
+compute the coefficients of \(F = \phi_0 \phi_1\) directly and
+use them to evaluate the antiderivatives \(H\) and \(V\) rather
+than using the fundamental theorem of calculus. Even if this
+did not save any computation, it may still be preferred over
+the FTC approach because it would remove the usage of quadrature
+points outside of the domain \(\mathcal{P}\).
+
 \bibliography{paper}

### 2018-08-23 doc/paper.tex
Adding in content from `proofs.tex` in thesis.

@@
 \usepackage[labelfont=bf]{caption}
+
+\theoremstyle{definition}
+\newtheorem{lemma}{Lemma}[section]
 
@@
 
+\appendix
+
+\section{Allowing Tessellation with Inverted Triangles}
+
+\begin{lemma}\label{lemma:bad-triangle}
+Consider three smooth curves
+\(b_0, b_1, b_2\) that form a closed loop: \(b_0(1) = b_1(0)\),
+\(b_1(1) = b_2(0)\) and \(b_2(1) = b_0(0)\).
+Take \emph{any} smooth map \(\varphi(s, t)\) on \(\utri\) that
+sends the edges to the three curves:
+\begin{equation}
+\varphi(r, 0) = b_0(r), \quad \varphi(1 - r, r) = b_1(r),
+  \quad \varphi(0, 1 - r) = b_2(r) \quad \text{for } r \in \left[0, 1\right].
+\end{equation}
+Then we must have
+\begin{equation}
+2 \int_{\utri} \det(D\varphi) \left[F \circ \varphi\right] \, dt \, ds =
+\oint_{b_0 \cup b_1 \cup b_2} H \, dy - V \, dx
+\end{equation}
+for antiderivatives that satisfy \(H_x = V_y = F\).
+
+When \(\det(D\varphi) > 0\), this is just the change of variables
+formula combined with Green's theorem.
+\end{lemma}
+
+\begin{proof}
+Let \(x(s, t)\) and \(y(s, t)\) be the components of \(\varphi\). Define
+\begin{equation}
+\Delta S = H(x, y) y_s - V(x, y) x_s \quad \text{and} \quad
+\Delta T = H(x, y) y_t - V(x, y) x_t.
+\end{equation}
+On the unit triangle \(\utri\), Green's theorem gives
+\begin{equation}\label{eq:basic-greens}
+\int_{\mathcal{U}} \left[\partial_s \Delta T -
+  \partial_t \Delta S\right] \, dV =
+\oint_{\partial \mathcal{U}} \Delta S \, ds + \Delta T \, dt.
+\end{equation}
+The boundary \(\partial \utri\) splits into the bottom edge \(E_0\),
+hypotenuse \(E_1\) and left edge \(E_2\).
+
+Since
+\begin{equation}
+E_0 = \left\{ \left[ \begin{array}{c} r \\ 0 \end{array}\right] \mid
+  r \in \left[0, 1\right] \right\}
+\end{equation}
+we take \(\varphi(r, 0) = b_0(r)\) hence
+\begin{equation}
+dx = x_s \, dr, dy = y_s \, dr \Longrightarrow
+H dx - V dy = \Delta S \, dr.
+\end{equation}
+We also have \(ds = dr\) and \(dt = 0\) due to the
+parameterization, thus
+\begin{equation}
+\int_{E_0} \Delta S \, ds + \Delta T \, dt =
+  \int_{r = 0}^{r = 1} \Delta S \, dr = \int_{b_0} H \, dx - V \, dy.
+\end{equation}
+We can similarly verify that
+\(\int_{E_j} \Delta S \, ds + \Delta T \, dt = \int_{b_j} H \, dx - V \, dy\)
+for the other two edges. Combining this with~\eqref{eq:basic-greens}
+we have
+\begin{equation}
+\int_{\mathcal{U}} \left[\partial_s \Delta T -
+  \partial_t \Delta S\right] \, dV =
+\oint_{b_0 \cup b_1 \cup b_2} H \, dx - V \, dy.
+\end{equation}
+To complete the proof, we need
+\begin{equation}
+\int_{\mathcal{U}} \left[\partial_s \Delta T -
+  \partial_t \Delta S\right] \, dV =
+2 \int_{\mathcal{U}} \det(D\varphi) \left[F \circ \varphi\right] \, dV
+\end{equation}
+but one can show directly that
+\begin{equation}
+\partial_s \Delta T - \partial_t \Delta S =
+  2 \left(x_s y_t - x_t y_s\right) F(x, y) =
+  2 \det(D\varphi) \left[F \circ \varphi\right]. \tag*{\qedhere}
+\end{equation}
+\end{proof}
+
 \end{document}

### 2018-08-23 doc/paper.tex
Porting in the intro from `solution-transfer.tex`.

@@
 \newcommand{\reals}{\mathbf{R}}
+\newcommand{\eps}{\varepsilon}
 \newcommand{\utri}{\mathcal{U}}
@@
 with low dissipation and low dispersion error.
+
+\subsection{Actual Intro}
+
+In this chapter, an algorithm for conservative solution transfer between curved
+meshes will be described. This has practical applications to many methods in
+computational physics. Solution transfer is needed when a solution
+(approximated by a discrete field) is known on a \emph{donor} mesh and must
+be transferred to a \emph{target} mesh. In many applications, the field
+must be conserved for physical reasons, e.g. mass or energy cannot leave or
+enter the system, hence the focus on \emph{conservative} solution transfer.
+A few scenarios where solution transfer is necessary will be considered below
+to motivate the ``black box'' solution transfer algorithm.
+
+Since solution transfer is so commonly needed in physical applications, this
+problem of conservative interpolation has been considered already for
+straight sided meshes. The \emph{common refinement} approach in
+\cite{Jiao2004} is used to compare several methods for solution transfer across
+two meshes. However, the problem of constructing a common refinement is
+not discussed there. The problem of constructing such a refinement is
+considered in \cite{Farrell2009, Farrell2011} (called a supermesh by
+the authors).
+However, the solution transfer becomes considerably more challenging for curved
+meshes. For a sense of the difference between the straight sided and curved
+cases, consider the problem of intersecting an element from the donor mesh
+with an element from the target mesh. If the elements are triangles, the
+intersection is either a convex polygon or has measure zero. If the elements
+are curved, the intersection can be non-convex and can even split into
+multiple disjoint regions.
+
+\subsubsection{Lagrangian Methods}
+
+\begin{figure}
+  \includegraphics{simple_transport.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{The solution to \(u_t + u_x = 0, \; u(x, 0) = x^3\) plotted in
+    the \(xu\)-plane. Demonstrates simple transport of
+    the solution.}
+  \label{fig:simple-transport}
+\end{figure}
+
+The method of characteristics helps transform partial differential equations
+into ordinary differential equations by dividing the physical domain into
+a family of curves. For example, the simple transport equation
+\begin{equation}\label{eq:simple-transport}
+u_t + c u_x = 0
+\end{equation}
+can be transformed when restricting to the family of lines
+\(x(t) = x_0 + c t\). On these lines \(u(x(t), t)\) is constant, by
+construction, and so the solution is ``transported'' from \(u(x_0, 0)\)
+along each characteristic line (Figure~\ref{fig:simple-transport}).
+
+Motivated by this, \emph{Lagrangian methods} treat each point in the
+physical domain as a ``particle'' which moves along a characteristic curve
+over time and then monitor values associated with the particle (heat / energy,
+velocity, pressure, density, concentration, etc.). They are an effective way
+to solve PDEs, even with higher order or non-linear terms.
+For example, if a diffusion term is added to~\eqref{eq:simple-transport}
+\begin{equation}
+u_t + c u_x - \eps u_{xx} = 0
+\end{equation}
+then the same characteristics can be used, but the value
+along each characteristic is no longer constant; instead it satisfies the
+ODE \(\frac{d}{dt} u(x(t), t) = \eps u_{xx}\).
+
+This approach transforms the numerical solution of PDEs into a family of
+numerical solutions to many independent ODEs. It allows the use of familiar
+and well understood ODE solvers. In addition, Lagrangian methods often
+have less restrictive conditions on time steps than Eulerian
+methods\footnote{In Eulerian methods, the mesh is fixed.}.
+When solving PDEs on unstructured meshes
+with Lagrangian methods, the nodes move (since they
+are treated like particles) and the mesh ``travels''.
+
+\subsubsection{Remeshing and Adaptivity}
+
+\begin{figure}
+  \includegraphics{mesh_distortion.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Distortion of a regular mesh caused by particle motion along
+    the velocity field \(\left[ y^2 \; 1 \right]^T\) from \(t = 0\)
+    to \(t = 1\) with \(\Delta t = 1/4\).}
+  \label{fig:mesh-distortion}
+\end{figure}
+
+A flow-based change to a mesh can cause problems if it causes the mesh to
+leave the domain being analyzed or if it distorts the mesh until the element
+quality is too low in some mesh elements. Over enough time, the mesh can
+even tangle (i.e. elements begin to overlap).
+For an example of such distortion (Figure~\ref{fig:mesh-distortion}),
+consider a PDE of the form
+\begin{equation}\label{eq:non-rigid-characteristics}
+u_t + \left[ \begin{array}{c} y^2 \\ 1 \end{array}\right] \cdot \nabla u +
+  F\left(u, \nabla u\right) = 0.
+\end{equation}
+The characteristics \(y(t) = y_0 + t, x(t) = x_0 +
+\left(y(t)^3 - y_0^3\right)/3\)
+distort the mesh considerably after just one second.
+
+\begin{figure}
+  \includegraphics{distortion_remesh.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Remeshing a domain after distortion caused by particle motion
+    along the velocity field \(\left[ y^2 \; 1 \right]^T\) from \(t = 0\)
+    to \(t = 1\).}
+  \label{fig:distortion-remesh}
+\end{figure}
+
+To deal with distortion, one can allow the mesh to adapt in between time
+steps. For example, Figure~\ref{fig:distortion-remesh} shows an example
+remeshing of the domain.
+In addition to improving mesh quality, mesh
+adaptivity can be used to dynamically focus computational effort to resolve
+sensitive features of a numerical solution. From \cite{Iske2004}
+\begin{quote}
+{\small In order to balance the method's approximation quality and its
+computational costs effectively, adaptivity is an essential requirement,
+especially when modelling multiscale phenomena.}
+\end{quote}
+For more on mesh adaptivity, see \cite{Babuska1978, Peraire1987, Pain2001}.
+
+In either case, the change in the
+mesh between time steps requires transferring a known solution on the
+discarded mesh to the mesh produced by the remeshing process. Without
+the ability to change the mesh, Lagrangian methods (or, more generally,
+ALE \cite{Hirt1974}) would not be useful, since after a limited time the
+mesh will distort.
+
+\subsubsection{High-order Meshes}
+
+\begin{figure}
+  \includegraphics{main_figure27.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Comparing straight sided meshes to a curved mesh when approximating
+    the unit disc in \(\reals^2\).}
+  \label{fig:curved-vs-straight-mesh}
+\end{figure}
+
+To allow for greater geometric flexibility and for high order of convergence,
+curved mesh elements can be used in the finite element method. Though the
+complexity of a method can steeply rise when allowing curved elements, the
+trade for high-order convergence can be worth it. (See \cite{Wang2013} for
+more on high-order CFD methods.) Curved meshes can typically
+represent a given geometry with far fewer elements than a straight sided mesh
+(for example, Figure~\ref{fig:curved-vs-straight-mesh}).
+The increase in accuracy also allows for the use of fewer elements, which
+in turn can also facilitate a reduction in the overall computation time.
+
+\begin{figure}
+  \includegraphics{element_distortion.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Movement of nodes in a quadratic element under distortion caused
+    by particle motion along the velocity field \(\left[ y^2 \; 1 \right]^T\)
+    from \(t = 0\) to \(t = 1\) with \(\Delta t = 1/2\). The green curves
+    represent the characteristics that each node travels along.}
+  \label{fig:element-distortion}
+\end{figure}
+
+Even if the domain has no inherent curvature, high-order (degree \(p\)) shape
+functions allow for order \(p + 1\) convergence, which is desirable in
+it's own right. However, even in such cases, a Lagrangian method must either
+curve the mesh or information about the flow of the geometry will be lost.
+Figure~\ref{fig:element-distortion} shows what happens to a given
+quadratic element as the nodes move along the
+characteristics from~\eqref{eq:non-rigid-characteristics}.
+This element uses the triangle vertices and edge
+midpoints to determine the shape functions. However, as the nodes move
+with the flow, the midpoints are no longer on the lines connecting
+the vertex nodes. To allow the mesh to more accurately represent the
+solution, the edges can instead curve so that the midpoint nodes remain
+halfway between (i.e. half of the parameter space) the vertex nodes along
+an edge.
+
+\subsubsection{Multiphysics and Comparing Methods}
+
+In multiphysics simulations, a problem is partitioned into physical components.
+This partitioning can apply to both the physical domain (e.g. separating a
+solid and fluid at an interface) and the simulation solution itself (e.g.
+solving for pressure on one mesh and velocity on another). Each (multi)physics
+component is solved for on its own mesh. When the components interact, the
+simulation solution must be transferred between those meshes.
+
+In a similar category of application, solution transfer enables the comparison
+of solutions defined on different meshes. For example, if a reference
+solution is known on a very fine special-purpose mesh, the error can be
+computed for a coarse mesh by transferring the solution from the fine
+mesh and taking the difference. Or, if the same method is used on
+different meshes of the same domain, the resulting computed solutions can
+be compared via solution transfer. Or, if two different methods use two
+different meshes of the same domain.
+
+\subsubsection{Local versus Global Transfer}
+
+Conservative solution transfer has been around since the advent of ALE,
+and as a result much of the existing literature focuses on mesh-mesh
+pairs that will occur during an ALE-based simulation. When flow-based
+mesh distortion occurs, elements are typically ``flipped'' (e.g. a
+diagonal is switched in a pair of elements) or elements are subdivided
+or combined. These operations are inherently local, hence the solution
+transfer can be done locally across known neighbors. Typically, this
+locality is crucial to solution transfer methods. In \cite{Margolin2003},
+the transfer is based on partitioning elements of the updated mesh into
+components of elements from the old mesh and ``swept regions'' from
+neighbouring elements. In \cite{Kucharik2008}, the (locally) changing
+connectivity of the mesh is addressed. In \cite{Garimella2007}, the
+local transfer is done on polyhedral meshes.
+
+Global solution transfer instead seeks to conserve the solution across
+the whole mesh. It makes no assumptions about the relationship between
+the donor and target meshes. The loss in local information makes
+the mesh intersection problem more computationally expensive, but the
+added flexibility reduces timestep restrictions since it allows remeshing
+to be done less often. In \cite{Dukowicz1984, Dukowicz1987}, a global
+transfer is enabled by transforming volume integrals to surface integrals
+via the divergence theorem to reduce the complexity of the problem.
+
+\subsubsection{Limitations}
+
+\begin{figure}
+  \includegraphics{main_figure29.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Partially overlapping meshes on a near identical domain. Both are
+    linear meshes that approximate the unit disc in \(\reals^2\). The outermost
+    columns show how the domain of each mesh can be expanded so they agree.}
+  \label{fig:partially-overlapping}
+\end{figure}
+
+The method described in this work only applies to meshes in \(\reals^2\).
+Application to meshes in \(\reals^3\) is a direction for future research,
+though the geometric kernels (see Chapter~\ref{sec:bezier-intersection})
+become significantly more challenging to describe and implement. In
+addition, the method will assume that every element in the
+target mesh is contained in the donor mesh. This ensures that the solution
+transfer is \emph{interpolation}. In the case where all target elements are
+partially covered, \emph{extrapolation} could be used to extend a solution
+outside the domain, but for totally uncovered elements there is no clear
+correspondence to elements in the donor mesh.
+
+The case of partially overlapping meshes can be addressed in particular
+cases (i.e. with more information). For example, consider a problem
+defined on \(\Omega = \reals^2\) and solution
+that tends towards zero as points tend to infinity. A typical approach
+may be to compute the solution on a circle of large enough radius and
+consider the numerical solution to be zero outside the circle.
+Figure~\ref{fig:partially-overlapping} shows how solution transfer could be
+performed in such cases when the meshes partially overlap: construct a
+simple region containing both computational domains and then mesh the
+newly introduced area. However, the assumption that the numerical solution
+is zero in the newly introduced area is very specific and
+a similar approach may not apply in other cases of partial overlap.
+
+Some attempts (\cite{Berger1987, Chesshire1994, Cai1999}) have been
+made to interpolate fluxes between overlapping meshes. These perform
+an interpolation on the region common to both meshes and then numerically
+solve the PDE to determine the values on the uncovered elements.
+
+When solving some PDEs with viscoelastic fields, additional nodes must be
+tracked at quadrature points. As the mesh travels, these quadrature points
+must be moved as well in a way that is consistent with the standard
+nodes that define the element. The solution transfer method described here
+does not provide a way either to determine quadrature points on a
+target mesh or to map the field onto known quadrature points.
 

### 2018-08-23 doc/paper.tex
Finished bringing over content from `solution-transfer.tex` in thesis.

@@
 \newcommand{\eps}{\varepsilon}
+\newcommand{\bigO}[1]{\mathcal{O}\left(#1\right)}
+\newcommand{\mach}{\mathbf{u}}
 \newcommand{\utri}{\mathcal{U}}
@@
 in-depth discussion of the computational geometry methods needed
-to implement to enable solution transfer. Section~\ref{sec:solution-transfer}
+to implement to enable solution transfer. Section~\ref{sec:galerkin-projection}
+(and following)
 describes the solution transfer process and gives results of some
@@
 
-\section{Solution Transfer}\label{sec:solution-transfer}
-
-Placeholder.
+\section{Galerkin Projection}\label{sec:galerkin-projection}
+
+\begin{figure}
+  \includegraphics{main_figure00.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Mesh pair: donor mesh \(\mathcal{M}_D\) and
+    target mesh \(\mathcal{M}_T\).}
+  \label{fig:donor-target-pair}
+\end{figure}
+
+Consider a donor mesh \(\mathcal{M}_D\) with shape function basis
+\(\phi_D^{(j)}\) and a known field \(\bm{q}_D = \sum_j d_j \phi_D^{(j)}\)
+\footnote{This is somewhat a simplification. In the CG case,
+some coefficients will be paired with multiple shape functions, such
+as the coefficient at a vertex node.}
+and a
+target mesh \(\mathcal{M}_T\) with shape function basis \(\phi_T^{(j)}\)
+(Figure~\ref{fig:donor-target-pair}).
+Each shape function \(\phi\) corresponds to a
+given isoparametric curved element (see Section~\ref{sec:curved-elements})
+\(\mathcal{T}\) in one of these meshes and has
+\(\operatorname{supp}(\phi) = \mathcal{T}\).
+Additionally, the shape functions are polynomial degree \(p\) (see
+Section~\ref{subsec:shape-functions} for a discussion of shape functions),
+but the degree of the donor mesh need not be the same as that of the
+target mesh. We assume that both meshes cover the same domain \(\Omega \subset
+\reals^2\), however we really only require the donor mesh to cover the
+target mesh.
+
+We seek the \(L_2\)-optimal interpolant \(\bm{q}_T = \sum_j t_j \phi_T^{(j)}\):
+\begin{equation}
+\left \lVert \bm{q}_T - \bm{q}_D \right \rVert_2 =
+\min_{\bm{q} \in \mathcal{V}_T}
+\left \lVert \bm{q} - \bm{q}_D \right \rVert_2
+\end{equation}
+where \(\mathcal{V}_T = \operatorname{Span}_j\left\{\phi_T^{(j)}\right\}\)
+is the function space defined on the target mesh. Since this is optimal in
+the \(L_2\) sense, by differentiating with respect to each \(t_j\) in
+\(\bm{q}_T\) we find the weak form:
+\begin{equation}
+\int_{\Omega} \bm{q}_D \phi_T^{(j)} \, dV =
+  \int_{\Omega} \bm{q}_T \phi_T^{(j)} \, dV, \qquad \text{for all } j.
+\end{equation}
+If the constant function \(1\) is contained in \(\mathcal{V}_T\),
+conservation follows from the weak form and linearity of the integral
+\begin{equation}
+\int_{\Omega} \bm{q}_D \, dV =
+  \int_{\Omega} \bm{q}_T \, dV.
+\end{equation}
+Expanding \(\bm{q}_D\) and \(\bm{q}_T\) with respect to their coefficients
+\(\bm{d}\) and \(\bm{t}\), the weak form gives rise to a linear system
+\begin{equation}\label{eq:weak-form-system}
+M_T \bm{t} = M_{TD} \bm{d}.
+\end{equation}
+Here \(M_T\) is the mass matrix for
+\(\mathcal{M}_T\) given by
+\begin{equation}
+\left(M_T\right)_{ij} = \int_{\Omega} \phi_T^{(i)} \phi_T^{(j)} \, dV.
+\end{equation}
+In the discontinuous Galerkin case, \(M_T\) is block diagonal with blocks
+that correspond to each element, so \eqref{eq:weak-form-system} can be
+solved locally on each element \(\mathcal{T}\) in the target mesh. By
+construction, \(M_T\) is symmetric and sparse since \(\left(M_T\right)_{ij}\)
+will be \(0\) unless \(\phi_T^{(i)}\) and \(\phi_T^{(j)}\) are supported
+on the same element \(\mathcal{T}\). In the continuous case, \(M_T\) is
+globally coupled since coefficients corresponding to boundary nodes interact
+with multiple elements. The matrix \(M_{TD}\) is a ``mixed'' mass matrix
+between the target and donor meshes:
+\begin{equation}
+\left(M_{TD}\right)_{ij} = \int_{\Omega} \phi_T^{(i)} \phi_D^{(j)} \, dV.
+\end{equation}
+Boundary conditions can be imposed on the system by fixing some coefficients,
+but that is equivalent to removing some of the basis functions which may
+in term make the projection non-conservative. This is because the removed
+basis functions may have been used in \(1 = \sum_j u_j \phi_{T}^{(j)}\).
+
+Computing \(M_T\) is fairly straightforward since the (bidirectional) mapping
+from elements \(\mathcal{T}\) to basis functions \(\phi_T^{(j)}\) supported
+on those elements is known. When using shape functions in the
+global coordinates basis (see Section~\ref{subsec:shape-functions}), the
+integrand \(F = \phi_T^{(i)} \phi_T^{(j)}\) will be a polynomial of degree
+\(2p\) on \(\reals^2\). The domain of integration \(\mathcal{T}
+= b\left(\utri\right)\) is the image of a (degree \(p\)) map \(b(s, t)\)
+from the unit triangle. Using substitution
+\begin{equation}\label{eq:mass-mat-subst}
+\int_{b\left(\utri\right)} F(x, y) \, dx \, dy =
+  \int_{\utri} \det(Db) F\left(x(s, t), y(s, t)\right) \, ds \, dt
+\end{equation}
+(we know the map preserves orientation, i.e. \(\det(Db)\) is positive).
+Once transformed this way, a quadrature rule on the unit
+triangle (\cite{Dunavant1985}) can be used.
+
+On the other hand, computing \(M_{TD}\) is significantly more
+challenging. This requires solving both a geometric problem ---
+finding the region to integrate over --- and an analytic
+problem --- computing the integrals. The integration can be done with
+a quadrature rule, though finding this region is significantly
+more difficult.
+
+\section{Common Refinement}
+
+\begin{figure}
+  \includegraphics{main_figure02.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{All donor elements that cover a target element}
+  \label{fig:target-elt-all-matching}
+\end{figure}
+
+Rather than computing \(M_{TD}\), the right-hand side
+of~\eqref{eq:weak-form-system} can be computed directly via
+\begin{equation}\label{eq:lumped-mixed-mass-matrix}
+\left(M_{TD} \bm{d}\right)_j = \int_{\Omega} \phi_T^{(j)} \bm{q}_D \, dV.
+\end{equation}
+Any given \(\phi\) is supported on an element \(\mathcal{T}\) in the
+target mesh. Since \(\bm{q}_D\) is piecewise defined over each element
+\(\mathcal{T}'\) in the donor mesh, the
+integral~\eqref{eq:lumped-mixed-mass-matrix} may be problematic.
+In the continuous Galerkin case, \(\bm{q}_D\) need not be differentiable
+across \(\mathcal{T}\) and in the discontinuous Galerkin case,
+\(\bm{q}_D\) need not even be continuous. This necessitates a
+partitioning of the domain:
+\begin{equation}
+\int_{\Omega} \phi \, \bm{q}_D \, dV =
+  \int_{\mathcal{T}} \phi \, \bm{q}_D \, dV =
+  \sum_{\mathcal{T}' \in \mathcal{M}_D} \int_{\mathcal{T} \cap \mathcal{T}'}
+    \phi \left.\bm{q}_D\right|_{\mathcal{T}'} \, dV.
+\end{equation}
+In other words, the integral over \(\mathcal{T}\) splits into integrals
+over intersections \(\mathcal{T} \cap \mathcal{T}'\) for all
+\(\mathcal{T}'\) in the donor mesh that intersect \(\mathcal{T}\)
+(Figure~\ref{fig:target-elt-all-matching}). Since both \(\phi\) and
+\(\left.\bm{q}_D\right|_{\mathcal{T}'}\) are polynomials on
+\(\mathcal{T} \cap \mathcal{T}'\), the integrals will be exact when
+using a quadrature scheme of an appropriate degree of accuracy.
+Without partitioning \(\mathcal{T}\), the integrand is not a polynomial
+(in fact, possibly not smooth), so the quadrature cannot be exact.
+
+In order to compute \(M_{TD} \bm{d}\), we'll need to compute the
+\emph{common refinement}, i.e. an intermediate mesh that contains
+both the donor and target meshes. This will consist of all non-empty
+\(\mathcal{T} \cap \mathcal{T}'\) as \(\mathcal{T}\) varies over
+elements of the target mesh and \(\mathcal{T}'\) over elements of the
+donor mesh. This requires solving three specific subproblems:
+\begin{itemize}
+%% H/T: https://tex.stackexchange.com/a/6086/32270
+\itemsep 0em
+\item Forming the region(s) of intersection between two elements that
+  are B\'{e}zier triangles.
+\item Finding all pairs of elements, one each from the target and donor mesh,
+  that intersect.
+\item Numerically integrating over a region of intersection between two
+  elements.
+\end{itemize}
+The first subproblem has been addressed in
+Section~\ref{subsec:intersect-bez-tri}
+and the curved polygon region(s) of intersection have been described
+in Section~\ref{subsec:curved-polygons}. The second will be considered
+in Section~\ref{subsec:advancing-front} and the third in
+Section~\ref{subsec:integration-on-curved} below.
+
+\subsection{Advancing Front}\label{subsec:advancing-front}
+
+\begin{figure}
+  \includegraphics{main_figure13.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Brute force search for a donor element \(\mathcal{T}'\) that matches
+    a fixed target element \(\mathcal{T}\).}
+  \label{fig:target-elt-brute-force}
+\end{figure}
+
+We seek to identify all pairs \(\mathcal{T}\) and \(\mathcal{T}'\) of
+intersecting target and donor elements. The na\"{i}ve approach just
+considers every pair
+of elements and takes \(\bigO{\left|\mathcal{M}_D\right|
+\left|\mathcal{M}_T\right|}\) to complete.\footnote{For a mesh \(\mathcal{M}\),
+the expression \(\left|\mathcal{M}\right|\) represents the number of elements
+in the mesh.} Taking after \cite{Farrell2011}, we can do much better than this
+quadratic time search. In fact, we can compute all integrals in
+\(\bigO{\left|\mathcal{M}_D\right| + \left|\mathcal{M}_T\right|}\).
+First, we fix an element of the target mesh and perform a brute-force search
+to find an intersecting element in the donor mesh
+(Figure~\ref{fig:target-elt-brute-force}). This has worst-case time
+\(\bigO{\left|\mathcal{M}_D\right|}\).
+
+\begin{figure}
+  \includegraphics{main_figure14.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{All donor elements \(\mathcal{T}'\) that cover a target element
+    \(\mathcal{T}\), with an extra layer of neighbors in the donor mesh
+    that \emph{do not} intersect \(\mathcal{T}\).}
+  \label{fig:target-elt-overlap-extra-layer}
+\end{figure}
+
+Once we have such a match, we use the connectivity graph of the
+donor mesh to perform a breadth first search
+for neighbors that also intersect the target
+element \(\mathcal{T}\) (Figure~\ref{fig:target-elt-overlap-extra-layer}).
+This search takes \(\bigO{1}\) time. It's also worthwhile to keep the first
+layer of donor elements that don't intersect \(\mathcal{T}\) because they are
+more likely to intersect the neighbors of \(\mathcal{T}\)\footnote{In the
+very unlikely case that the boundary of \(\mathcal{T}\)
+\emph{exactly matches} the boundaries of the donor elements that cover it,
+\emph{none} of the overlapping donor elements can intersect the neighbors of
+\(\mathcal{T}\) so the first layer of non-intersected donor
+elements must be considered.}. Using the list of intersected elements, a
+neighbor of \(\mathcal{T}\) can find a donor element it intersects with in
+\(\bigO{1}\) time (Figure~\ref{fig:target-elt-neighbor}).
+As seen, after our \(\bigO{\left|\mathcal{M}_D\right|}\)
+initial brute-force search, the localized intersections for each
+target element \(\mathcal{T}\) take
+\(\bigO{1}\) time. So together, the process takes
+\(\bigO{\left|\mathcal{M}_D\right| + \left|\mathcal{M}_T\right|}\).
+
+For special cases, e.g. ALE methods, the initial brute-force search
+can be reduced to \(\bigO{1}\). This could be enabled by tracking
+the remeshing process so a correspondence already exists. If a full
+mapping from donor to target mesh exists, the process of computing
+\(M_T\) and \(M_{TD} \bm{d}\) can be fully parallelized across
+elements of the target mesh, or even across shape functions
+\(\phi_T^{(j)}\).
+
+\begin{figure}
+  \includegraphics{main_figure15.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{First match between a neighbor of the previously considered
+    target element and all the donor elements that match the
+    previously considered target element.}
+  \label{fig:target-elt-neighbor}
+\end{figure}
+
+\subsection{Integration over Curved Polygons}
+\label{subsec:integration-on-curved}
+
+In order to numerically evaluate integrals of the form
+\begin{equation}
+\int_{\mathcal{T}_0 \cap \mathcal{T}_1} F(x, y) \, dV
+\end{equation}
+we must have a quadrature rule on these curved polygon
+(Section~\ref{subsec:curved-polygons}) intersections
+\(\mathcal{T}_0 \cap \mathcal{T}_1\).
+To do this, we transform the integral into several line integrals
+via Green's theorem and then use an exact Gaussian quadrature to
+evaluate them. Throughout this section we'll assume the integrand
+is of the form \(F = \phi_0 \phi_1\) where each \(\phi_j\) is a shape
+function on \(\mathcal{T}_j\). In addition, we'll refer to the two
+B\'{e}zier maps that define the elements being intersected:
+\(\mathcal{T}_0 = b_0\left(\utri\right)\) and
+\(\mathcal{T}_1 = b_1\left(\utri\right)\).
+
+\begin{figure}
+  \includegraphics{polygon_vs_curved.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Comparing the relative error for the computed area of a quadratic
+    B\'{e}zier triangle. In one method, the curved boundary is used and the
+    result is correct to machine precision. In the other, the curved edges
+    are approximated by polygonal paths.}
+  \label{fig:polygon-vs-curved}
+\end{figure}
+
+\begin{figure}
+  \includegraphics
+      {polygon_vs_curved_intersection.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Comparing the relative error for the computed area of the
+    intersection of two quadratic B\'{e}zier triangles. In one method, the
+    intersection boundary is fully specified as the union of B\'{e}zier curve
+    segments and the area is computed correctly to machine precision. In the
+    other, the curved edges are approximated by polygonal paths and the
+    intersection of the resulting polygons is computed.}
+  \label{fig:polygon-vs-curved-intersection}
+\end{figure}
+
+First a discussion of a method not used. A somewhat simple approach would be
+be to use polygonal approximation. I.e. approximate the boundary of each
+B\'{e}zier triangle with line segments, intersect the resulting polygons,
+triangulate the intersection polygon(s) and then numerically integrate
+on each triangulated cell. However, this approach is prohibitively inefficient.
+For example, consider the curved polygon in
+Figure~\ref{fig:polygon-vs-curved}. Computing the area of \(\mathcal{P}\)
+can be done via an integral: \(\int_{\mathcal{P}} 1 \, dV\).
+By using the actual curved boundary, this integral can be computed with
+relative error (the dashed line in the bottom right subplot) on the order
+of machine precision \(\bigO{\mach}\). On the other hand, approximating
+each side of \(\mathcal{P}\) with \(N\) line segments, the relative error is
+\(\bigO{1/N^2}\). (For example, if \(N = 2\) an edge curve \(b(s, 0)\) would be
+replaced by segments connecting \(b(0, 0), b(1/2, 0)\) and \(b(1, 0)\), i.e.
+\(N + 1\) equally spaced parameters.) This means that in order to perform as
+well as an \emph{exact} quadrature used in the curved case, we'd
+need \(N = \bigO{1/\sqrt{\mach}}\). Compute the area of \(\mathcal{P}\)
+in this way assumes that \(\mathcal{P}\) is already known.
+If instead only the B\'{e}zier triangles in the intersection are known, as
+in Figure~\ref{fig:polygon-vs-curved-intersection}, the polygonal approach
+suffers from the same inefficiency.
+
+Since polygonal approximation is prohibitively expensive,
+we work directly with curved edges and compute integrals on a regular
+domain via substitution.
+If two B\'{e}zier triangles intersect with positive measure, then
+the region of intersection is one or more disjoint curved polygons:
+\(\mathcal{T}_0 \cap \mathcal{T}_1 = \mathcal{P}\) or
+\(\mathcal{T}_0 \cap \mathcal{T}_1 = \mathcal{P} \cup
+\mathcal{P}' \cup \cdots\).
+The second case can be handled in the same way as the first by handling each
+disjoint region independently:
+\begin{equation}
+\int_{\mathcal{T}_0 \cap \mathcal{T}_1} F(x, y) \, dV =
+  \int_{\mathcal{P}} F(x, y) \, dV +
+  \int_{\mathcal{P}'} F(x, y) \, dV + \cdots.
+\end{equation}
+Each curved polygon \(\mathcal{P}\) is defined by its boundary, a
+piecewise smooth parametric curve:
+\begin{equation}
+\partial \mathcal{P} = C_1 \cup \cdots \cup C_n.
+\end{equation}
+This can be thought of as a polygon with \(n\)-sides that happens to
+have curved edges.
+
+Quadrature rules for straight sided polygons have been
+studied (\cite{Mousavi2009}) though they are not in wide use. Even
+if a polygonal quadrature rule was to be employed, a map would need to be
+established from a reference polygon onto the curved edges. This map
+could then be used with a change of coordinates to move the integral
+from the curved polygon to the reference polygon. The problem of extending
+a mapping from a boundary to an entire domain has been studied as
+transfinite interpolation
+(\cite{chenin:tel-00284680, Gordon1982, Perronnet1998}),
+barycentric coordinates (\cite{Wachspress1975}) or mean value coordinates
+(\cite{Floater2003}). However, these maps aren't typically suitable for
+numerical integration because they are either not bijective or increase the
+degree of the edges.
+
+\begin{figure}
+  \includegraphics{main_figure11.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Curved polygon tessellation, done by introducing diagonals
+    from a single vertex node.}
+  \label{fig:tessellated-curved-polygon}
+\end{figure}
+
+Since simple and well established quadrature rules do exist for triangles,
+a valid approach would be
+to tessellate a curved polygon into valid B\'{e}zier triangles
+(Figure~\ref{fig:tessellated-curved-polygon}) and then use substitution as
+in~\eqref{eq:mass-mat-subst}. However, tessellation is challenging for both
+theoretical and computational reasons.
+Theoretical: it's not even clear if an arbitrary curved polygon \emph{can}
+be tessellated into B\'{e}zier triangles. Computational: the placement
+of diagonals and potential introduction of interior nodes is very
+complex in cases where the curved polygon is nonconvex. What's more,
+the curved polygon is given only by the boundary, so higher degree triangles
+(i.e. cubic and above) introduced during tessellation would need to place
+interior control points without causing the triangle to invert. To get a
+sense for these challenges, note how the ``simple'' introduction of
+diagonals in Figure~\ref{fig:bad-tessellation-required} leads to one
+inverted element (the gray element) and another element with area outside
+of the curved polygon (the yellow element). Inverted B\'{e}zier triangles
+are problematic because the accompanying mapping leaves the boundary
+established by the edge curves. For example,
+if the tessellation of \(\mathcal{P}\) contains an inverted
+B\'{e}zier triangle \(\mathcal{T}_2 = b\left(\utri\right)\) then we'll
+need to numerically integrate
+\begin{equation}
+\int_{\mathcal{T}_2} \phi_0 \phi_1 \, dx \, dy =
+  \int_{\utri} \left|\det(Db)\right| \left(\phi_0 \circ b\right)
+  \left(\phi_1 \circ b\right) \, ds \, dt.
+\end{equation}
+If the shape functions are from the pre-image basis (see
+Section~\ref{subsec:shape-functions}), then \(\phi_0\)
+will not be defined at \(b(s, t) \not\in \mathcal{T}_0\) (similarly for
+\(\phi_1\)). Additionally, the absolute value in \(\left|\det(Db)\right|\)
+makes the integrand non-smooth since for inverted elements
+\(\det(Db)\) takes both signs. If the shape functions are from the
+global coordinates basis, then tessellation can be used via an
+application of Lemma~\ref{lemma:bad-triangle}, however this involves
+more computation than just applying Green's theorem along
+\(\partial \mathcal{P}\). By applying the lemma, inverted elements may
+be used in a tessellation, for example by introducing artificial
+diagonals from a vertex as in Figure~\ref{fig:tessellated-curved-polygon}.
+In the global coordinates basis, \(F = \phi_0 \phi_1\) \emph{can}
+be evaluated for points in an inverted element that leave
+\(\mathcal{T}_0\) or \(\mathcal{T}_1\).
+
+\begin{figure}
+  \includegraphics{main_figure16.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Curved polygon intersection that can't be tessellated
+    (with valid B\'{e}zier triangles) by introducing diagonals.}
+  \label{fig:bad-tessellation-required}
+\end{figure}
+
+Instead, we focus on a Green's theorem based approach.
+Define horizontal and vertical antiderivatives
+\(H, V\) of the integrand \(F\) such that \(H_x = V_y = F\).
+We make these \emph{unique} by imposing the
+extra condition that \(H(0, y) \equiv V(x, 0) \equiv 0\).
+This distinction is arbitrary, but in order to \emph{evaluate}
+\(H\) and \(V\), the univariate functions \(H(0, y)\) and \(V(x, 0)\)
+must be specified.
+Green's theorem tells us that
+\begin{equation}
+\int_{\mathcal{P}} 2 F \, dV =
+\int_{\mathcal{P}} H_x + V_y \, dV =
+\oint_{\partial \mathcal{P}} H \, dy - V \, dx =
+\sum_j \int_{C_j} H \, dy - V \, dx.
+\end{equation}
+For a given curve \(C\) with components \(x(r), y(r)\)
+defined on the unit interval, this amounts to having
+to integrate
+\begin{equation}
+G(r) = H(x(r), y(r)) y'(r) - V(x(r), y(r)) x'(r).
+\end{equation}
+To do this, we'll use Gaussian
+quadrature with degree of accuracy sufficient to cover the degree
+of \(G(r)\).
+
+If the shape functions are in the global coordinates basis
+(Section~\ref{subsec:shape-functions}), then \(G\) will also be a polynomial.
+This is because for these shape functions \(F = \phi_0 \phi_1\) will be
+polynomial on \(\reals^2\) and so will \(H\) and \(V\) and since each curve
+\(C\) is a B\'{e}zier curve segment, the components are also polynomials.
+If the shape functions are in the pre-image basis, then \(F\) won't in general
+be polynomial, hence the quadrature rules can only be approximate.
+
+To evaluate \(G\), we must also evaluate \(H\) and \(V\) numerically.
+For example, since \(H(0, y) \equiv 0\),
+the fundamental theorem of calculus tells us that
+\(H\left(\alpha, \beta\right) = \int_0^{\alpha} F\left(x, \beta\right) \, dx\).
+To compute this integral via Gaussian quadrature
+\begin{equation}
+H\left(\alpha, \beta\right) \approx \frac{\alpha}{2} \sum_j w_j
+  F\left(\frac{\alpha}{2} (x_j + 1), \beta\right)
+\end{equation}
+we must be able to evaluate \(F\) for
+points on the line \(y = \beta\) for \(x\) between \(0\) and \(\alpha\). If
+the shape functions are from the pre-image basis, it may not even be possible
+to evaluate \(F\) for such points. Since \(\left[\begin{array}{c c} \alpha &
+\beta \end{array}\right]^T\) is on the boundary of \(\mathcal{P}\), without
+loss of generality
+assume it is on the boundary of \(\mathcal{T}_0\). Thus, for some elements
+(e.g. if the point is on the bottom of the element), points
+\(\left[\begin{array}{c c} \nu & \beta \end{array}\right]^T\) may not be
+in \(\mathcal{T}_0\). Since \(\operatorname{supp}(\phi_0) = \mathcal{T}_0\),
+we could take \(\phi_0(\nu, \beta) = 0\), but this would make the integrand
+non-smooth and so the accuracy of the \emph{exact} quadrature would be
+lost. But extending \(\phi_0 = \widehat{\phi}_0 \circ b_0^{-1}\) outside
+of \(\mathcal{T}_0\) may be impossible: even though \(b_0\) is bijective on
+\(\utri\) it may be many-to-one elsewhere hence \(b_0^{-1}\) can't be
+reliably extended outside of \(\mathcal{T}_0\).
+
+Even if the shape functions are from the global coordinates basis,
+setting \(H(0, y) \equiv 0\) may introduce quadrature points that
+are very far from \(\mathcal{P}\). This can be somewhat addressed by using
+\(H(m, y) \equiv 0\) for a suitably chosen \(m\) (e.g. the minimum
+\(x\)-value in \(\mathcal{P}\)). Then we have
+\(H\left(\alpha, \beta\right) = \int_m^{\alpha} F\left(x, \beta\right) \, dx\).
+
+\section{Numerical Experiments}
+
+\begin{figure}
+  \includegraphics{main_figure30.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Some example meshes used during the numerical
+    experiments; the donor meshs is on the left / blue and the target
+    mesh is on the right / green. These meshes are the cubic approximations
+    of each domain and have been refined twice.}
+  \label{fig:meshes-used-refined}
+\end{figure}
+
+A numerical experiment was performed to investigate the observed order
+of convergence. Three pairs of random meshes were generated, the donor
+on a square of width \(17 / 8\) centered at the origin
+and the target on the unit disc. These domains were chosen intentionally so
+that the target mesh was completely covered by the donor mesh and the
+boundaries did not accidentally introduce ill-conditioned intersection between
+elements. The pairs were linear, quadratic and
+cubic approximations of the domains. The convergence test was done by
+refining each pair of meshes four times and performing solution transfer
+at each level. Figure~\ref{fig:meshes-used-refined} shows the cubic
+pair of meshes after two refinements.
+
+\begin{figure}
+  \includegraphics{main_figure25.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Convergence results for scalar fields on three pairs of related
+    meshes: a linear, quadratic and cubic mesh of the same domain.}
+  \label{fig:composite-errors}
+\end{figure}
+
+Taking after \cite{Farrell2011}, we transfer three
+discrete fields in the discontinuous Galerkin (DG) basis.
+Each field is derived from one of the smooth scalar functions
+\begin{align}
+\zeta_1(x, y) &= 5 y^3 + x^2 + 2y + 3 \\
+\zeta_2(x, y) &= \exp\left(x^2\right) + 2y \\
+\zeta_3(x, y) &= \sin(x) + \cos(y).
+\end{align}
+For a given mesh size \(h\), we expect that on a degree \(p\) isoparametric
+mesh our solution transfer will have \(\bigO{h^{p + 1}}\) errors. To measure
+the rate of convergence:
+\begin{itemize}
+\itemsep 0em
+\item Choose a mesh pair \(\mathcal{M}_D\), \(\mathcal{M}_T\) and
+a known function \(\zeta(x, y)\).
+\item Refine the meshes recursively, starting with
+  \(\mathcal{M}_D^{(0)} = \mathcal{M}_D\),
+  \(\mathcal{M}_T^{(0)} = \mathcal{M}_T\).
+\item Create meshes
+\(\mathcal{M}_D^{(j)}\) and \(\mathcal{M}_T^{(j)}\) from
+\(\mathcal{M}_D^{(j - 1)}\)
+and \(\mathcal{M}_T^{(j - 1)}\) by subdividing each curved
+element into four elements.
+\item Approximate \(\zeta\) by a discrete field: the nodal
+interpolant on the donor mesh \(\mathcal{M}_D^{(j)}\). The
+nodal interpolant is constructed by evaluating \(\zeta\) at the
+nodes \(\bm{n}_j\) corresponding to each shape function:
+\begin{equation}
+\bm{f}_j = \sum_i \zeta\left(\bm{n}_i\right) \phi_D^{(i)}.
+\end{equation}
+\item Transfer \(\bm{f}_j\) to the discrete field \(\bm{g}_j\) on
+the target mesh  \(\mathcal{M}_T^{(j)}\).
+\item Compute the relative error on \(\mathcal{M}_T^{(j)}\):
+\(E_j = \| \bm{g}_j - \zeta \|_2 / \| \zeta \|_2\) (here \(\| \cdot \|_2\)
+is the \(L_2\) norm on the target mesh).
+
+We should instead be measuring \(\| \bm{g}_j - \bm{f}_j \|_2 /
+\| \bm{f}_j \|_2\), but \(E_j\) is much easier to
+compute for \(\zeta(x, y)\) that are straightforward to evaluate.
+Due to the triangle inequality \(E_j\) can be a reliable proxy
+for the actual projection error, though when
+\(\| \bm{f}_j - \zeta \|_2\) becomes too large it will dominate
+the error and no convergence will be observed.
+\end{itemize}
+
+Convergence results are shown in Figure~\ref{fig:composite-errors}
+and confirm the expected orders. Since \(\zeta_1\) is a cubic polynomial,
+the solution transfer on the cubic mesh should be \emph{exact}, so there
+is a certain minimum threshold that can be reached.
 

### 2018-08-23 doc/paper.tex
Making figure and equation numbering specific to section.
Adding Per as co-author.
Also removing the last sentence of the abstract. It was there in the
disseration as a way to flow into the discussion of compensated
algorithms for curve intersection, but here that isn't the focus.
Fixing first part of Introduction to be fluid.
It had two disjoint sections just pasted next to each other.

Also

- Making the introduction subsections into actual subsections
  rather than subsubsections
- Moving the "Bezier Intersection Problems" section to the appendix
- Adding a missing period after R^2 in a sen

@@
 \lhead{High-order Solution Transfer between Curved Meshes}
-\rhead{Danny Hermes}
-
+\rhead{Danny Hermes, Per-Olof Persson}
+
+%% H/T: https://tex.stackexchange.com/a/28334/32270
+\usepackage{chngcntr}
+\counterwithin{figure}{section}
+\counterwithin{equation}{section}
 %% H/T: https://tex.stackexchange.com/a/202047/32270
@@
 unstructured meshes --- by considering high-order isoparametric meshes
-with curved elements. The implementation is highly reliant on accurate
-computational geometry routines for evaluating points on and
-intersecting B\'{e}zier curves and triangles.
+with curved elements.
 \\ \\
@@
 
-The first part is a general-purpose tool for computational physics problems.
-The tool enables solution transfer across two curved meshes.
-Since the tool requires a significant amount of computational geometry, the
-second half focuses on computational geometry. In particular, it considers
-cases where the geometric methods used have seriously degraded accuracy due to
-ill-conditioning.
-
-In computational physics, the problem of solution transfer between meshes
-occurs in several applications. For example, by allowing the underyling
+In this paper, an algorithm for conservative solution transfer between curved
+meshes will be described. This has practical applications to many methods in
+computational physics. For example, by allowing the underyling
 computational domain to change during a simulation, computational
 effort can be focused dynamically to resolve sensitive features
-of a numerical solution. Mesh adaptivity (see, for example,
-\cite{Babuska1978, Peraire1987, Pain2001}), this in-flight change in the mesh,
+of a numerical solution. Mesh adaptivity, this in-flight change in the mesh,
 requires translating the numerical solution from the old mesh to the new,
@@
 methods treat each node in the mesh as a particle and so with each timestep the
-mesh travels \emph{with} the fluid (see, for example, \cite{Hirt1974}).
+mesh travels \emph{with} the fluid.
 However, over (typically limited) time the mesh
@@
 domain must be remeshed or rezoned and the solution must be
-transferred (remapped) onto the new mesh configuration.
-
-When pointwise interpolation is used to transfer a solution, quantities with
-physical meaning (e.g. mass, concentration, energy) may not be conserved.
-To address this, there have been many explorations (for example,
-\cite{Jiao2004, Farrell2009, Farrell2011}) of
-\emph{conservative interpolation} (typically using Galerkin or
-\(L_2\)-minimizing methods). In this work, the author introduces a
-conservative interpolation method for solution transfer between high-order
-meshes. These high-order meshes are typically curved, but not necessarily
-all elements or at all timesteps.
-
-The existing work on solution transfer has considered straight sided meshes,
-which use shape functions that have degree \(p = 1\) to represent solutions
-on each element or so-called superparametric elements (i.e. a linear mesh
-with degree \(p > 1\) shape functions on a regular grid of points).
-However, both to allow for greater geometric flexibility
-and for high order of convergence, this work will consider the case
-of curved isoparametric\footnote{I.e. the degree of the discrete field on the
-mesh is same as the degree of the shape functions that determine the
-mesh.} meshes. Allowing curved geometries is useful since many practical
-problems involve geometries that change over time, such as flapping flight
-or fluid-structure interactions. In addition, high-order CFD methods
-(\cite{Wang2013}) have the ability to produce highly accurate solutions
-with low dissipation and low dispersion error.
-
-\subsection{Actual Intro}
-
-In this chapter, an algorithm for conservative solution transfer between curved
-meshes will be described. This has practical applications to many methods in
-computational physics. Solution transfer is needed when a solution
+transferred (remapped) onto the new mesh configuration. A few scenarios
+where solution transfer is necessary will be considered below
+to motivate the ``black box'' solution transfer algorithm.
+
+Solution transfer is needed when a solution
 (approximated by a discrete field) is known on a \emph{donor} mesh and must
@@
 must be conserved for physical reasons, e.g. mass or energy cannot leave or
-enter the system, hence the focus on \emph{conservative} solution transfer.
-A few scenarios where solution transfer is necessary will be considered below
-to motivate the ``black box'' solution transfer algorithm.
-
-Since solution transfer is so commonly needed in physical applications, this
-problem of conservative interpolation has been considered already for
-straight sided meshes. The \emph{common refinement} approach in
+enter the system, hence the focus on \emph{conservative} solution transfer
+(typically using Galerkin or \(L_2\)-minimizing methods).
+
+When pointwise interpolation is used to transfer a solution, quantities with
+physical meaning (e.g. mass, concentration, energy) may not be conserved.
+To address this, there have been many explorations of
+\emph{conservative interpolation}. Since solution transfer is so commonly
+needed in physical applications, this problem of conservative interpolation
+has been considered already for straight sided meshes.
+However, both to allow for greater
+geometric flexibility and for high order of convergence, this paper will
+consider the case of curved isoparametric\footnote{I.e. the degree of the
+discrete field on the mesh is same as the degree of the shape functions that
+determine the mesh.} meshes. Allowing curved geometries is useful since
+many practical
+problems involve geometries that change over time, such as flapping flight
+or fluid-structure interactions. In addition, high-order CFD methods
+have the ability to produce highly accurate solutions
+with low dissipation and low dispersion error.
+
+The \emph{common refinement} approach in
 \cite{Jiao2004} is used to compare several methods for solution transfer across
@@
 
-\subsubsection{Lagrangian Methods}
+\subsection{Lagrangian Methods}
 
@@
 
-\subsubsection{Remeshing and Adaptivity}
+\subsection{Remeshing and Adaptivity}
 
@@
 
-\subsubsection{High-order Meshes}
+\subsection{High-order Meshes}
 
@@
 
-\subsubsection{Multiphysics and Comparing Methods}
+\subsection{Multiphysics and Comparing Methods}
 
@@
 
-\subsubsection{Local versus Global Transfer}
+\subsection{Local versus Global Transfer}
 
@@
 
-\subsubsection{Limitations}
+\subsection{Limitations}
 
@@
 
-The method described in this work only applies to meshes in \(\reals^2\).
+The method described in this paper only applies to meshes in \(\reals^2\).
 Application to meshes in \(\reals^3\) is a direction for future research,
@@
 
-This work is organized as follows. Section~\ref{sec:preliminaries}
+This paper is organized as follows. Section~\ref{sec:preliminaries}
 establishes common notation and reviews basic results relevant to the
@@
 
+\section{Galerkin Projection}\label{sec:galerkin-projection}
+
+\begin{figure}
+  \includegraphics{main_figure00.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Mesh pair: donor mesh \(\mathcal{M}_D\) and
+    target mesh \(\mathcal{M}_T\).}
+  \label{fig:donor-target-pair}
+\end{figure}
+
+Consider a donor mesh \(\mathcal{M}_D\) with shape function basis
+\(\phi_D^{(j)}\) and a known field \(\bm{q}_D = \sum_j d_j \phi_D^{(j)}\)
+\footnote{This is somewhat a simplification. In the CG case,
+some coefficients will be paired with multiple shape functions, such
+as the coefficient at a vertex node.}
+and a
+target mesh \(\mathcal{M}_T\) with shape function basis \(\phi_T^{(j)}\)
+(Figure~\ref{fig:donor-target-pair}).
+Each shape function \(\phi\) corresponds to a
+given isoparametric curved element (see Section~\ref{sec:curved-elements})
+\(\mathcal{T}\) in one of these meshes and has
+\(\operatorname{supp}(\phi) = \mathcal{T}\).
+Additionally, the shape functions are polynomial degree \(p\) (see
+Section~\ref{subsec:shape-functions} for a discussion of shape functions),
+but the degree of the donor mesh need not be the same as that of the
+target mesh. We assume that both meshes cover the same domain \(\Omega \subset
+\reals^2\), however we really only require the donor mesh to cover the
+target mesh.
+
+We seek the \(L_2\)-optimal interpolant \(\bm{q}_T = \sum_j t_j \phi_T^{(j)}\):
+\begin{equation}
+\left \lVert \bm{q}_T - \bm{q}_D \right \rVert_2 =
+\min_{\bm{q} \in \mathcal{V}_T}
+\left \lVert \bm{q} - \bm{q}_D \right \rVert_2
+\end{equation}
+where \(\mathcal{V}_T = \operatorname{Span}_j\left\{\phi_T^{(j)}\right\}\)
+is the function space defined on the target mesh. Since this is optimal in
+the \(L_2\) sense, by differentiating with respect to each \(t_j\) in
+\(\bm{q}_T\) we find the weak form:
+\begin{equation}
+\int_{\Omega} \bm{q}_D \phi_T^{(j)} \, dV =
+  \int_{\Omega} \bm{q}_T \phi_T^{(j)} \, dV, \qquad \text{for all } j.
+\end{equation}
+If the constant function \(1\) is contained in \(\mathcal{V}_T\),
+conservation follows from the weak form and linearity of the integral
+\begin{equation}
+\int_{\Omega} \bm{q}_D \, dV =
+  \int_{\Omega} \bm{q}_T \, dV.
+\end{equation}
+Expanding \(\bm{q}_D\) and \(\bm{q}_T\) with respect to their coefficients
+\(\bm{d}\) and \(\bm{t}\), the weak form gives rise to a linear system
+\begin{equation}\label{eq:weak-form-system}
+M_T \bm{t} = M_{TD} \bm{d}.
+\end{equation}
+Here \(M_T\) is the mass matrix for
+\(\mathcal{M}_T\) given by
+\begin{equation}
+\left(M_T\right)_{ij} = \int_{\Omega} \phi_T^{(i)} \phi_T^{(j)} \, dV.
+\end{equation}
+In the discontinuous Galerkin case, \(M_T\) is block diagonal with blocks
+that correspond to each element, so \eqref{eq:weak-form-system} can be
+solved locally on each element \(\mathcal{T}\) in the target mesh. By
+construction, \(M_T\) is symmetric and sparse since \(\left(M_T\right)_{ij}\)
+will be \(0\) unless \(\phi_T^{(i)}\) and \(\phi_T^{(j)}\) are supported
+on the same element \(\mathcal{T}\). In the continuous case, \(M_T\) is
+globally coupled since coefficients corresponding to boundary nodes interact
+with multiple elements. The matrix \(M_{TD}\) is a ``mixed'' mass matrix
+between the target and donor meshes:
+\begin{equation}
+\left(M_{TD}\right)_{ij} = \int_{\Omega} \phi_T^{(i)} \phi_D^{(j)} \, dV.
+\end{equation}
+Boundary conditions can be imposed on the system by fixing some coefficients,
+but that is equivalent to removing some of the basis functions which may
+in term make the projection non-conservative. This is because the removed
+basis functions may have been used in \(1 = \sum_j u_j \phi_{T}^{(j)}\).
+
+Computing \(M_T\) is fairly straightforward since the (bidirectional) mapping
+from elements \(\mathcal{T}\) to basis functions \(\phi_T^{(j)}\) supported
+on those elements is known. When using shape functions in the
+global coordinates basis (see Section~\ref{subsec:shape-functions}), the
+integrand \(F = \phi_T^{(i)} \phi_T^{(j)}\) will be a polynomial of degree
+\(2p\) on \(\reals^2\). The domain of integration \(\mathcal{T}
+= b\left(\utri\right)\) is the image of a (degree \(p\)) map \(b(s, t)\)
+from the unit triangle. Using substitution
+\begin{equation}\label{eq:mass-mat-subst}
+\int_{b\left(\utri\right)} F(x, y) \, dx \, dy =
+  \int_{\utri} \det(Db) F\left(x(s, t), y(s, t)\right) \, ds \, dt
+\end{equation}
+(we know the map preserves orientation, i.e. \(\det(Db)\) is positive).
+Once transformed this way, a quadrature rule on the unit
+triangle (\cite{Dunavant1985}) can be used.
+
+On the other hand, computing \(M_{TD}\) is significantly more
+challenging. This requires solving both a geometric problem ---
+finding the region to integrate over --- and an analytic
+problem --- computing the integrals. The integration can be done with
+a quadrature rule, though finding this region is significantly
+more difficult.
+
+\section{Common Refinement}
+
+\begin{figure}
+  \includegraphics{main_figure02.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{All donor elements that cover a target element}
+  \label{fig:target-elt-all-matching}
+\end{figure}
+
+Rather than computing \(M_{TD}\), the right-hand side
+of~\eqref{eq:weak-form-system} can be computed directly via
+\begin{equation}\label{eq:lumped-mixed-mass-matrix}
+\left(M_{TD} \bm{d}\right)_j = \int_{\Omega} \phi_T^{(j)} \bm{q}_D \, dV.
+\end{equation}
+Any given \(\phi\) is supported on an element \(\mathcal{T}\) in the
+target mesh. Since \(\bm{q}_D\) is piecewise defined over each element
+\(\mathcal{T}'\) in the donor mesh, the
+integral~\eqref{eq:lumped-mixed-mass-matrix} may be problematic.
+In the continuous Galerkin case, \(\bm{q}_D\) need not be differentiable
+across \(\mathcal{T}\) and in the discontinuous Galerkin case,
+\(\bm{q}_D\) need not even be continuous. This necessitates a
+partitioning of the domain:
+\begin{equation}
+\int_{\Omega} \phi \, \bm{q}_D \, dV =
+  \int_{\mathcal{T}} \phi \, \bm{q}_D \, dV =
+  \sum_{\mathcal{T}' \in \mathcal{M}_D} \int_{\mathcal{T} \cap \mathcal{T}'}
+    \phi \left.\bm{q}_D\right|_{\mathcal{T}'} \, dV.
+\end{equation}
+In other words, the integral over \(\mathcal{T}\) splits into integrals
+over intersections \(\mathcal{T} \cap \mathcal{T}'\) for all
+\(\mathcal{T}'\) in the donor mesh that intersect \(\mathcal{T}\)
+(Figure~\ref{fig:target-elt-all-matching}). Since both \(\phi\) and
+\(\left.\bm{q}_D\right|_{\mathcal{T}'}\) are polynomials on
+\(\mathcal{T} \cap \mathcal{T}'\), the integrals will be exact when
+using a quadrature scheme of an appropriate degree of accuracy.
+Without partitioning \(\mathcal{T}\), the integrand is not a polynomial
+(in fact, possibly not smooth), so the quadrature cannot be exact.
+
+In order to compute \(M_{TD} \bm{d}\), we'll need to compute the
+\emph{common refinement}, i.e. an intermediate mesh that contains
+both the donor and target meshes. This will consist of all non-empty
+\(\mathcal{T} \cap \mathcal{T}'\) as \(\mathcal{T}\) varies over
+elements of the target mesh and \(\mathcal{T}'\) over elements of the
+donor mesh. This requires solving three specific subproblems:
+\begin{itemize}
+%% H/T: https://tex.stackexchange.com/a/6086/32270
+\itemsep 0em
+\item Forming the region(s) of intersection between two elements that
+  are B\'{e}zier triangles.
+\item Finding all pairs of elements, one each from the target and donor mesh,
+  that intersect.
+\item Numerically integrating over a region of intersection between two
+  elements.
+\end{itemize}
+The first subproblem has been addressed in
+Section~\ref{subsec:intersect-bez-tri}
+and the curved polygon region(s) of intersection have been described
+in Section~\ref{subsec:curved-polygons}. The second will be considered
+in Section~\ref{subsec:advancing-front} and the third in
+Section~\ref{subsec:integration-on-curved} below.
+
+\subsection{Advancing Front}\label{subsec:advancing-front}
+
+\begin{figure}
+  \includegraphics{main_figure13.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Brute force search for a donor element \(\mathcal{T}'\) that matches
+    a fixed target element \(\mathcal{T}\).}
+  \label{fig:target-elt-brute-force}
+\end{figure}
+
+We seek to identify all pairs \(\mathcal{T}\) and \(\mathcal{T}'\) of
+intersecting target and donor elements. The na\"{i}ve approach just
+considers every pair
+of elements and takes \(\bigO{\left|\mathcal{M}_D\right|
+\left|\mathcal{M}_T\right|}\) to complete.\footnote{For a mesh \(\mathcal{M}\),
+the expression \(\left|\mathcal{M}\right|\) represents the number of elements
+in the mesh.} Taking after \cite{Farrell2011}, we can do much better than this
+quadratic time search. In fact, we can compute all integrals in
+\(\bigO{\left|\mathcal{M}_D\right| + \left|\mathcal{M}_T\right|}\).
+First, we fix an element of the target mesh and perform a brute-force search
+to find an intersecting element in the donor mesh
+(Figure~\ref{fig:target-elt-brute-force}). This has worst-case time
+\(\bigO{\left|\mathcal{M}_D\right|}\).
+
+\begin{figure}
+  \includegraphics{main_figure14.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{All donor elements \(\mathcal{T}'\) that cover a target element
+    \(\mathcal{T}\), with an extra layer of neighbors in the donor mesh
+    that \emph{do not} intersect \(\mathcal{T}\).}
+  \label{fig:target-elt-overlap-extra-layer}
+\end{figure}
+
+Once we have such a match, we use the connectivity graph of the
+donor mesh to perform a breadth first search
+for neighbors that also intersect the target
+element \(\mathcal{T}\) (Figure~\ref{fig:target-elt-overlap-extra-layer}).
+This search takes \(\bigO{1}\) time. It's also worthwhile to keep the first
+layer of donor elements that don't intersect \(\mathcal{T}\) because they are
+more likely to intersect the neighbors of \(\mathcal{T}\)\footnote{In the
+very unlikely case that the boundary of \(\mathcal{T}\)
+\emph{exactly matches} the boundaries of the donor elements that cover it,
+\emph{none} of the overlapping donor elements can intersect the neighbors of
+\(\mathcal{T}\) so the first layer of non-intersected donor
+elements must be considered.}. Using the list of intersected elements, a
+neighbor of \(\mathcal{T}\) can find a donor element it intersects with in
+\(\bigO{1}\) time (Figure~\ref{fig:target-elt-neighbor}).
+As seen, after our \(\bigO{\left|\mathcal{M}_D\right|}\)
+initial brute-force search, the localized intersections for each
+target element \(\mathcal{T}\) take
+\(\bigO{1}\) time. So together, the process takes
+\(\bigO{\left|\mathcal{M}_D\right| + \left|\mathcal{M}_T\right|}\).
+
+For special cases, e.g. ALE methods, the initial brute-force search
+can be reduced to \(\bigO{1}\). This could be enabled by tracking
+the remeshing process so a correspondence already exists. If a full
+mapping from donor to target mesh exists, the process of computing
+\(M_T\) and \(M_{TD} \bm{d}\) can be fully parallelized across
+elements of the target mesh, or even across shape functions
+\(\phi_T^{(j)}\).
+
+\begin{figure}
+  \includegraphics{main_figure15.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{First match between a neighbor of the previously considered
+    target element and all the donor elements that match the
+    previously considered target element.}
+  \label{fig:target-elt-neighbor}
+\end{figure}
+
+\subsection{Integration over Curved Polygons}
+\label{subsec:integration-on-curved}
+
+In order to numerically evaluate integrals of the form
+\begin{equation}
+\int_{\mathcal{T}_0 \cap \mathcal{T}_1} F(x, y) \, dV
+\end{equation}
+we must have a quadrature rule on these curved polygon
+(Section~\ref{subsec:curved-polygons}) intersections
+\(\mathcal{T}_0 \cap \mathcal{T}_1\).
+To do this, we transform the integral into several line integrals
+via Green's theorem and then use an exact Gaussian quadrature to
+evaluate them. Throughout this section we'll assume the integrand
+is of the form \(F = \phi_0 \phi_1\) where each \(\phi_j\) is a shape
+function on \(\mathcal{T}_j\). In addition, we'll refer to the two
+B\'{e}zier maps that define the elements being intersected:
+\(\mathcal{T}_0 = b_0\left(\utri\right)\) and
+\(\mathcal{T}_1 = b_1\left(\utri\right)\).
+
+\begin{figure}
+  \includegraphics{polygon_vs_curved.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Comparing the relative error for the computed area of a quadratic
+    B\'{e}zier triangle. In one method, the curved boundary is used and the
+    result is correct to machine precision. In the other, the curved edges
+    are approximated by polygonal paths.}
+  \label{fig:polygon-vs-curved}
+\end{figure}
+
+\begin{figure}
+  \includegraphics
+      {polygon_vs_curved_intersection.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Comparing the relative error for the computed area of the
+    intersection of two quadratic B\'{e}zier triangles. In one method, the
+    intersection boundary is fully specified as the union of B\'{e}zier curve
+    segments and the area is computed correctly to machine precision. In the
+    other, the curved edges are approximated by polygonal paths and the
+    intersection of the resulting polygons is computed.}
+  \label{fig:polygon-vs-curved-intersection}
+\end{figure}
+
+First a discussion of a method not used. A somewhat simple approach would be
+be to use polygonal approximation. I.e. approximate the boundary of each
+B\'{e}zier triangle with line segments, intersect the resulting polygons,
+triangulate the intersection polygon(s) and then numerically integrate
+on each triangulated cell. However, this approach is prohibitively inefficient.
+For example, consider the curved polygon in
+Figure~\ref{fig:polygon-vs-curved}. Computing the area of \(\mathcal{P}\)
+can be done via an integral: \(\int_{\mathcal{P}} 1 \, dV\).
+By using the actual curved boundary, this integral can be computed with
+relative error (the dashed line in the bottom right subplot) on the order
+of machine precision \(\bigO{\mach}\). On the other hand, approximating
+each side of \(\mathcal{P}\) with \(N\) line segments, the relative error is
+\(\bigO{1/N^2}\). (For example, if \(N = 2\) an edge curve \(b(s, 0)\) would be
+replaced by segments connecting \(b(0, 0), b(1/2, 0)\) and \(b(1, 0)\), i.e.
+\(N + 1\) equally spaced parameters.) This means that in order to perform as
+well as an \emph{exact} quadrature used in the curved case, we'd
+need \(N = \bigO{1/\sqrt{\mach}}\). Compute the area of \(\mathcal{P}\)
+in this way assumes that \(\mathcal{P}\) is already known.
+If instead only the B\'{e}zier triangles in the intersection are known, as
+in Figure~\ref{fig:polygon-vs-curved-intersection}, the polygonal approach
+suffers from the same inefficiency.
+
+Since polygonal approximation is prohibitively expensive,
+we work directly with curved edges and compute integrals on a regular
+domain via substitution.
+If two B\'{e}zier triangles intersect with positive measure, then
+the region of intersection is one or more disjoint curved polygons:
+\(\mathcal{T}_0 \cap \mathcal{T}_1 = \mathcal{P}\) or
+\(\mathcal{T}_0 \cap \mathcal{T}_1 = \mathcal{P} \cup
+\mathcal{P}' \cup \cdots\).
+The second case can be handled in the same way as the first by handling each
+disjoint region independently:
+\begin{equation}
+\int_{\mathcal{T}_0 \cap \mathcal{T}_1} F(x, y) \, dV =
+  \int_{\mathcal{P}} F(x, y) \, dV +
+  \int_{\mathcal{P}'} F(x, y) \, dV + \cdots.
+\end{equation}
+Each curved polygon \(\mathcal{P}\) is defined by its boundary, a
+piecewise smooth parametric curve:
+\begin{equation}
+\partial \mathcal{P} = C_1 \cup \cdots \cup C_n.
+\end{equation}
+This can be thought of as a polygon with \(n\)-sides that happens to
+have curved edges.
+
+Quadrature rules for straight sided polygons have been
+studied (\cite{Mousavi2009}) though they are not in wide use. Even
+if a polygonal quadrature rule was to be employed, a map would need to be
+established from a reference polygon onto the curved edges. This map
+could then be used with a change of coordinates to move the integral
+from the curved polygon to the reference polygon. The problem of extending
+a mapping from a boundary to an entire domain has been studied as
+transfinite interpolation
+(\cite{chenin:tel-00284680, Gordon1982, Perronnet1998}),
+barycentric coordinates (\cite{Wachspress1975}) or mean value coordinates
+(\cite{Floater2003}). However, these maps aren't typically suitable for
+numerical integration because they are either not bijective or increase the
+degree of the edges.
+
+\begin{figure}
+  \includegraphics{main_figure11.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Curved polygon tessellation, done by introducing diagonals
+    from a single vertex node.}
+  \label{fig:tessellated-curved-polygon}
+\end{figure}
+
+Since simple and well established quadrature rules do exist for triangles,
+a valid approach would be
+to tessellate a curved polygon into valid B\'{e}zier triangles
+(Figure~\ref{fig:tessellated-curved-polygon}) and then use substitution as
+in~\eqref{eq:mass-mat-subst}. However, tessellation is challenging for both
+theoretical and computational reasons.
+Theoretical: it's not even clear if an arbitrary curved polygon \emph{can}
+be tessellated into B\'{e}zier triangles. Computational: the placement
+of diagonals and potential introduction of interior nodes is very
+complex in cases where the curved polygon is nonconvex. What's more,
+the curved polygon is given only by the boundary, so higher degree triangles
+(i.e. cubic and above) introduced during tessellation would need to place
+interior control points without causing the triangle to invert. To get a
+sense for these challenges, note how the ``simple'' introduction of
+diagonals in Figure~\ref{fig:bad-tessellation-required} leads to one
+inverted element (the gray element) and another element with area outside
+of the curved polygon (the yellow element). Inverted B\'{e}zier triangles
+are problematic because the accompanying mapping leaves the boundary
+established by the edge curves. For example,
+if the tessellation of \(\mathcal{P}\) contains an inverted
+B\'{e}zier triangle \(\mathcal{T}_2 = b\left(\utri\right)\) then we'll
+need to numerically integrate
+\begin{equation}
+\int_{\mathcal{T}_2} \phi_0 \phi_1 \, dx \, dy =
+  \int_{\utri} \left|\det(Db)\right| \left(\phi_0 \circ b\right)
+  \left(\phi_1 \circ b\right) \, ds \, dt.
+\end{equation}
+If the shape functions are from the pre-image basis (see
+Section~\ref{subsec:shape-functions}), then \(\phi_0\)
+will not be defined at \(b(s, t) \not\in \mathcal{T}_0\) (similarly for
+\(\phi_1\)). Additionally, the absolute value in \(\left|\det(Db)\right|\)
+makes the integrand non-smooth since for inverted elements
+\(\det(Db)\) takes both signs. If the shape functions are from the
+global coordinates basis, then tessellation can be used via an
+application of Lemma~\ref{lemma:bad-triangle}, however this involves
+more computation than just applying Green's theorem along
+\(\partial \mathcal{P}\). By applying the lemma, inverted elements may
+be used in a tessellation, for example by introducing artificial
+diagonals from a vertex as in Figure~\ref{fig:tessellated-curved-polygon}.
+In the global coordinates basis, \(F = \phi_0 \phi_1\) \emph{can}
+be evaluated for points in an inverted element that leave
+\(\mathcal{T}_0\) or \(\mathcal{T}_1\).
+
+\begin{figure}
+  \includegraphics{main_figure16.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Curved polygon intersection that can't be tessellated
+    (with valid B\'{e}zier triangles) by introducing diagonals.}
+  \label{fig:bad-tessellation-required}
+\end{figure}
+
+Instead, we focus on a Green's theorem based approach.
+Define horizontal and vertical antiderivatives
+\(H, V\) of the integrand \(F\) such that \(H_x = V_y = F\).
+We make these \emph{unique} by imposing the
+extra condition that \(H(0, y) \equiv V(x, 0) \equiv 0\).
+This distinction is arbitrary, but in order to \emph{evaluate}
+\(H\) and \(V\), the univariate functions \(H(0, y)\) and \(V(x, 0)\)
+must be specified.
+Green's theorem tells us that
+\begin{equation}
+\int_{\mathcal{P}} 2 F \, dV =
+\int_{\mathcal{P}} H_x + V_y \, dV =
+\oint_{\partial \mathcal{P}} H \, dy - V \, dx =
+\sum_j \int_{C_j} H \, dy - V \, dx.
+\end{equation}
+For a given curve \(C\) with components \(x(r), y(r)\)
+defined on the unit interval, this amounts to having
+to integrate
+\begin{equation}
+G(r) = H(x(r), y(r)) y'(r) - V(x(r), y(r)) x'(r).
+\end{equation}
+To do this, we'll use Gaussian
+quadrature with degree of accuracy sufficient to cover the degree
+of \(G(r)\).
+
+If the shape functions are in the global coordinates basis
+(Section~\ref{subsec:shape-functions}), then \(G\) will also be a polynomial.
+This is because for these shape functions \(F = \phi_0 \phi_1\) will be
+polynomial on \(\reals^2\) and so will \(H\) and \(V\) and since each curve
+\(C\) is a B\'{e}zier curve segment, the components are also polynomials.
+If the shape functions are in the pre-image basis, then \(F\) won't in general
+be polynomial, hence the quadrature rules can only be approximate.
+
+To evaluate \(G\), we must also evaluate \(H\) and \(V\) numerically.
+For example, since \(H(0, y) \equiv 0\),
+the fundamental theorem of calculus tells us that
+\(H\left(\alpha, \beta\right) = \int_0^{\alpha} F\left(x, \beta\right) \, dx\).
+To compute this integral via Gaussian quadrature
+\begin{equation}
+H\left(\alpha, \beta\right) \approx \frac{\alpha}{2} \sum_j w_j
+  F\left(\frac{\alpha}{2} (x_j + 1), \beta\right)
+\end{equation}
+we must be able to evaluate \(F\) for
+points on the line \(y = \beta\) for \(x\) between \(0\) and \(\alpha\). If
+the shape functions are from the pre-image basis, it may not even be possible
+to evaluate \(F\) for such points. Since \(\left[\begin{array}{c c} \alpha &
+\beta \end{array}\right]^T\) is on the boundary of \(\mathcal{P}\), without
+loss of generality
+assume it is on the boundary of \(\mathcal{T}_0\). Thus, for some elements
+(e.g. if the point is on the bottom of the element), points
+\(\left[\begin{array}{c c} \nu & \beta \end{array}\right]^T\) may not be
+in \(\mathcal{T}_0\). Since \(\operatorname{supp}(\phi_0) = \mathcal{T}_0\),
+we could take \(\phi_0(\nu, \beta) = 0\), but this would make the integrand
+non-smooth and so the accuracy of the \emph{exact} quadrature would be
+lost. But extending \(\phi_0 = \widehat{\phi}_0 \circ b_0^{-1}\) outside
+of \(\mathcal{T}_0\) may be impossible: even though \(b_0\) is bijective on
+\(\utri\) it may be many-to-one elsewhere hence \(b_0^{-1}\) can't be
+reliably extended outside of \(\mathcal{T}_0\).
+
+Even if the shape functions are from the global coordinates basis,
+setting \(H(0, y) \equiv 0\) may introduce quadrature points that
+are very far from \(\mathcal{P}\). This can be somewhat addressed by using
+\(H(m, y) \equiv 0\) for a suitably chosen \(m\) (e.g. the minimum
+\(x\)-value in \(\mathcal{P}\)). Then we have
+\(H\left(\alpha, \beta\right) = \int_m^{\alpha} F\left(x, \beta\right) \, dx\).
+
+\section{Numerical Experiments}
+
+\begin{figure}
+  \includegraphics{main_figure30.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Some example meshes used during the numerical
+    experiments; the donor meshs is on the left / blue and the target
+    mesh is on the right / green. These meshes are the cubic approximations
+    of each domain and have been refined twice.}
+  \label{fig:meshes-used-refined}
+\end{figure}
+
+A numerical experiment was performed to investigate the observed order
+of convergence. Three pairs of random meshes were generated, the donor
+on a square of width \(17 / 8\) centered at the origin
+and the target on the unit disc. These domains were chosen intentionally so
+that the target mesh was completely covered by the donor mesh and the
+boundaries did not accidentally introduce ill-conditioned intersection between
+elements. The pairs were linear, quadratic and
+cubic approximations of the domains. The convergence test was done by
+refining each pair of meshes four times and performing solution transfer
+at each level. Figure~\ref{fig:meshes-used-refined} shows the cubic
+pair of meshes after two refinements.
+
+\begin{figure}
+  \includegraphics{main_figure25.pdf}
+  \centering
+  \captionsetup{width=.75\linewidth}
+  \caption{Convergence results for scalar fields on three pairs of related
+    meshes: a linear, quadratic and cubic mesh of the same domain.}
+  \label{fig:composite-errors}
+\end{figure}
+
+Taking after \cite{Farrell2011}, we transfer three
+discrete fields in the discontinuous Galerkin (DG) basis.
+Each field is derived from one of the smooth scalar functions
+\begin{align}
+\zeta_1(x, y) &= 5 y^3 + x^2 + 2y + 3 \\
+\zeta_2(x, y) &= \exp\left(x^2\right) + 2y \\
+\zeta_3(x, y) &= \sin(x) + \cos(y).
+\end{align}
+For a given mesh size \(h\), we expect that on a degree \(p\) isoparametric
+mesh our solution transfer will have \(\bigO{h^{p + 1}}\) errors. To measure
+the rate of convergence:
+\begin{itemize}
+\itemsep 0em
+\item Choose a mesh pair \(\mathcal{M}_D\), \(\mathcal{M}_T\) and
+a known function \(\zeta(x, y)\).
+\item Refine the meshes recursively, starting with
+  \(\mathcal{M}_D^{(0)} = \mathcal{M}_D\),
+  \(\mathcal{M}_T^{(0)} = \mathcal{M}_T\).
+\item Create meshes
+\(\mathcal{M}_D^{(j)}\) and \(\mathcal{M}_T^{(j)}\) from
+\(\mathcal{M}_D^{(j - 1)}\)
+and \(\mathcal{M}_T^{(j - 1)}\) by subdividing each curved
+element into four elements.
+\item Approximate \(\zeta\) by a discrete field: the nodal
+interpolant on the donor mesh \(\mathcal{M}_D^{(j)}\). The
+nodal interpolant is constructed by evaluating \(\zeta\) at the
+nodes \(\bm{n}_j\) corresponding to each shape function:
+\begin{equation}
+\bm{f}_j = \sum_i \zeta\left(\bm{n}_i\right) \phi_D^{(i)}.
+\end{equation}
+\item Transfer \(\bm{f}_j\) to the discrete field \(\bm{g}_j\) on
+the target mesh  \(\mathcal{M}_T^{(j)}\).
+\item Compute the relative error on \(\mathcal{M}_T^{(j)}\):
+\(E_j = \| \bm{g}_j - \zeta \|_2 / \| \zeta \|_2\) (here \(\| \cdot \|_2\)
+is the \(L_2\) norm on the target mesh).
+
+We should instead be measuring \(\| \bm{g}_j - \bm{f}_j \|_2 /
+\| \bm{f}_j \|_2\), but \(E_j\) is much easier to
+compute for \(\zeta(x, y)\) that are straightforward to evaluate.
+Due to the triangle inequality \(E_j\) can be a reliable proxy
+for the actual projection error, though when
+\(\| \bm{f}_j - \zeta \|_2\) becomes too large it will dominate
+the error and no convergence will be observed.
+\end{itemize}
+
+Convergence results are shown in Figure~\ref{fig:composite-errors}
+and confirm the expected orders. Since \(\zeta_1\) is a cubic polynomial,
+the solution transfer on the cubic mesh should be \emph{exact}, so there
+is a certain minimum threshold that can be reached.
+
+\section{Conclusion}
+
+This paper has described a method for conservative interpolation
+between curved meshes. The transfer process conserves globally
+to machine precision since we can use exact quadratures for all
+integrals. The primary source of error comes from solving the linear
+system with the mass matrix for the target mesh. This allows
+less restrictive usage of mesh adaptivity, which can make computations
+more efficient. Additionally, having a global transfer algorithm
+allows for remeshing to be done less frequently.
+
+The algorithm breaks down into three core subproblems: B\'{e}zier triangle
+intersection, an advancing front for intersecting elements and
+integration on curved polygons. The inherently local nature of the
+advancing front allows the algorithm to be parallelized via domain
+decomposition with little data shared between processes. By
+restricting integration to the intersection of elements from the
+target and donor meshes, the algorithm can accurately transfer
+both continuous and discontinuous fields.
+
+\subsection{Future Work}
+
+As mentioned in the preceding chapters, there are several research
+directions possible to build upon the solution transfer algorithm.
+The usage of Green's theorem nicely extends to \(\reals^3\) via
+Stoke's theorem, but the B\'{e}zier triangle intersection algorithm
+is specific to \(\reals^2\). The equivalent B\'{e}zier tetrahedron
+intersection algorithm is significantly more challenging.
+
+The restriction to shape functions from the global coordinates basis
+is a symptom of the method and not of the inherent problem. The
+pre-image basis has several appealing properties, for example
+this basis can be precomputed on \(\utri\). The problem of a
+valid tessellation of a curved polygon warrants more exploration.
+Such a tessellation algorithm would enable usage of the pre-image
+basis.
+
+The usage of the global coordinates basis does have some benefits.
+In particular, the product of shape functions from different meshes
+is still a polynomial in \(\reals^2\). This means that we could
+compute the coefficients of \(F = \phi_0 \phi_1\) directly and
+use them to evaluate the antiderivatives \(H\) and \(V\) rather
+than using the fundamental theorem of calculus. Even if this
+did not save any computation, it may still be preferred over
+the FTC approach because it would remove the usage of quadrature
+points outside of the domain \(\mathcal{P}\).
+
+\bibliography{paper}
+\bibliographystyle{alpha}
+
+\appendix
+
 \section{B\'{e}zier Intersection Problems}\label{sec:bezier-intersection}
@@
 The problem of intersecting two B\'{e}zier curves is a core building
-block for intersecting two B\'{e}zier triangles in \(\reals^2\)
+block for intersecting two B\'{e}zier triangles in \(\reals^2\).
 Since a curve is an algebraic variety of dimension one,
@@
 
-In the implementation for this work, the B\'{e}zier subdivision
+In the implementation for this paper, the B\'{e}zier subdivision
 algorithm is used.
@@
 
-\section{Galerkin Projection}\label{sec:galerkin-projection}
-
-\begin{figure}
-  \includegraphics{main_figure00.pdf}
-  \centering
-  \captionsetup{width=.75\linewidth}
-  \caption{Mesh pair: donor mesh \(\mathcal{M}_D\) and
-    target mesh \(\mathcal{M}_T\).}
-  \label{fig:donor-target-pair}
-\end{figure}
-
-Consider a donor mesh \(\mathcal{M}_D\) with shape function basis
-\(\phi_D^{(j)}\) and a known field \(\bm{q}_D = \sum_j d_j \phi_D^{(j)}\)
-\footnote{This is somewhat a simplification. In the CG case,
-some coefficients will be paired with multiple shape functions, such
-as the coefficient at a vertex node.}
-and a
-target mesh \(\mathcal{M}_T\) with shape function basis \(\phi_T^{(j)}\)
-(Figure~\ref{fig:donor-target-pair}).
-Each shape function \(\phi\) corresponds to a
-given isoparametric curved element (see Section~\ref{sec:curved-elements})
-\(\mathcal{T}\) in one of these meshes and has
-\(\operatorname{supp}(\phi) = \mathcal{T}\).
-Additionally, the shape functions are polynomial degree \(p\) (see
-Section~\ref{subsec:shape-functions} for a discussion of shape functions),
-but the degree of the donor mesh need not be the same as that of the
-target mesh. We assume that both meshes cover the same domain \(\Omega \subset
-\reals^2\), however we really only require the donor mesh to cover the
-target mesh.
-
-We seek the \(L_2\)-optimal interpolant \(\bm{q}_T = \sum_j t_j \phi_T^{(j)}\):
-\begin{equation}
-\left \lVert \bm{q}_T - \bm{q}_D \right \rVert_2 =
-\min_{\bm{q} \in \mathcal{V}_T}
-\left \lVert \bm{q} - \bm{q}_D \right \rVert_2
-\end{equation}
-where \(\mathcal{V}_T = \operatorname{Span}_j\left\{\phi_T^{(j)}\right\}\)
-is the function space defined on the target mesh. Since this is optimal in
-the \(L_2\) sense, by differentiating with respect to each \(t_j\) in
-\(\bm{q}_T\) we find the weak form:
-\begin{equation}
-\int_{\Omega} \bm{q}_D \phi_T^{(j)} \, dV =
-  \int_{\Omega} \bm{q}_T \phi_T^{(j)} \, dV, \qquad \text{for all } j.
-\end{equation}
-If the constant function \(1\) is contained in \(\mathcal{V}_T\),
-conservation follows from the weak form and linearity of the integral
-\begin{equation}
-\int_{\Omega} \bm{q}_D \, dV =
-  \int_{\Omega} \bm{q}_T \, dV.
-\end{equation}
-Expanding \(\bm{q}_D\) and \(\bm{q}_T\) with respect to their coefficients
-\(\bm{d}\) and \(\bm{t}\), the weak form gives rise to a linear system
-\begin{equation}\label{eq:weak-form-system}
-M_T \bm{t} = M_{TD} \bm{d}.
-\end{equation}
-Here \(M_T\) is the mass matrix for
-\(\mathcal{M}_T\) given by
-\begin{equation}
-\left(M_T\right)_{ij} = \int_{\Omega} \phi_T^{(i)} \phi_T^{(j)} \, dV.
-\end{equation}
-In the discontinuous Galerkin case, \(M_T\) is block diagonal with blocks
-that correspond to each element, so \eqref{eq:weak-form-system} can be
-solved locally on each element \(\mathcal{T}\) in the target mesh. By
-construction, \(M_T\) is symmetric and sparse since \(\left(M_T\right)_{ij}\)
-will be \(0\) unless \(\phi_T^{(i)}\) and \(\phi_T^{(j)}\) are supported
-on the same element \(\mathcal{T}\). In the continuous case, \(M_T\) is
-globally coupled since coefficients corresponding to boundary nodes interact
-with multiple elements. The matrix \(M_{TD}\) is a ``mixed'' mass matrix
-between the target and donor meshes:
-\begin{equation}
-\left(M_{TD}\right)_{ij} = \int_{\Omega} \phi_T^{(i)} \phi_D^{(j)} \, dV.
-\end{equation}
-Boundary conditions can be imposed on the system by fixing some coefficients,
-but that is equivalent to removing some of the basis functions which may
-in term make the projection non-conservative. This is because the removed
-basis functions may have been used in \(1 = \sum_j u_j \phi_{T}^{(j)}\).
-
-Computing \(M_T\) is fairly straightforward since the (bidirectional) mapping
-from elements \(\mathcal{T}\) to basis functions \(\phi_T^{(j)}\) supported
-on those elements is known. When using shape functions in the
-global coordinates basis (see Section~\ref{subsec:shape-functions}), the
-integrand \(F = \phi_T^{(i)} \phi_T^{(j)}\) will be a polynomial of degree
-\(2p\) on \(\reals^2\). The domain of integration \(\mathcal{T}
-= b\left(\utri\right)\) is the image of a (degree \(p\)) map \(b(s, t)\)
-from the unit triangle. Using substitution
-\begin{equation}\label{eq:mass-mat-subst}
-\int_{b\left(\utri\right)} F(x, y) \, dx \, dy =
-  \int_{\utri} \det(Db) F\left(x(s, t), y(s, t)\right) \, ds \, dt
-\end{equation}
-(we know the map preserves orientation, i.e. \(\det(Db)\) is positive).
-Once transformed this way, a quadrature rule on the unit
-triangle (\cite{Dunavant1985}) can be used.
-
-On the other hand, computing \(M_{TD}\) is significantly more
-challenging. This requires solving both a geometric problem ---
-finding the region to integrate over --- and an analytic
-problem --- computing the integrals. The integration can be done with
-a quadrature rule, though finding this region is significantly
-more difficult.
-
-\section{Common Refinement}
-
-\begin{figure}
-  \includegraphics{main_figure02.pdf}
-  \centering
-  \captionsetup{width=.75\linewidth}
-  \caption{All donor elements that cover a target element}
-  \label{fig:target-elt-all-matching}
-\end{figure}
-
-Rather than computing \(M_{TD}\), the right-hand side
-of~\eqref{eq:weak-form-system} can be computed directly via
-\begin{equation}\label{eq:lumped-mixed-mass-matrix}
-\left(M_{TD} \bm{d}\right)_j = \int_{\Omega} \phi_T^{(j)} \bm{q}_D \, dV.
-\end{equation}
-Any given \(\phi\) is supported on an element \(\mathcal{T}\) in the
-target mesh. Since \(\bm{q}_D\) is piecewise defined over each element
-\(\mathcal{T}'\) in the donor mesh, the
-integral~\eqref{eq:lumped-mixed-mass-matrix} may be problematic.
-In the continuous Galerkin case, \(\bm{q}_D\) need not be differentiable
-across \(\mathcal{T}\) and in the discontinuous Galerkin case,
-\(\bm{q}_D\) need not even be continuous. This necessitates a
-partitioning of the domain:
-\begin{equation}
-\int_{\Omega} \phi \, \bm{q}_D \, dV =
-  \int_{\mathcal{T}} \phi \, \bm{q}_D \, dV =
-  \sum_{\mathcal{T}' \in \mathcal{M}_D} \int_{\mathcal{T} \cap \mathcal{T}'}
-    \phi \left.\bm{q}_D\right|_{\mathcal{T}'} \, dV.
-\end{equation}
-In other words, the integral over \(\mathcal{T}\) splits into integrals
-over intersections \(\mathcal{T} \cap \mathcal{T}'\) for all
-\(\mathcal{T}'\) in the donor mesh that intersect \(\mathcal{T}\)
-(Figure~\ref{fig:target-elt-all-matching}). Since both \(\phi\) and
-\(\left.\bm{q}_D\right|_{\mathcal{T}'}\) are polynomials on
-\(\mathcal{T} \cap \mathcal{T}'\), the integrals will be exact when
-using a quadrature scheme of an appropriate degree of accuracy.
-Without partitioning \(\mathcal{T}\), the integrand is not a polynomial
-(in fact, possibly not smooth), so the quadrature cannot be exact.
-
-In order to compute \(M_{TD} \bm{d}\), we'll need to compute the
-\emph{common refinement}, i.e. an intermediate mesh that contains
-both the donor and target meshes. This will consist of all non-empty
-\(\mathcal{T} \cap \mathcal{T}'\) as \(\mathcal{T}\) varies over
-elements of the target mesh and \(\mathcal{T}'\) over elements of the
-donor mesh. This requires solving three specific subproblems:
-\begin{itemize}
-%% H/T: https://tex.stackexchange.com/a/6086/32270
-\itemsep 0em
-\item Forming the region(s) of intersection between two elements that
-  are B\'{e}zier triangles.
-\item Finding all pairs of elements, one each from the target and donor mesh,
-  that intersect.
-\item Numerically integrating over a region of intersection between two
-  elements.
-\end{itemize}
-The first subproblem has been addressed in
-Section~\ref{subsec:intersect-bez-tri}
-and the curved polygon region(s) of intersection have been described
-in Section~\ref{subsec:curved-polygons}. The second will be considered
-in Section~\ref{subsec:advancing-front} and the third in
-Section~\ref{subsec:integration-on-curved} below.
-
-\subsection{Advancing Front}\label{subsec:advancing-front}
-
-\begin{figure}
-  \includegraphics{main_figure13.pdf}
-  \centering
-  \captionsetup{width=.75\linewidth}
-  \caption{Brute force search for a donor element \(\mathcal{T}'\) that matches
-    a fixed target element \(\mathcal{T}\).}
-  \label{fig:target-elt-brute-force}
-\end{figure}
-
-We seek to identify all pairs \(\mathcal{T}\) and \(\mathcal{T}'\) of
-intersecting target and donor elements. The na\"{i}ve approach just
-considers every pair
-of elements and takes \(\bigO{\left|\mathcal{M}_D\right|
-\left|\mathcal{M}_T\right|}\) to complete.\footnote{For a mesh \(\mathcal{M}\),
-the expression \(\left|\mathcal{M}\right|\) represents the number of elements
-in the mesh.} Taking after \cite{Farrell2011}, we can do much better than this
-quadratic time search. In fact, we can compute all integrals in
-\(\bigO{\left|\mathcal{M}_D\right| + \left|\mathcal{M}_T\right|}\).
-First, we fix an element of the target mesh and perform a brute-force search
-to find an intersecting element in the donor mesh
-(Figure~\ref{fig:target-elt-brute-force}). This has worst-case time
-\(\bigO{\left|\mathcal{M}_D\right|}\).
-
-\begin{figure}
-  \includegraphics{main_figure14.pdf}
-  \centering
-  \captionsetup{width=.75\linewidth}
-  \caption{All donor elements \(\mathcal{T}'\) that cover a target element
-    \(\mathcal{T}\), with an extra layer of neighbors in the donor mesh
-    that \emph{do not} intersect \(\mathcal{T}\).}
-  \label{fig:target-elt-overlap-extra-layer}
-\end{figure}
-
-Once we have such a match, we use the connectivity graph of the
-donor mesh to perform a breadth first search
-for neighbors that also intersect the target
-element \(\mathcal{T}\) (Figure~\ref{fig:target-elt-overlap-extra-layer}).
-This search takes \(\bigO{1}\) time. It's also worthwhile to keep the first
-layer of donor elements that don't intersect \(\mathcal{T}\) because they are
-more likely to intersect the neighbors of \(\mathcal{T}\)\footnote{In the
-very unlikely case that the boundary of \(\mathcal{T}\)
-\emph{exactly matches} the boundaries of the donor elements that cover it,
-\emph{none} of the overlapping donor elements can intersect the neighbors of
-\(\mathcal{T}\) so the first layer of non-intersected donor
-elements must be considered.}. Using the list of intersected elements, a
-neighbor of \(\mathcal{T}\) can find a donor element it intersects with in
-\(\bigO{1}\) time (Figure~\ref{fig:target-elt-neighbor}).
-As seen, after our \(\bigO{\left|\mathcal{M}_D\right|}\)
-initial brute-force search, the localized intersections for each
-target element \(\mathcal{T}\) take
-\(\bigO{1}\) time. So together, the process takes
-\(\bigO{\left|\mathcal{M}_D\right| + \left|\mathcal{M}_T\right|}\).
-
-For special cases, e.g. ALE methods, the initial brute-force search
-can be reduced to \(\bigO{1}\). This could be enabled by tracking
-the remeshing process so a correspondence already exists. If a full
-mapping from donor to target mesh exists, the process of computing
-\(M_T\) and \(M_{TD} \bm{d}\) can be fully parallelized across
-elements of the target mesh, or even across shape functions
-\(\phi_T^{(j)}\).
-
-\begin{figure}
-  \includegraphics{main_figure15.pdf}
-  \centering
-  \captionsetup{width=.75\linewidth}
-  \caption{First match between a neighbor of the previously considered
-    target element and all the donor elements that match the
-    previously considered target element.}
-  \label{fig:target-elt-neighbor}
-\end{figure}
-
-\subsection{Integration over Curved Polygons}
-\label{subsec:integration-on-curved}
-
-In order to numerically evaluate integrals of the form
-\begin{equation}
-\int_{\mathcal{T}_0 \cap \mathcal{T}_1} F(x, y) \, dV
-\end{equation}
-we must have a quadrature rule on these curved polygon
-(Section~\ref{subsec:curved-polygons}) intersections
-\(\mathcal{T}_0 \cap \mathcal{T}_1\).
-To do this, we transform the integral into several line integrals
-via Green's theorem and then use an exact Gaussian quadrature to
-evaluate them. Throughout this section we'll assume the integrand
-is of the form \(F = \phi_0 \phi_1\) where each \(\phi_j\) is a shape
-function on \(\mathcal{T}_j\). In addition, we'll refer to the two
-B\'{e}zier maps that define the elements being intersected:
-\(\mathcal{T}_0 = b_0\left(\utri\right)\) and
-\(\mathcal{T}_1 = b_1\left(\utri\right)\).
-
-\begin{figure}
-  \includegraphics{polygon_vs_curved.pdf}
-  \centering
-  \captionsetup{width=.75\linewidth}
-  \caption{Comparing the relative error for the computed area of a quadratic
-    B\'{e}zier triangle. In one method, the curved boundary is used and the
-    result is correct to machine precision. In the other, the curved edges
-    are approximated by polygonal paths.}
-  \label{fig:polygon-vs-curved}
-\end{figure}
-
-\begin{figure}
-  \includegraphics
-      {polygon_vs_curved_intersection.pdf}
-  \centering
-  \captionsetup{width=.75\linewidth}
-  \caption{Comparing the relative error for the computed area of the
-    intersection of two quadratic B\'{e}zier triangles. In one method, the
-    intersection boundary is fully specified as the union of B\'{e}zier curve
-    segments and the area is computed correctly to machine precision. In the
-    other, the curved edges are approximated by polygonal paths and the
-    intersection of the resulting polygons is computed.}
-  \label{fig:polygon-vs-curved-intersection}
-\end{figure}
-
-First a discussion of a method not used. A somewhat simple approach would be
-be to use polygonal approximation. I.e. approximate the boundary of each
-B\'{e}zier triangle with line segments, intersect the resulting polygons,
-triangulate the intersection polygon(s) and then numerically integrate
-on each triangulated cell. However, this approach is prohibitively inefficient.
-For example, consider the curved polygon in
-Figure~\ref{fig:polygon-vs-curved}. Computing the area of \(\mathcal{P}\)
-can be done via an integral: \(\int_{\mathcal{P}} 1 \, dV\).
-By using the actual curved boundary, this integral can be computed with
-relative error (the dashed line in the bottom right subplot) on the order
-of machine precision \(\bigO{\mach}\). On the other hand, approximating
-each side of \(\mathcal{P}\) with \(N\) line segments, the relative error is
-\(\bigO{1/N^2}\). (For example, if \(N = 2\) an edge curve \(b(s, 0)\) would be
-replaced by segments connecting \(b(0, 0), b(1/2, 0)\) and \(b(1, 0)\), i.e.
-\(N + 1\) equally spaced parameters.) This means that in order to perform as
-well as an \emph{exact} quadrature used in the curved case, we'd
-need \(N = \bigO{1/\sqrt{\mach}}\). Compute the area of \(\mathcal{P}\)
-in this way assumes that \(\mathcal{P}\) is already known.
-If instead only the B\'{e}zier triangles in the intersection are known, as
-in Figure~\ref{fig:polygon-vs-curved-intersection}, the polygonal approach
-suffers from the same inefficiency.
-
-Since polygonal approximation is prohibitively expensive,
-we work directly with curved edges and compute integrals on a regular
-domain via substitution.
-If two B\'{e}zier triangles intersect with positive measure, then
-the region of intersection is one or more disjoint curved polygons:
-\(\mathcal{T}_0 \cap \mathcal{T}_1 = \mathcal{P}\) or
-\(\mathcal{T}_0 \cap \mathcal{T}_1 = \mathcal{P} \cup
-\mathcal{P}' \cup \cdots\).
-The second case can be handled in the same way as the first by handling each
-disjoint region independently:
-\begin{equation}
-\int_{\mathcal{T}_0 \cap \mathcal{T}_1} F(x, y) \, dV =
-  \int_{\mathcal{P}} F(x, y) \, dV +
-  \int_{\mathcal{P}'} F(x, y) \, dV + \cdots.
-\end{equation}
-Each curved polygon \(\mathcal{P}\) is defined by its boundary, a
-piecewise smooth parametric curve:
-\begin{equation}
-\partial \mathcal{P} = C_1 \cup \cdots \cup C_n.
-\end{equation}
-This can be thought of as a polygon with \(n\)-sides that happens to
-have curved edges.
-
-Quadrature rules for straight sided polygons have been
-studied (\cite{Mousavi2009}) though they are not in wide use. Even
-if a polygonal quadrature rule was to be employed, a map would need to be
-established from a reference polygon onto the curved edges. This map
-could then be used with a change of coordinates to move the integral
-from the curved polygon to the reference polygon. The problem of extending
-a mapping from a boundary to an entire domain has been studied as
-transfinite interpolation
-(\cite{chenin:tel-00284680, Gordon1982, Perronnet1998}),
-barycentric coordinates (\cite{Wachspress1975}) or mean value coordinates
-(\cite{Floater2003}). However, these maps aren't typically suitable for
-numerical integration because they are either not bijective or increase the
-degree of the edges.
-
-\begin{figure}
-  \includegraphics{main_figure11.pdf}
-  \centering
-  \captionsetup{width=.75\linewidth}
-  \caption{Curved polygon tessellation, done by introducing diagonals
-    from a single vertex node.}
-  \label{fig:tessellated-curved-polygon}
-\end{figure}
-
-Since simple and well established quadrature rules do exist for triangles,
-a valid approach would be
-to tessellate a curved polygon into valid B\'{e}zier triangles
-(Figure~\ref{fig:tessellated-curved-polygon}) and then use substitution as
-in~\eqref{eq:mass-mat-subst}. However, tessellation is challenging for both
-theoretical and computational reasons.
-Theoretical: it's not even clear if an arbitrary curved polygon \emph{can}
-be tessellated into B\'{e}zier triangles. Computational: the placement
-of diagonals and potential introduction of interior nodes is very
-complex in cases where the curved polygon is nonconvex. What's more,
-the curved polygon is given only by the boundary, so higher degree triangles
-(i.e. cubic and above) introduced during tessellation would need to place
-interior control points without causing the triangle to invert. To get a
-sense for these challenges, note how the ``simple'' introduction of
-diagonals in Figure~\ref{fig:bad-tessellation-required} leads to one
-inverted element (the gray element) and another element with area outside
-of the curved polygon (the yellow element). Inverted B\'{e}zier triangles
-are problematic because the accompanying mapping leaves the boundary
-established by the edge curves. For example,
-if the tessellation of \(\mathcal{P}\) contains an inverted
-B\'{e}zier triangle \(\mathcal{T}_2 = b\left(\utri\right)\) then we'll
-need to numerically integrate
-\begin{equation}
-\int_{\mathcal{T}_2} \phi_0 \phi_1 \, dx \, dy =
-  \int_{\utri} \left|\det(Db)\right| \left(\phi_0 \circ b\right)
-  \left(\phi_1 \circ b\right) \, ds \, dt.
-\end{equation}
-If the shape functions are from the pre-image basis (see
-Section~\ref{subsec:shape-functions}), then \(\phi_0\)
-will not be defined at \(b(s, t) \not\in \mathcal{T}_0\) (similarly for
-\(\phi_1\)). Additionally, the absolute value in \(\left|\det(Db)\right|\)
-makes the integrand non-smooth since for inverted elements
-\(\det(Db)\) takes both signs. If the shape functions are from the
-global coordinates basis, then tessellation can be used via an
-application of Lemma~\ref{lemma:bad-triangle}, however this involves
-more computation than just applying Green's theorem along
-\(\partial \mathcal{P}\). By applying the lemma, inverted elements may
-be used in a tessellation, for example by introducing artificial
-diagonals from a vertex as in Figure~\ref{fig:tessellated-curved-polygon}.
-In the global coordinates basis, \(F = \phi_0 \phi_1\) \emph{can}
-be evaluated for points in an inverted element that leave
-\(\mathcal{T}_0\) or \(\mathcal{T}_1\).
-
-\begin{figure}
-  \includegraphics{main_figure16.pdf}
-  \centering
-  \captionsetup{width=.75\linewidth}
-  \caption{Curved polygon intersection that can't be tessellated
-    (with valid B\'{e}zier triangles) by introducing diagonals.}
-  \label{fig:bad-tessellation-required}
-\end{figure}
-
-Instead, we focus on a Green's theorem based approach.
-Define horizontal and vertical antiderivatives
-\(H, V\) of the integrand \(F\) such that \(H_x = V_y = F\).
-We make these \emph{unique} by imposing the
-extra condition that \(H(0, y) \equiv V(x, 0) \equiv 0\).
-This distinction is arbitrary, but in order to \emph{evaluate}
-\(H\) and \(V\), the univariate functions \(H(0, y)\) and \(V(x, 0)\)
-must be specified.
-Green's theorem tells us that
-\begin{equation}
-\int_{\mathcal{P}} 2 F \, dV =
-\int_{\mathcal{P}} H_x + V_y \, dV =
-\oint_{\partial \mathcal{P}} H \, dy - V \, dx =
-\sum_j \int_{C_j} H \, dy - V \, dx.
-\end{equation}
-For a given curve \(C\) with components \(x(r), y(r)\)
-defined on the unit interval, this amounts to having
-to integrate
-\begin{equation}
-G(r) = H(x(r), y(r)) y'(r) - V(x(r), y(r)) x'(r).
-\end{equation}
-To do this, we'll use Gaussian
-quadrature with degree of accuracy sufficient to cover the degree
-of \(G(r)\).
-
-If the shape functions are in the global coordinates basis
-(Section~\ref{subsec:shape-functions}), then \(G\) will also be a polynomial.
-This is because for these shape functions \(F = \phi_0 \phi_1\) will be
-polynomial on \(\reals^2\) and so will \(H\) and \(V\) and since each curve
-\(C\) is a B\'{e}zier curve segment, the components are also polynomials.
-If the shape functions are in the pre-image basis, then \(F\) won't in general
-be polynomial, hence the quadrature rules can only be approximate.
-
-To evaluate \(G\), we must also evaluate \(H\) and \(V\) numerically.
-For example, since \(H(0, y) \equiv 0\),
-the fundamental theorem of calculus tells us that
-\(H\left(\alpha, \beta\right) = \int_0^{\alpha} F\left(x, \beta\right) \, dx\).
-To compute this integral via Gaussian quadrature
-\begin{equation}
-H\left(\alpha, \beta\right) \approx \frac{\alpha}{2} \sum_j w_j
-  F\left(\frac{\alpha}{2} (x_j + 1), \beta\right)
-\end{equation}
-we must be able to evaluate \(F\) for
-points on the line \(y = \beta\) for \(x\) between \(0\) and \(\alpha\). If
-the shape functions are from the pre-image basis, it may not even be possible
-to evaluate \(F\) for such points. Since \(\left[\begin{array}{c c} \alpha &
-\beta \end{array}\right]^T\) is on the boundary of \(\mathcal{P}\), without
-loss of generality
-assume it is on the boundary of \(\mathcal{T}_0\). Thus, for some elements
-(e.g. if the point is on the bottom of the element), points
-\(\left[\begin{array}{c c} \nu & \beta \end{array}\right]^T\) may not be
-in \(\mathcal{T}_0\). Since \(\operatorname{supp}(\phi_0) = \mathcal{T}_0\),
-we could take \(\phi_0(\nu, \beta) = 0\), but this would make the integrand
-non-smooth and so the accuracy of the \emph{exact} quadrature would be
-lost. But extending \(\phi_0 = \widehat{\phi}_0 \circ b_0^{-1}\) outside
-of \(\mathcal{T}_0\) may be impossible: even though \(b_0\) is bijective on
-\(\utri\) it may be many-to-one elsewhere hence \(b_0^{-1}\) can't be
-reliably extended outside of \(\mathcal{T}_0\).
-
-Even if the shape functions are from the global coordinates basis,
-setting \(H(0, y) \equiv 0\) may introduce quadrature points that
-are very far from \(\mathcal{P}\). This can be somewhat addressed by using
-\(H(m, y) \equiv 0\) for a suitably chosen \(m\) (e.g. the minimum
-\(x\)-value in \(\mathcal{P}\)). Then we have
-\(H\left(\alpha, \beta\right) = \int_m^{\alpha} F\left(x, \beta\right) \, dx\).
-
-\section{Numerical Experiments}
-
-\begin{figure}
-  \includegraphics{main_figure30.pdf}
-  \centering
-  \captionsetup{width=.75\linewidth}
-  \caption{Some example meshes used during the numerical
-    experiments; the donor meshs is on the left / blue and the target
-    mesh is on the right / green. These meshes are the cubic approximations
-    of each domain and have been refined twice.}
-  \label{fig:meshes-used-refined}
-\end{figure}
-
-A numerical experiment was performed to investigate the observed order
-of convergence. Three pairs of random meshes were generated, the donor
-on a square of width \(17 / 8\) centered at the origin
-and the target on the unit disc. These domains were chosen intentionally so
-that the target mesh was completely covered by the donor mesh and the
-boundaries did not accidentally introduce ill-conditioned intersection between
-elements. The pairs were linear, quadratic and
-cubic approximations of the domains. The convergence test was done by
-refining each pair of meshes four times and performing solution transfer
-at each level. Figure~\ref{fig:meshes-used-refined} shows the cubic
-pair of meshes after two refinements.
-
-\begin{figure}
-  \includegraphics{main_figure25.pdf}
-  \centering
-  \captionsetup{width=.75\linewidth}
-  \caption{Convergence results for scalar fields on three pairs of related
-    meshes: a linear, quadratic and cubic mesh of the same domain.}
-  \label{fig:composite-errors}
-\end{figure}
-
-Taking after \cite{Farrell2011}, we transfer three
-discrete fields in the discontinuous Galerkin (DG) basis.
-Each field is derived from one of the smooth scalar functions
-\begin{align}
-\zeta_1(x, y) &= 5 y^3 + x^2 + 2y + 3 \\
-\zeta_2(x, y) &= \exp\left(x^2\right) + 2y \\
-\zeta_3(x, y) &= \sin(x) + \cos(y).
-\end{align}
-For a given mesh size \(h\), we expect that on a degree \(p\) isoparametric
-mesh our solution transfer will have \(\bigO{h^{p + 1}}\) errors. To measure
-the rate of convergence:
-\begin{itemize}
-\itemsep 0em
-\item Choose a mesh pair \(\mathcal{M}_D\), \(\mathcal{M}_T\) and
-a known function \(\zeta(x, y)\).
-\item Refine the meshes recursively, starting with
-  \(\mathcal{M}_D^{(0)} = \mathcal{M}_D\),
-  \(\mathcal{M}_T^{(0)} = \mathcal{M}_T\).
-\item Create meshes
-\(\mathcal{M}_D^{(j)}\) and \(\mathcal{M}_T^{(j)}\) from
-\(\mathcal{M}_D^{(j - 1)}\)
-and \(\mathcal{M}_T^{(j - 1)}\) by subdividing each curved
-element into four elements.
-\item Approximate \(\zeta\) by a discrete field: the nodal
-interpolant on the donor mesh \(\mathcal{M}_D^{(j)}\). The
-nodal interpolant is constructed by evaluating \(\zeta\) at the
-nodes \(\bm{n}_j\) corresponding to each shape function:
-\begin{equation}
-\bm{f}_j = \sum_i \zeta\left(\bm{n}_i\right) \phi_D^{(i)}.
-\end{equation}
-\item Transfer \(\bm{f}_j\) to the discrete field \(\bm{g}_j\) on
-the target mesh  \(\mathcal{M}_T^{(j)}\).
-\item Compute the relative error on \(\mathcal{M}_T^{(j)}\):
-\(E_j = \| \bm{g}_j - \zeta \|_2 / \| \zeta \|_2\) (here \(\| \cdot \|_2\)
-is the \(L_2\) norm on the target mesh).
-
-We should instead be measuring \(\| \bm{g}_j - \bm{f}_j \|_2 /
-\| \bm{f}_j \|_2\), but \(E_j\) is much easier to
-compute for \(\zeta(x, y)\) that are straightforward to evaluate.
-Due to the triangle inequality \(E_j\) can be a reliable proxy
-for the actual projection error, though when
-\(\| \bm{f}_j - \zeta \|_2\) becomes too large it will dominate
-the error and no convergence will be observed.
-\end{itemize}
-
-Convergence results are shown in Figure~\ref{fig:composite-errors}
-and confirm the expected orders. Since \(\zeta_1\) is a cubic polynomial,
-the solution transfer on the cubic mesh should be \emph{exact}, so there
-is a certain minimum threshold that can be reached.
-
-\section{Conclusion}
-
-This work has described a method for conservative interpolation
-between curved meshes. The transfer process conserves globally
-to machine precision since we can use exact quadratures for all
-integrals. The primary source of error comes from solving the linear
-system with the mass matrix for the target mesh. This allows
-less restrictive usage of mesh adaptivity, which can make computations
-more efficient. Additionally, having a global transfer algorithm
-allows for remeshing to be done less frequently.
-
-The algorithm breaks down into three core subproblems: B\'{e}zier triangle
-intersection, an advancing front for intersecting elements and
-integration on curved polygons. The inherently local nature of the
-advancing front allows the algorithm to be parallelized via domain
-decomposition with little data shared between processes. By
-restricting integration to the intersection of elements from the
-target and donor meshes, the algorithm can accurately transfer
-both continuous and discontinuous fields.
-
-\subsection{Future Work}
-
-As mentioned in the preceding chapters, there are several research
-directions possible to build upon the solution transfer algorithm.
-The usage of Green's theorem nicely extends to \(\reals^3\) via
-Stoke's theorem, but the B\'{e}zier triangle intersection algorithm
-is specific to \(\reals^2\). The equivalent B\'{e}zier tetrahedron
-intersection algorithm is significantly more challenging.
-
-The restriction to shape functions from the global coordinates basis
-is a symptom of the method and not of the inherent problem. The
-pre-image basis has several appealing properties, for example
-this basis can be precomputed on \(\utri\). The problem of a
-valid tessellation of a curved polygon warrants more exploration.
-Such a tessellation algorithm would enable usage of the pre-image
-basis.
-
-The usage of the global coordinates basis does have some benefits.
-In particular, the product of shape functions from different meshes
-is still a polynomial in \(\reals^2\). This means that we could
-compute the coefficients of \(F = \phi_0 \phi_1\) directly and
-use them to evaluate the antiderivatives \(H\) and \(V\) rather
-than using the fundamental theorem of calculus. Even if this
-did not save any computation, it may still be preferred over
-the FTC approach because it would remove the usage of quadrature
-points outside of the domain \(\mathcal{P}\).
-
-\bibliography{paper}
-\bibliographystyle{alpha}
-
-\appendix
-
 \section{Allowing Tessellation with Inverted Triangles}

### 2018-08-23 doc/paper.tex
Slimming down the introduction.
Removing three figures and the overly simply method of
characteristics explanation.

@@
 
-\begin{figure}
-  \includegraphics{simple_transport.pdf}
-  \centering
-  \captionsetup{width=.75\linewidth}
-  \caption{The solution to \(u_t + u_x = 0, \; u(x, 0) = x^3\) plotted in
-    the \(xu\)-plane. Demonstrates simple transport of
-    the solution.}
-  \label{fig:simple-transport}
-\end{figure}
-
-The method of characteristics helps transform partial differential equations
-into ordinary differential equations by dividing the physical domain into
-a family of curves. For example, the simple transport equation
-\begin{equation}\label{eq:simple-transport}
-u_t + c u_x = 0
-\end{equation}
-can be transformed when restricting to the family of lines
-\(x(t) = x_0 + c t\). On these lines \(u(x(t), t)\) is constant, by
-construction, and so the solution is ``transported'' from \(u(x_0, 0)\)
-along each characteristic line (Figure~\ref{fig:simple-transport}).
-
-Motivated by this, \emph{Lagrangian methods} treat each point in the
+Lagrangian methods treat each point in the
 physical domain as a ``particle'' which moves along a characteristic curve
@@
 to solve PDEs, even with higher order or non-linear terms.
-For example, if a diffusion term is added to~\eqref{eq:simple-transport}
+For example, the simple transport equation with a diffusion term
 \begin{equation}
@@
 \end{equation}
-then the same characteristics can be used, but the value
-along each characteristic is no longer constant; instead it satisfies the
+has characteristics \(x(t) = x_0 + ct\) that only correspond to the
+first order terms. The value then satisfies the
 ODE \(\frac{d}{dt} u(x(t), t) = \eps u_{xx}\).
@@
 
-\begin{figure}
-  \includegraphics{distortion_remesh.pdf}
-  \centering
-  \captionsetup{width=.75\linewidth}
-  \caption{Remeshing a domain after distortion caused by particle motion
-    along the velocity field \(\left[ y^2 \; 1 \right]^T\) from \(t = 0\)
-    to \(t = 1\).}
-  \label{fig:distortion-remesh}
-\end{figure}
-
 To deal with distortion, one can allow the mesh to adapt in between time
-steps. For example, Figure~\ref{fig:distortion-remesh} shows an example
-remeshing of the domain.
-In addition to improving mesh quality, mesh
+steps. In addition to improving mesh quality, mesh
 adaptivity can be used to dynamically focus computational effort to resolve
@@
 
-\begin{figure}
-  \includegraphics{main_figure27.pdf}
-  \centering
-  \captionsetup{width=.75\linewidth}
-  \caption{Comparing straight sided meshes to a curved mesh when approximating
-    the unit disc in \(\reals^2\).}
-  \label{fig:curved-vs-straight-mesh}
-\end{figure}
-
 To allow for greater geometric flexibility and for high order of convergence,
@@
 more on high-order CFD methods.) Curved meshes can typically
-represent a given geometry with far fewer elements than a straight sided mesh
-(for example, Figure~\ref{fig:curved-vs-straight-mesh}).
+represent a given geometry with far fewer elements than a straight sided mesh.
 The increase in accuracy also allows for the use of fewer elements, which

### 2018-08-23 doc/paper.tex
Removing figures for polygonal approximation.
Also making a few small tweaks (some for content, some for
formatting).

@@
 the unit triangle (or unit simplex) in \(\reals^2\):
-\(\utri = \left\{(s, t) \mid 0 \leq s, t, s + t \leq 1\right\}\).
+\begin{equation}
+\utri = \left\{(s, t) \mid 0 \leq s, t, s + t \leq 1\right\}.
+\end{equation}
 When dealing with sequences with multiple indices, e.g.
 \(s_{m, n} = m + n\), we'll use bold symbols to represent
-a multi-index: \(\bm{i} = (m, n)\). We'll use \(\left|\bm{i}\right|\) to
-represent the sum of the components in a multi-index.
+a multi-index: \(\bm{i} = (m, n)\).
 The binomial coefficient
@@
 function; due to composition with \(b^{-1}\) we can only guarantee that
-it is algebraic (i.e. it can be defined as the zero set of polynomials).
+it is algebraic (i.e. it can be defined as the zero set of polynomials
+with coefficients in \(\reals\left[x, y\right]\)).
 
@@
 \end{itemize}
-The first subproblem has been addressed in
+The first subproblem is discussed in
 Section~\ref{subsec:intersect-bez-tri}
@@
 
-\begin{figure}
-  \includegraphics{polygon_vs_curved.pdf}
-  \centering
-  \captionsetup{width=.75\linewidth}
-  \caption{Comparing the relative error for the computed area of a quadratic
-    B\'{e}zier triangle. In one method, the curved boundary is used and the
-    result is correct to machine precision. In the other, the curved edges
-    are approximated by polygonal paths.}
-  \label{fig:polygon-vs-curved}
-\end{figure}
-
-\begin{figure}
-  \includegraphics
-      {polygon_vs_curved_intersection.pdf}
-  \centering
-  \captionsetup{width=.75\linewidth}
-  \caption{Comparing the relative error for the computed area of the
-    intersection of two quadratic B\'{e}zier triangles. In one method, the
-    intersection boundary is fully specified as the union of B\'{e}zier curve
-    segments and the area is computed correctly to machine precision. In the
-    other, the curved edges are approximated by polygonal paths and the
-    intersection of the resulting polygons is computed.}
-  \label{fig:polygon-vs-curved-intersection}
-\end{figure}
-
 First a discussion of a method not used. A somewhat simple approach would be
@@
 on each triangulated cell. However, this approach is prohibitively inefficient.
-For example, consider the curved polygon in
-Figure~\ref{fig:polygon-vs-curved}. Computing the area of \(\mathcal{P}\)
-can be done via an integral: \(\int_{\mathcal{P}} 1 \, dV\).
-By using the actual curved boundary, this integral can be computed with
-relative error (the dashed line in the bottom right subplot) on the order
-of machine precision \(\bigO{\mach}\). On the other hand, approximating
-each side of \(\mathcal{P}\) with \(N\) line segments, the relative error is
-\(\bigO{1/N^2}\). (For example, if \(N = 2\) an edge curve \(b(s, 0)\) would be
-replaced by segments connecting \(b(0, 0), b(1/2, 0)\) and \(b(1, 0)\), i.e.
-\(N + 1\) equally spaced parameters.) This means that in order to perform as
-well as an \emph{exact} quadrature used in the curved case, we'd
-need \(N = \bigO{1/\sqrt{\mach}}\). Compute the area of \(\mathcal{P}\)
-in this way assumes that \(\mathcal{P}\) is already known.
-If instead only the B\'{e}zier triangles in the intersection are known, as
-in Figure~\ref{fig:polygon-vs-curved-intersection}, the polygonal approach
-suffers from the same inefficiency.
+For example, consider computing the area of \(\mathcal{P}\) via an
+integral: \(\int_{\mathcal{P}} 1 \, dV\). By using the actual curved
+boundaries of each element, this integral can be computed with relative
+error on the order of machine precision \(\bigO{\mach}\). On the other hand,
+approximating each side of \(\mathcal{P}\) with \(N\) line segments, the
+relative error is \(\bigO{1/N^2}\). (For example, if \(N = 2\) an edge
+curve \(b(s, 0)\) would be replaced by segments connecting \(b(0, 0),
+b(1/2, 0)\) and \(b(1, 0)\), i.e. \(N + 1\) equally spaced parameters.) This
+means that in order to perform as well as an \emph{exact} quadrature used in
+the curved case, we'd need \(N = \bigO{1/\sqrt{\mach}}\).
 
@@
 \end{equation}
-This can be thought of as a polygon with \(n\)-sides that happens to
+This can be thought of as a polygon with \(n\) sides that happens to
 have curved edges.
@@
 If the shape functions are in the pre-image basis, then \(F\) won't in general
-be polynomial, hence the quadrature rules can only be approximate.
+be polynomial, hence standard quadrature rules can't be exact.
 

### 2018-08-23 doc/paper.tex
Adding reference to Qiu paper.
Also changing Numerical Analysis keyword to DG.

@@
 \noindent \emph{Keywords}: Remapping, Curved Meshes, Lagrangian,
-Solution Transfer, Numerical analysis
+Solution Transfer, Discontinuous Galerkin
 \end{abstract}
@@
 are curved, the intersection can be non-convex and can even split into
-multiple disjoint regions.
+multiple disjoint regions. In \cite{Qiu2018}, a related problem is considered
+where squares are allowed to curve along characteristics and the solution is
+remapped onto a regular square grid.
 

### 2018-09-11 doc/paper.tex
Renaming Lemma B.1 as a theorem.

@@
 \theoremstyle{definition}
-\newtheorem{lemma}{Lemma}[section]
+\newtheorem{theorem}{Theorem}[section]
 
@@
 global coordinates basis, then tessellation can be used via an
-application of Lemma~\ref{lemma:bad-triangle}, however this involves
+application of Theorem~\ref{theorem:bad-triangle}, however this involves
 more computation than just applying Green's theorem along
-\(\partial \mathcal{P}\). By applying the lemma, inverted elements may
+\(\partial \mathcal{P}\). By applying the theorem, inverted elements may
 be used in a tessellation, for example by introducing artificial
@@
 
-\begin{lemma}\label{lemma:bad-triangle}
+\begin{theorem}\label{theorem:bad-triangle}
 Consider three smooth curves
@@
 formula combined with Green's theorem.
-\end{lemma}
+\end{theorem}
 

### 2018-09-11 doc/paper.tex
Removing "Future Work" heading from conclusion.
Replacing "Advancing Front" with "Expanding Front"
Per and I had discussed using BFS, but it isn't appropriate
because the algorithm isn't doing a search, it's covering
**all** elements / element pairs.

@@
 in Section~\ref{subsec:curved-polygons}. The second will be considered
-in Section~\ref{subsec:advancing-front} and the third in
+in Section~\ref{subsec:expanding-front} and the third in
 Section~\ref{subsec:integration-on-curved} below.
 
-\subsection{Advancing Front}\label{subsec:advancing-front}
+\subsection{Expanding Front}\label{subsec:expanding-front}
 
@@
 Once we have such a match, we use the connectivity graph of the
-donor mesh to perform a breadth first search
+donor mesh to perform a breadth-first search
 for neighbors that also intersect the target
@@
 The algorithm breaks down into three core subproblems: B\'{e}zier triangle
-intersection, an advancing front for intersecting elements and
+intersection, a expanding front for intersecting elements and
 integration on curved polygons. The inherently local nature of the
-advancing front allows the algorithm to be parallelized via domain
+expanding front allows the algorithm to be parallelized via domain
 decomposition with little data shared between processes. By
@@
 both continuous and discontinuous fields.
-
-\subsection{Future Work}
 

### 2018-09-12 doc/paper.tex
Combined Sections 3 and 4.
Removing "for example" in Section 1.1.
This was just a simple 1D PDE with diffusion.
Dropping Figure 1.1 that shows distortion.
Also modifying the reference to that PDE to just list the velocity
field.

@@
 to solve PDEs, even with higher order or non-linear terms.
-For example, the simple transport equation with a diffusion term
-\begin{equation}
-u_t + c u_x - \eps u_{xx} = 0
-\end{equation}
-has characteristics \(x(t) = x_0 + ct\) that only correspond to the
-first order terms. The value then satisfies the
-ODE \(\frac{d}{dt} u(x(t), t) = \eps u_{xx}\).
 
@@
 
-\begin{figure}
-  \includegraphics{mesh_distortion.pdf}
-  \centering
-  \captionsetup{width=.75\linewidth}
-  \caption{Distortion of a regular mesh caused by particle motion along
-    the velocity field \(\left[ y^2 \; 1 \right]^T\) from \(t = 0\)
-    to \(t = 1\) with \(\Delta t = 1/4\).}
-  \label{fig:mesh-distortion}
-\end{figure}
-
 A flow-based change to a mesh can cause problems if it causes the mesh to
@@
 even tangle (i.e. elements begin to overlap).
-For an example of such distortion (Figure~\ref{fig:mesh-distortion}),
-consider a PDE of the form
-\begin{equation}\label{eq:non-rigid-characteristics}
-u_t + \left[ \begin{array}{c} y^2 \\ 1 \end{array}\right] \cdot \nabla u +
-  F\left(u, \nabla u\right) = 0.
-\end{equation}
-The characteristics \(y(t) = y_0 + t, x(t) = x_0 +
-\left(y(t)^3 - y_0^3\right)/3\)
-distort the mesh considerably after just one second.
 
@@
 quadratic element as the nodes move along the
-characteristics from~\eqref{eq:non-rigid-characteristics}.
+characteristics given by the velocity field
+\(\left[ \begin{array}{c c} y^2 & 1 \end{array}\right]^T\).
 This element uses the triangle vertices and edge
@@
 
-\section{Common Refinement}
+\subsection{Common Refinement}
 

### 2018-09-12 doc/paper.tex
Removing subsections from introduction.
Changed intro to just introduce the problem.
The "solution" is introduced later on (at the start of the
limitations paragraphs.)

@@
 
-In this paper, an algorithm for conservative solution transfer between curved
-meshes will be described. This has practical applications to many methods in
+Solution transfer between meshes is a common problem that
+has practical applications to many methods in
 computational physics. For example, by allowing the underyling
@@
 
-\subsection{Lagrangian Methods}
-
 Lagrangian methods treat each point in the
@@
 are treated like particles) and the mesh ``travels''.
-
-\subsection{Remeshing and Adaptivity}
 
@@
 mesh will distort.
-
-\subsection{High-order Meshes}
 
@@
 
-\subsection{Multiphysics and Comparing Methods}
-
 In multiphysics simulations, a problem is partitioned into physical components.
@@
 different meshes of the same domain.
-
-\subsection{Local versus Global Transfer}
 
@@
 
-\subsection{Limitations}
-
 \begin{figure}
@@
 
-The method described in this paper only applies to meshes in \(\reals^2\).
+In this paper, an algorithm for conservative solution transfer between curved
+meshes will be described. This method applies to meshes in \(\reals^2\).
 Application to meshes in \(\reals^3\) is a direction for future research,
@@
 target mesh or to map the field onto known quadrature points.
-
-\subsection{Overview}
 

### 2018-10-11 doc/paper.tex
Minor updates.

@@
 discrete field on the mesh is same as the degree of the shape functions that
-determine the mesh.} meshes. Allowing curved geometries is useful since
-many practical
-problems involve geometries that change over time, such as flapping flight
-or fluid-structure interactions. In addition, high-order CFD methods
+determine the mesh.} meshes. High-order methods
 have the ability to produce highly accurate solutions
-with low dissipation and low dispersion error.
+with low dissipation and low dispersion error, however, they typically
+require curved meshes. In addition, curved elements have
+advantages in problems that involve geometries that change over time,
+such as flapping flight or fluid-structure interactions.
 
@@
 velocity, pressure, density, concentration, etc.). They are an effective way
-to solve PDEs, even with higher order or non-linear terms.
-
+to solve PDEs, even with higher order or non-linear terms \cite{MR3023731}.
 This approach transforms the numerical solution of PDEs into a family of
@@
 are treated like particles) and the mesh ``travels''.
-
 A flow-based change to a mesh can cause problems if it causes the mesh to

### 2018-10-12 doc/paper.tex
Made some edits after discussion with Per.
Including

- Adding more detail about method to abstract
- Adding note about numerical experiment to results
- Adding a subsection at beginning of `3. Galerkin Projection`
- Clarify the comment about `zeta1` not being exact on cubic meshes
- Fix Stoke's -> Stokes' theorem
- Changing title to "Curved Triangular Meshes"

@@
 \pagestyle{fancy}
-\lhead{High-order Solution Transfer between Curved Meshes}
+\lhead{High-order Solution Transfer between Curved Triangular Meshes}
 \rhead{Danny Hermes, Per-Olof Persson}
@@
 unstructured meshes --- by considering high-order isoparametric meshes
-with curved elements.
+with curved elements. To facilitate solution transfer, we numerically
+integrate the product of shape functions via Green's theorem along the
+boundary of the intersection of two curved elements. We perform a numerical
+experiment and confirm the expected accuracy by transferring test fields
+across two families of meshes.
 \\ \\
@@
 
+\subsection{Linear System for Projection}
+
 \begin{figure}
@@
 and confirm the expected orders. Since \(\zeta_1\) is a cubic polynomial,
-the solution transfer on the cubic mesh should be \emph{exact}, so there
-is a certain minimum threshold that can be reached.
+one might expect the solution transfer on the cubic mesh to be \emph{exact}.
+This expectation would hold in the superparametric case (i.e. where the
+elements are straight sided but the shape functions are higher degree).
+However, when the elements aren't straight side the isoparametric mapping
+changes the underlying function space.
 
@@
 The usage of Green's theorem nicely extends to \(\reals^3\) via
-Stoke's theorem, but the B\'{e}zier triangle intersection algorithm
+Stokes' theorem, but the B\'{e}zier triangle intersection algorithm
 is specific to \(\reals^2\). The equivalent B\'{e}zier tetrahedron

### 2018-10-12 nox.py
Formatting article for publication.
Per https://msp.org/camcos/about/journal/submissions.html, I
used the `amsart` class.

@@ -78,5 +78,5 @@ def build_tex(session):
         session,
         "paper",
         "5178018C9121C4981906E150C72BEC1B",
-        extensions=("aux", "bbl", "blg", "log", "out", "toc"),
+        extensions=("aux", "bbl", "blg", "log", "out"),
     )

### 2019-06-21 doc/paper.tex
Formatting article for publication.
Per https://msp.org/camcos/about/journal/submissions.html, I
used the `amsart` class.
Using `amsaddr` package.
Commenting out `urladdr` (for now).
Removing address from my (Danny's) author heading.
Fixing "it's" -> "its" grammatical error.

@@
-\documentclass[letterpaper,10pt]{article}
+\documentclass[oneside, reqno]{amsart}
+
+%% H/T: https://tex.stackexchange.com/a/226826/32270
+\usepackage{amsaddr}
 
@@
 \allowdisplaybreaks
-%% H/T: https://tex.stackexchange.com/a/71153/32270
-\usepackage[nottoc,notlot,notlof]{tocbibind}
 
@@
 
-\usepackage{fancyhdr}
-\pagestyle{fancy}
-\lhead{High-order Solution Transfer between Curved Triangular Meshes}
-\rhead{Danny Hermes, Per-Olof Persson}
-
 %% H/T: https://tex.stackexchange.com/a/28334/32270
@@
 
-\renewcommand{\headrulewidth}{0pt}
 \renewcommand{\qed}{\(\blacksquare\)}
@@
 \begin{document}
+
+\title{High-order Solution Transfer between Curved Triangular Meshes}
+
+\author{Danny Hermes}
+\email{dhermes@berkeley.edu}
+
+\author{Per-Olof Persson}
+\address{UC Berkeley, 970 Evans Hall \#3840, Berkeley, CA 94720-3840 USA}
+\email{persson@berkeley.edu}
+%% \urladdr{persson.berkeley.edu}
 
@@
 
-\tableofcontents
+\maketitle
 
@@
 functions allow for order \(p + 1\) convergence, which is desirable in
-it's own right. However, even in such cases, a Lagrangian method must either
+its own right. However, even in such cases, a Lagrangian method must either
 curve the mesh or information about the flow of the geometry will be lost.
@@
 \(\left[0, 1\right]\) when \(s\) is as well. Due to this fact, the
-curve must be contained in the convex hull of it's control points.
+curve must be contained in the convex hull of its control points.
 

### 2019-06-21 doc/paper.tex
Change wording regarding bijective Jacobian.
Based on review feedback.
Incorporating two changes based on review feedback.
- Fix "in term" -> "in turn" typo
- Change "In the CG case, ..." to "In CG, ..."

@@
 diffeomorphic to \(\utri\), i.e. \(b(s, t)\) is bijective and has
-an everywhere invertible Jacobian. We must also have the orientation
+an invertible Jacobian everywhere. We must also have the orientation
 preserved, i.e. the Jacobian must have positive determinant. For example, in
@@
 \(\phi_D^{(j)}\) and a known field \(\bm{q}_D = \sum_j d_j \phi_D^{(j)}\)
-\footnote{This is somewhat a simplification. In the CG case,
+\footnote{This is somewhat a simplification. In CG,
 some coefficients will be paired with multiple shape functions, such
@@
 but that is equivalent to removing some of the basis functions which may
-in term make the projection non-conservative. This is because the removed
+in turn make the projection non-conservative. This is because the removed
 basis functions may have been used in \(1 = \sum_j u_j \phi_{T}^{(j)}\).

### 2019-06-21 doc/paper.tex
Removed remark about leaving domain.
Based on review feedback. The comment

> if it causes the mesh to leave the domain being analyzed

was too vague and didn't deliver much value. One reviewer interpreted
it as having contradicted the idea of a free boundary. (The original
intent was aimed at problems on an infinite domain with a solution
that dissipates to 0 outside the domain. In these cases, boundary
elements are just there to "box in" the solution.)

@@
 are treated like particles) and the mesh ``travels''.
-A flow-based change to a mesh can cause problems if it causes the mesh to
-leave the domain being analyzed or if it distorts the mesh until the element
+A flow-based change to a mesh can cause problems if it
+distorts the mesh until the element
 quality is too low in some mesh elements. Over enough time, the mesh can

### 2019-06-21 doc/paper.tex
Fix sentence fragment.
Added extra comment about solution transfer for methods using
different meshes of same domain.
Adding caveat about mesh modification in ALE.
A reviewer was concerned that the sentence about flipping elements
implied that **all** ALE methods will distort the mesh.

@@
 be compared via solution transfer. Or, if two different methods use two
-different meshes of the same domain.
+different meshes of the same domain, a solution may need to be transferred
+across these meshes for comparison.
 
@@
 and as a result much of the existing literature focuses on mesh-mesh
-pairs that will occur during an ALE-based simulation. When flow-based
+pairs that will occur during an ALE-based simulation. Many ALE methods
+modify the mesh during simulation: when flow-based
 mesh distortion occurs, elements are typically ``flipped'' (e.g. a

### 2019-06-21 nox.py
Bringing over script from `phd-thesis`.
This was used to create `element_distortion.pdf`. I have modified
it slightly (to remove the triangles) and will continue to do so
based on reviewer feedback about the coloring of the "fading"
nodes (i.e. alpha < 1.0).

@@ -80,3 +80,41 @@ def build_tex(session):
         "5178018C9121C4981906E150C72BEC1B",
         extensions=("aux", "bbl", "blg", "log", "out"),
     )
+
+
+@nox.session
+def make_images(session):
+    session.interpreter = SINGLE_INTERP
+    # Install all dependencies.
+    session.install("--requirement", "make-images-requirements.txt")
+    # Run the script(s).
+    # Make sure
+    # - Custom ``matplotlibrc`` is used
+    # - Code in ``src/`` is importable
+    # - PDFs have deterministic ``CreationDate``
+    env = {"MATPLOTLIBRC": get_path("images"), "SOURCE_DATE_EPOCH": "0"}
+    script_paths = ("distort.py",)
+    for script_path in script_paths:
+        script = get_path("scripts", script_path)
+        session.run("python", script, env=env)
+
+
+@nox.session
+def update_requirements(session):
+    session.interpreter = SINGLE_INTERP
+
+    if py.path.local.sysfind("git") is None:
+        session.skip("`git` must be installed")
+
+    # Install all dependencies.
+    session.install("pip-tools")
+
+    # Update all of the requirements file(s).
+    names = ("make-images",)
+    for name in names:
+        in_name = "{}-requirements.in".format(name)
+        txt_name = "{}-requirements.txt".format(name)
+        session.run(
+            "pip-compile", "--upgrade", "--output-file", txt_name, in_name
+        )
+        session.run("git", "add", txt_name)

### 2019-06-21 scripts/distort.py

@@ -1,0 +1,153 @@
+# Licensed under the Apache License, Version 2.0 (the "License");
+# you may not use this file except in compliance with the License.
+# You may obtain a copy of the License at
+#
+#     https://www.apache.org/licenses/LICENSE-2.0
+#
+# Unless required by applicable law or agreed to in writing, software
+# distributed under the License is distributed on an "AS IS" BASIS,
+# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+# See the License for the specific language governing permissions and
+# limitations under the License.
+
+import bezier
+import matplotlib.pyplot as plt
+import numpy as np
+
+import plot_utils
+
+
+ALPHA = 0.375
+
+
+def point_on_characteristic(xv, yv, t):
+    yt = yv + t
+    xt = xv + (yt * yt * yt - yv * yv * yv) / 3
+    return xt, yt
+
+
+def get_title(t):
+    if t == int(t):
+        return "$t = {:d}.0$".format(int(t))
+    else:
+        return "$t = {:g}$".format(t)
+
+
+def distort_cubic_tri():
+    node1 = np.array([-0.75, 0.0])
+    node2 = np.array([2.25, -1.5])
+    node3 = np.array([1.5, 1.5])
+    control_points = np.array(
+        [
+            node1,
+            0.5 * (node1 + node2),
+            node2,
+            0.5 * (node1 + node3),
+            0.5 * (node2 + node3),
+            node3,
+        ]
+    )
+
+    figure, all_axes = plt.subplots(2, 3, sharex=True, sharey=True)
+    min_y = -1.65
+    max_y = 2.8
+    control_x = control_points[:, 0]
+    control_y = control_points[:, 1]
+    bezier_nodes = np.empty((2, len(control_x)), order="F")
+
+    # First add characteristic curves to the top row of axes.
+    for i, xv in enumerate(control_x):
+        yv = control_y[i]
+        min_t = min_y - yv
+        max_t = max_y - yv
+        t_vals = np.linspace(min_t, max_t, 100)
+        to_plot = point_on_characteristic(xv, yv, t_vals)
+        for ax in all_axes[0, :]:
+            ax.plot(
[…]

### 2019-06-21 scripts/plot_utils.py

@@ -1,0 +1,43 @@
+# Licensed under the Apache License, Version 2.0 (the "License");
+# you may not use this file except in compliance with the License.
+# You may obtain a copy of the License at
+#
+#     https://www.apache.org/licenses/LICENSE-2.0
+#
+# Unless required by applicable law or agreed to in writing, software
+# distributed under the License is distributed on an "AS IS" BASIS,
+# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+# See the License for the specific language governing permissions and
+# limitations under the License.
+
+"""Shared utilities and settings for plotting."""
+
+
+import os
+
+import seaborn
+
+
+# As of ``0.9.0``, this palette has (BLUE, ORANGE, GREEN, RED, PURPLE, BROWN).
+_COLORS = seaborn.color_palette(palette="deep", n_colors=6)
+GREEN = _COLORS[2]
+del _COLORS
+TEXT_SIZE = 10
+TICK_SIZE = 7
+
+
+def set_styles():
+    """Set the styles used for plotting."""
+    seaborn.set(style="white")
+
+
+def get_path(*parts):
+    """Get a file path in the ``images/`` directory.
+
+    This assumes the script is currently in the ``scripts/``
+    directory.
+    """
+    curr_dir = os.path.abspath(os.path.dirname(__file__))
+    root_dir = os.path.dirname(curr_dir)
+    images_dir = os.path.join(root_dir, "images")
+    return os.path.join(images_dir, *parts)

### 2019-06-21 scripts/distort.py
Updating `element_distortion.pdf` to use colors for nodes in each timestep.

@@ -18,6 +18,7 @@ import plot_utils
 
 
 ALPHA = 0.375
+NODE_COLORS = (plot_utils.BLUE, plot_utils.PURPLE, "black")
 
 
 def point_on_characteristic(xv, yv, t):
@@ -95,24 +96,23 @@ def distort_cubic_tri():
         surface = bezier.Surface.from_nodes(bezier_nodes)
         surface.plot(256, ax=ax_below)
 
-        # Add "nodes" to both plots.
-        for ax in (ax_top, ax_below):
-            ax.plot(
-                xt,
-                yt,
-                color="black",
-                marker="o",
-                linestyle="none",
-                markersize=4,
-            )
+        # Add "nodes" to bottom plot.
+        ax_below.plot(
+            xt,
+            yt,
+            color=NODE_COLORS[index],
+            marker="o",
+            linestyle="none",
+            markersize=4,
+        )
         # Add shadow "nodes" to top row for "next" plots.
-        for next_index in range(index + 1, 3):
+        for next_index in range(index, 3):
             ax = all_axes[0, next_index]
             ax.plot(
                 xt,
                 yt,
-                color="black",
-                alpha=0.5 - 0.25 * (next_index - index - 1),
+                color=NODE_COLORS[index],
+                alpha=0.75,
                 marker="o",
                 linestyle="none",
                 markersize=4,

### 2019-06-21 scripts/plot_utils.py

@@ -20,7 +20,9 @@ import seaborn
 
 # As of ``0.9.0``, this palette has (BLUE, ORANGE, GREEN, RED, PURPLE, BROWN).
 _COLORS = seaborn.color_palette(palette="deep", n_colors=6)
+BLUE = _COLORS[0]
 GREEN = _COLORS[2]
+PURPLE = _COLORS[4]
 del _COLORS
 TEXT_SIZE = 10
 TICK_SIZE = 7

### 2020-04-29 doc/paper.tex
Changing "interpolation" -> "interpolative".
This was based on review feedback and the part of speech fits
better in the sentence structure.
Adding a footnote describing what ALE is.

@@
 the ability to change the mesh, Lagrangian methods (or, more generally,
-ALE \cite{Hirt1974}) would not be useful, since after a limited time the
-mesh will distort.
+ALE\footnote{ALE, or Arbitrary Lagrangian-Eulerian methods are not constrained
+by a fixed computational mesh (the Eulerian approach) or a fixed fluid flow
+(the Lagrangian approach) and typically combine the benefits of both approaches
+to create composite methods} \cite{Hirt1974}) would not be useful, since after '
+a limited time the mesh will distort.
 
@@
 target mesh is contained in the donor mesh. This ensures that the solution
-transfer is \emph{interpolation}. In the case where all target elements are
+transfer is \emph{interpolative}. In the case where all target elements are
 partially covered, \emph{extrapolation} could be used to extend a solution

### 2020-04-29 doc/paper.tex
Adding further clarification about CG.

@@
 \(\phi_D^{(j)}\) and a known field \(\bm{q}_D = \sum_j d_j \phi_D^{(j)}\)
-\footnote{This is somewhat a simplification. In CG,
-some coefficients will be paired with multiple shape functions, such
-as the coefficient at a vertex node.}
+\footnote{This is somewhat a simplification. In CG (continuous Galerkin, as
+opposed to DG or discontinuous Galerkin), some coefficients will be paired
+with multiple shape functions, such as the coefficient at a vertex node.}
 and a

### 2020-04-30 doc/paper.tex
Adding citation for "Spatially accelerated shape embedding in multimaterial simulations" as a way to speed up the brute-force search for pairs of mesh elements.
Adding `Anderson2018` citation.
It is unused for now, but will be referenced shortly. Also
removing a stray `'`.'

@@
 (the Lagrangian approach) and typically combine the benefits of both approaches
-to create composite methods} \cite{Hirt1974}) would not be useful, since after '
+to create composite methods} \cite{Hirt1974}) would not be useful, since after
 a limited time the mesh will distort.
@@
 elements of the target mesh, or even across shape functions
-\(\phi_T^{(j)}\).
+\(\phi_T^{(j)}\). Spatial binning techniques for mesh elements could also be
+used to improve the initial brute-force search as in \cite{Weiss16_imr}.
 

### 2020-09-29 doc/paper.tex
Fixing typo: "straight side" -> "straight sided".
Major pass on the introduction.

@@
 computational domain to change during a simulation, computational
-effort can be focused dynamically to resolve sensitive features
-of a numerical solution. Mesh adaptivity, this in-flight change in the mesh,
+effort can be focused dynamically to resolve relevant features
+of a numerical solution. This so-called mesh adaptivity typically
 requires translating the numerical solution from the old mesh to the new,
-i.e. solution transfer. As another example, Lagrangian or particle-based
+i.e. solution transfer \cite{Babuska1978,Peraire1987,Pain2001,Iske2004}. As another example, Lagrangian or particle-based
 methods treat each node in the mesh as a particle and so with each timestep the
-mesh travels \emph{with} the fluid.
-However, over (typically limited) time the mesh
-becomes distorted and suffers a loss in element quality which causes
-catastrophic loss in the accuracy of computation. To overcome this, the
+mesh travels \emph{with} the fluid \cite{MR3023731}.
+However, over (typically short) time the mesh
+becomes distorted and suffers a loss in element quality which eventually causes
+inaccurate solutions. To overcome this, the
 domain must be remeshed or rezoned and the solution must be
-transferred (remapped) onto the new mesh configuration. A few scenarios
-where solution transfer is necessary will be considered below
-to motivate the ``black box'' solution transfer algorithm.
+transferred (remapped) onto the new mesh configuration. A related more general
+class of methods is the Arbitrary Lagrangian-Eulerian (ALE) method, which
+are not constrained by a fixed computational mesh (the Eulerian approach) or
+by a fixed fluid flow (the Lagrangian approach) and typically combine the benefits
+of both approaches \cite{Hirt1974,MR3302403}.
 
@@
 (approximated by a discrete field) is known on a \emph{donor} mesh and must
-be transferred to a \emph{target} mesh. In many applications, the field
-must be conserved for physical reasons, e.g. mass or energy cannot leave or
-enter the system, hence the focus on \emph{conservative} solution transfer
-(typically using Galerkin or \(L_2\)-minimizing methods).
-
+be transferred to a \emph{target} mesh.
 When pointwise interpolation is used to transfer a solution, quantities with
 physical meaning (e.g. mass, concentration, energy) may not be conserved.
-To address this, there have been many explorations of
-\emph{conservative interpolation}. Since solution transfer is so commonly
-needed in physical applications, this problem of conservative interpolation
-has been considered already for straight sided meshes.
+In many applications, the field
+must be conserved for physical reasons, e.g. mass or energy cannot leave or
+enter the system, hence this paper focuses on \emph{conservative} solution transfer
+(typically using Galerkin or \(L_2\)-minimizing methods).
+
+%% When pointwise interpolation is used to transfer a solution, quantities with
+%% physical meaning (e.g. mass, concentration, energy) may not be conserved.
+%% To address this, there have been many explorations of
+%% \emph{conservative interpolation}. Since solution transfer is so commonly
+%% needed in physical applications, this ...
+
+The problem of conservative interpolation
+has been considered previously for straight sided meshes.
 However, both to allow for greater
-geometric flexibility and for high order of convergence, this paper will
-consider the case of curved isoparametric\footnote{I.e. the degree of the
-discrete field on the mesh is same as the degree of the shape functions that
-determine the mesh.} meshes. High-order methods
-have the ability to produce highly accurate solutions
-with low dissipation and low dispersion error, however, they typically
-require curved meshes. In addition, curved elements have
-advantages in problems that involve geometries that change over time,
-such as flapping flight or fluid-structure interactions.
+geometric flexibility and for high order of convergence, this paper
+addresses the case of curved isoparametric meshes. This is based on the
+recent interest in so-called high-order methods \cite{Wang2013}, which have the ability to
+produce highly accurate solutions with low dissipation and low dispersion error.
+However, these methods typically require curved meshes to obtain the high accuracy.
+
+%% In addition, curved elements have advantages in problems that involve geometries that change over time,
+%% such as flapping flight or fluid-structure interactions.
 
@@
 \cite{Jiao2004} is used to compare several methods for solution transfer across
-two meshes. However, the problem of constructing a common refinement is
-not discussed there. The problem of constructing such a refinement is
+two meshes. The problem of constructing such a refinement is
 considered in \cite{Farrell2009, Farrell2011} (called a supermesh by
@@
 
-Lagrangian methods treat each point in the
-physical domain as a ``particle'' which moves along a characteristic curve
-over time and then monitor values associated with the particle (heat / energy,
-velocity, pressure, density, concentration, etc.). They are an effective way
-to solve PDEs, even with higher order or non-linear terms \cite{MR3023731}.
-This approach transforms the numerical solution of PDEs into a family of
-numerical solutions to many independent ODEs. It allows the use of familiar
-and well understood ODE solvers. In addition, Lagrangian methods often
-have less restrictive conditions on time steps than Eulerian
-methods\footnote{In Eulerian methods, the mesh is fixed.}.
-When solving PDEs on unstructured meshes
-with Lagrangian methods, the nodes move (since they
-are treated like particles) and the mesh ``travels''.
-A flow-based change to a mesh can cause problems if it
-distorts the mesh until the element
-quality is too low in some mesh elements. Over enough time, the mesh can
-even tangle (i.e. elements begin to overlap).
-
-To deal with distortion, one can allow the mesh to adapt in between time
-steps. In addition to improving mesh quality, mesh
-adaptivity can be used to dynamically focus computational effort to resolve
-sensitive features of a numerical solution. From \cite{Iske2004}
-\begin{quote}
-{\small In order to balance the method's approximation quality and its
-computational costs effectively, adaptivity is an essential requirement,
-especially when modelling multiscale phenomena.}
-\end{quote}
-For more on mesh adaptivity, see \cite{Babuska1978, Peraire1987, Pain2001}.
-
-In either case, the change in the
-mesh between time steps requires transferring a known solution on the
-discarded mesh to the mesh produced by the remeshing process. Without
-the ability to change the mesh, Lagrangian methods (or, more generally,
-ALE\footnote{ALE, or Arbitrary Lagrangian-Eulerian methods are not constrained
-by a fixed computational mesh (the Eulerian approach) or a fixed fluid flow
-(the Lagrangian approach) and typically combine the benefits of both approaches
-to create composite methods} \cite{Hirt1974}) would not be useful, since after
-a limited time the mesh will distort.
-
-To allow for greater geometric flexibility and for high order of convergence,
-curved mesh elements can be used in the finite element method. Though the
-complexity of a method can steeply rise when allowing curved elements, the
-trade for high-order convergence can be worth it. (See \cite{Wang2013} for
-more on high-order CFD methods.) Curved meshes can typically
-represent a given geometry with far fewer elements than a straight sided mesh.
-The increase in accuracy also allows for the use of fewer elements, which
-in turn can also facilitate a reduction in the overall computation time.
-
-\begin{figure}
-  \includegraphics{element_distortion.pdf}
-  \centering
-  \captionsetup{width=.75\linewidth}
-  \caption{Movement of nodes in a quadratic element under distortion caused
-    by particle motion along the velocity field \(\left[ y^2 \; 1 \right]^T\)
-    from \(t = 0\) to \(t = 1\) with \(\Delta t = 1/2\). The green curves
-    represent the characteristics that each node travels along.}
-  \label{fig:element-distortion}
-\end{figure}
-
-Even if the domain has no inherent curvature, high-order (degree \(p\)) shape
-functions allow for order \(p + 1\) convergence, which is desirable in
-its own right. However, even in such cases, a Lagrangian method must either
-curve the mesh or information about the flow of the geometry will be lost.
-Figure~\ref{fig:element-distortion} shows what happens to a given
-quadratic element as the nodes move along the
-characteristics given by the velocity field
-\(\left[ \begin{array}{c c} y^2 & 1 \end{array}\right]^T\).
-This element uses the triangle vertices and edge
-midpoints to determine the shape functions. However, as the nodes move
-with the flow, the midpoints are no longer on the lines connecting
-the vertex nodes. To allow the mesh to more accurately represent the
-solution, the edges can instead curve so that the midpoint nodes remain
-halfway between (i.e. half of the parameter space) the vertex nodes along
-an edge.
-
-In multiphysics simulations, a problem is partitioned into physical components.
-This partitioning can apply to both the physical domain (e.g. separating a
-solid and fluid at an interface) and the simulation solution itself (e.g.
-solving for pressure on one mesh and velocity on another). Each (multi)physics
-component is solved for on its own mesh. When the components interact, the
-simulation solution must be transferred between those meshes.
-
-In a similar category of application, solution transfer enables the comparison
-of solutions defined on different meshes. For example, if a reference
-solution is known on a very fine special-purpose mesh, the error can be
-computed for a coarse mesh by transferring the solution from the fine
-mesh and taking the difference. Or, if the same method is used on
-different meshes of the same domain, the resulting computed solutions can
-be compared via solution transfer. Or, if two different methods use two
-different meshes of the same domain, a solution may need to be transferred
-across these meshes for comparison.
+%% Lagrangian methods treat each point in the
+%% physical domain as a ``particle'' which moves along a characteristic curve
+%% over time and then monitor values associated with the particle (heat / energy,
+%% velocity, pressure, density, concentration, etc.). They are an effective way
+%% to solve PDEs, even with higher order or non-linear terms \cite{MR3023731}.
+%% This approach transforms the numerical solution of PDEs into a family of
+%% numerical solutions to many independent ODEs. It allows the use of familiar
+%% and well understood ODE solvers. In addition, Lagrangian methods often
+%% have less restrictive conditions on time steps than Eulerian
+%% methods\footnote{In Eulerian methods, the mesh is fixed.}.
+%% When solving PDEs on unstructured meshes
+%% with Lagrangian methods, the nodes move (since they
+%% are treated like particles) and the mesh ``travels''.
+%% A flow-based change to a mesh can cause problems if it
+%% distorts the mesh until the element
+%% quality is too low in some mesh elements. Over enough time, the mesh can
+%% even tangle (i.e. elements begin to overlap).
+
+%% To deal with distortion, one can allow the mesh to adapt in between time
+%% steps. In addition to improving mesh quality, mesh
+%% adaptivity can be used to dynamically focus computational effort to resolve
+%% sensitive features of a numerical solution. From \cite{Iske2004}
+%% \begin{quote}
+%% {\small In order to balance the method's approximation quality and its
+%% computational costs effectively, adaptivity is an essential requirement,
+%% especially when modelling multiscale phenomena.}
+%% \end{quote}
+%% For more on mesh adaptivity, see \cite{Babuska1978, Peraire1987, Pain2001}.
+
+%% In either case, the change in the
+%% mesh between time steps requires transferring a known solution on the
+%% discarded mesh to the mesh produced by the remeshing process. Without
+%% the ability to change the mesh, Lagrangian methods (or, more generally,
+%% ALE\footnote{ALE, or Arbitrary Lagrangian-Eulerian methods are not constrained
+%% by a fixed computational mesh (the Eulerian approach) or a fixed fluid flow
+%% (the Lagrangian approach) and typically combine the benefits of both approaches
+%% to create composite methods} \cite{Hirt1974}) would not be useful, since after
+%% a limited time the mesh will distort.
+
+%% To allow for greater geometric flexibility and for high order of convergence,
+%% curved mesh elements can be used in the finite element method. Though the
+%% complexity of a method can steeply rise when allowing curved elements, the
+%% trade for high-order convergence can be worth it. (See \cite{Wang2013} for
+%% more on high-order CFD methods.) Curved meshes can typically
+%% represent a given geometry with far fewer elements than a straight sided mesh.
+%% The increase in accuracy also allows for the use of fewer elements, which
+%% in turn can also facilitate a reduction in the overall computation time.
+
+%% \begin{figure}
+%%   \includegraphics{element_distortion.pdf}
+%%   \centering
+%%   \captionsetup{width=.75\linewidth}
+%%   \caption{Movement of nodes in a quadratic element under distortion caused
+%%     by particle motion along the velocity field \(\left[ y^2 \; 1 \right]^T\)
+%%     from \(t = 0\) to \(t = 1\) with \(\Delta t = 1/2\). The green curves
+%%     represent the characteristics that each node travels along.}
+%%   \label{fig:element-distortion}
+%% \end{figure}
+
+%% Even if the domain has no inherent curvature, high-order (degree \(p\)) shape
+%% functions allow for order \(p + 1\) convergence, which is desirable in
+%% its own right. However, even in such cases, a Lagrangian method must either
+%% curve the mesh or information about the flow of the geometry will be lost.
+%% Figure~\ref{fig:element-distortion} shows what happens to a given
+%% quadratic element as the nodes move along the
+%% characteristics given by the velocity field
+%% \(\left[ \begin{array}{c c} y^2 & 1 \end{array}\right]^T\).
+%% This element uses the triangle vertices and edge
+%% midpoints to determine the shape functions. However, as the nodes move
+%% with the flow, the midpoints are no longer on the lines connecting
+%% the vertex nodes. To allow the mesh to more accurately represent the
+%% solution, the edges can instead curve so that the midpoint nodes remain
+%% halfway between (i.e. half of the parameter space) the vertex nodes along
+%% an edge.
+
+%% In multiphysics simulations, a problem is partitioned into physical components.
+%% This partitioning can apply to both the physical domain (e.g. separating a
+%% solid and fluid at an interface) and the simulation solution itself (e.g.
+%% solving for pressure on one mesh and velocity on another). Each (multi)physics
+%% component is solved for on its own mesh. When the components interact, the
+%% simulation solution must be transferred between those meshes.
+
+%% In a similar category of application, solution transfer enables the comparison
+%% of solutions defined on different meshes. For example, if a reference
+%% solution is known on a very fine special-purpose mesh, the error can be
+%% computed for a coarse mesh by transferring the solution from the fine
+%% mesh and taking the difference. Or, if the same method is used on
+%% different meshes of the same domain, the resulting computed solutions can
+%% be compared via solution transfer. Or, if two different methods use two
+%% different meshes of the same domain, a solution may need to be transferred
+%% across these meshes for comparison.
 
@@
 
-\begin{figure}
-  \includegraphics{main_figure29.pdf}
-  \centering
-  \captionsetup{width=.75\linewidth}
-  \caption{Partially overlapping meshes on a near identical domain. Both are
-    linear meshes that approximate the unit disc in \(\reals^2\). The outermost
-    columns show how the domain of each mesh can be expanded so they agree.}
-  \label{fig:partially-overlapping}
-\end{figure}
+In addition to conservation, there are many other considerations for a
+solution transfer method that are important in various applications. For
+example, since our focus is on high-order methods, these typically produce
+oscillations in the solutions that can be non-physical and break the numerical
+solvers. This can happen for the standard Galerkin projections that we
+consider here, which means that e.g. discontinuities such as shocks in the
+solution could become nonphysical after our solution transfer. Various
+solutions to this have been proposed before, often referred to as limiting or
+bound/monotonicity preserving methods, see e.g. \cite{MR3302403,Anderson2018}
+where several approaches are studied including a high-order extension of the
+flux-corrected transport (FCT) method. Other considerations for a solution
+transfer scheme include the preservation of additional constraints, such
+as the divergence or the curl of the solution.
 
@@
 
-The case of partially overlapping meshes can be addressed in particular
-cases (i.e. with more information). For example, consider a problem
-defined on \(\Omega = \reals^2\) and solution
-that tends towards zero as points tend to infinity. A typical approach
-may be to compute the solution on a circle of large enough radius and
-consider the numerical solution to be zero outside the circle.
-Figure~\ref{fig:partially-overlapping} shows how solution transfer could be
-performed in such cases when the meshes partially overlap: construct a
-simple region containing both computational domains and then mesh the
-newly introduced area. However, the assumption that the numerical solution
-is zero in the newly introduced area is very specific and
-a similar approach may not apply in other cases of partial overlap.
-
-Some attempts (\cite{Berger1987, Chesshire1994, Cai1999}) have been
-made to interpolate fluxes between overlapping meshes. These perform
-an interpolation on the region common to both meshes and then numerically
-solve the PDE to determine the values on the uncovered elements.
-
-When solving some PDEs with viscoelastic fields, additional nodes must be
-tracked at quadrature points. As the mesh travels, these quadrature points
-must be moved as well in a way that is consistent with the standard
-nodes that define the element. The solution transfer method described here
-does not provide a way either to determine quadrature points on a
-target mesh or to map the field onto known quadrature points.
+%%%%%%%%%%%%%%%
+%% Overlapping meshes - exclude for now
+
+%% \begin{figure}
+%%   \includegraphics{main_figure29.pdf}
+%%   \centering
+%%   \captionsetup{width=.75\linewidth}
+%%   \caption{Partially overlapping meshes on a near identical domain. Both are
+%%     linear meshes that approximate the unit disc in \(\reals^2\). The outermost
+%%     columns show how the domain of each mesh can be expanded so they agree.}
+%%   \label{fig:partially-overlapping}
+%% \end{figure}
+
+%% The case of partially overlapping meshes can be addressed in particular
+%% cases (i.e. with more information). For example, consider a problem
+%% defined on \(\Omega = \reals^2\) and solution
+%% that tends towards zero as points tend to infinity. A typical approach
+%% may be to compute the solution on a circle of large enough radius and
+%% consider the numerical solution to be zero outside the circle.
+%% Figure~\ref{fig:partially-overlapping} shows how solution transfer could be
+%% performed in such cases when the meshes partially overlap: construct a
+%% simple region containing both computational domains and then mesh the
+%% newly introduced area. However, the assumption that the numerical solution
+%% is zero in the newly introduced area is very specific and
+%% a similar approach may not apply in other cases of partial overlap.
+
+%% Some attempts (\cite{Berger1987, Chesshire1994, Cai1999}) have been
+%% made to interpolate fluxes between overlapping meshes. These perform
+%% an interpolation on the region common to both meshes and then numerically
+%% solve the PDE to determine the values on the uncovered elements.
+
+%%%%%%%%%%%%%%%
+
+%% When solving some PDEs with viscoelastic fields, additional nodes must be
+%% tracked at quadrature points. As the mesh travels, these quadrature points
+%% must be moved as well in a way that is consistent with the standard
+%% nodes that define the element. The solution transfer method described here
+%% does not provide a way either to determine quadrature points on a
+%% target mesh or to map the field onto known quadrature points.
 
@@
 elements are straight sided but the shape functions are higher degree).
-However, when the elements aren't straight side the isoparametric mapping
+However, when the elements aren't straight sided the isoparametric mapping
 changes the underlying function space.

### 2024-09-07 doc/paper.tex
Final updates for revised manuscript. Addressing a few more reviewer comments. Adding \ref commands for (optionally) highlighting the changes.

@@
 \newcommand{\utri}{\mathcal{U}}
+
+%\newcommand{\rev}[1]{\textcolor{red}{#1}}
+\newcommand{\rev}[1]{#1}
 
@@
 has practical applications to many methods in
-computational physics. For example, by allowing the underyling
+computational physics. \rev{For example, by allowing the underyling
 computational domain to change during a simulation, computational
@@
 requires translating the numerical solution from the old mesh to the new,
-i.e. solution transfer \cite{Babuska1978,Peraire1987,Pain2001,Iske2004}. As another example, Lagrangian or particle-based
+\rev{i.e. solution transfer \cite{Babuska1978,Peraire1987,Pain2001,Iske2004}}}. As another example, Lagrangian or particle-based
 methods treat each node in the mesh as a particle and so with each timestep the
-mesh travels \emph{with} the fluid \cite{MR3023731}.
+\rev{mesh travels \emph{with} the fluid \cite{MR3023731}.
 However, over (typically short) time the mesh
 becomes distorted and suffers a loss in element quality which eventually causes
-inaccurate solutions. To overcome this, the
+inaccurate solutions.} To overcome this, the
 domain must be remeshed or rezoned and the solution must be
-transferred (remapped) onto the new mesh configuration. A related more general
+transferred (remapped) onto the new mesh configuration. \rev{A related more general
 class of methods is the Arbitrary Lagrangian-Eulerian (ALE) method, which
@@
 by a fixed fluid flow (the Lagrangian approach) and typically combine the benefits
-of both approaches \cite{Hirt1974,MR3302403}.
+of both approaches \cite{Hirt1974,MR3302403}.}
 
@@
 geometric flexibility and for high order of convergence, this paper
-addresses the case of curved isoparametric meshes. This is based on the
+addresses the case of curved isoparametric meshes. \rev{This is based on the
 recent interest in so-called high-order methods \cite{Wang2013}, which have the ability to
 produce highly accurate solutions with low dissipation and low dispersion error.
-However, these methods typically require curved meshes to obtain the high accuracy.
+However, these methods typically require curved meshes to obtain the high accuracy.}
 
@@
 and as a result much of the existing literature focuses on mesh-mesh
-pairs that will occur during an ALE-based simulation. Many ALE methods
+pairs that will occur during an ALE-based simulation. \rev{Many ALE methods
 modify the mesh during simulation: when flow-based
@@
 diagonal is switched in a pair of elements) or elements are subdivided
-or combined. These operations are inherently local, hence the solution
+or combined.} These operations are inherently local, hence the solution
 transfer can be done locally across known neighbors. Typically, this
@@
 
-In addition to conservation, there are many other considerations for a
+\rev{In addition to conservation, there are many other considerations for a
 solution transfer method that are important in various applications. For
@@
 transfer scheme include the preservation of additional constraints, such
-as the divergence or the curl of the solution.
+as the divergence or the curl of the solution.}
 
@@
 target mesh is contained in the donor mesh. This ensures that the solution
-transfer is \emph{interpolative}. In the case where all target elements are
+transfer is \rev{\emph{interpolative}}. In the case where all target elements are
 partially covered, \emph{extrapolation} could be used to extend a solution
@@
 \(\left[0, 1\right]\) when \(s\) is as well. Due to this fact, the
-curve must be contained in the convex hull of its control points.
+curve must be contained in the convex hull of \rev{its} control points.
 
@@
 diffeomorphic to \(\utri\), i.e. \(b(s, t)\) is bijective and has
-an invertible Jacobian everywhere. We must also have the orientation
+an \rev{invertible Jacobian everywhere}. We must also have the orientation
 preserved, i.e. the Jacobian must have positive determinant. For example, in
@@
 \(\phi_D^{(j)}\) and a known field \(\bm{q}_D = \sum_j d_j \phi_D^{(j)}\)
-\footnote{This is somewhat a simplification. In CG (continuous Galerkin, as
-opposed to DG or discontinuous Galerkin), some coefficients will be paired
+\footnote{This is somewhat a simplification. \rev{In CG (continuous Galerkin, as
+opposed to DG or discontinuous Galerkin)}, some coefficients will be paired
 with multiple shape functions, such as the coefficient at a vertex node.}
@@
 but that is equivalent to removing some of the basis functions which may
-in turn make the projection non-conservative. This is because the removed
+\rev{in turn} make the projection non-conservative. This is because the removed
 basis functions may have been used in \(1 = \sum_j u_j \phi_{T}^{(j)}\).
@@
 elements of the target mesh, or even across shape functions
-\(\phi_T^{(j)}\). Spatial binning techniques for mesh elements could also be
-used to improve the initial brute-force search as in \cite{Weiss16_imr}.
+\(\phi_T^{(j)}\). \rev{Spatial binning techniques for mesh elements could also be
+used to improve the initial brute-force search as in \cite{Weiss16_imr}.}
 
@@
 elements are straight sided but the shape functions are higher degree).
-However, when the elements aren't straight sided the isoparametric mapping
+However, when the elements aren't straight \rev{sided} the isoparametric mapping
 changes the underlying function space.
@@
 coincide) so the subdivision process breaks down.
+
+\rev{In all of our experiments, we did not encounter any of these difficulties with our implementation.
+However, for fail-safe code, additional fallback strategies would be required, and we refer the reader to the extensive literature for further details on covering all possible special cases that might occur \cite{Sederberg1986,Sederberg1990,Kim1998}.}
 

### 2024-09-24 noxfile.py
Update to `py=` for newer `nox`.

@@ -23,7 +23,7 @@ import py.path
 
 
 NOX_DIR = os.path.abspath(os.path.dirname(__file__))
-SINGLE_INTERP = "python3.7"
+DEFAULT_INTERPRETER = "python3.7"
 
 
 def get_path(*names):
@@ -59,10 +59,8 @@ def build_tex_file(session, base, new_id, extensions=()):
     session.run("python", modify_id, "--base", path, "--id", new_id)
 
 
-@nox.session
+@nox.session(py=DEFAULT_INTERPRETER)
 def build_tex(session):
-    session.interpreter = SINGLE_INTERP
-
     if py.path.local.sysfind("pdflatex") is None:
         session.skip("`pdflatex` must be installed")
 
@@ -82,9 +80,8 @@ def build_tex(session):
     )
 
 
-@nox.session
+@nox.session(py=DEFAULT_INTERPRETER)
 def make_images(session):
-    session.interpreter = SINGLE_INTERP
     # Install all dependencies.
     session.install("--requirement", "make-images-requirements.txt")
     # Run the script(s).
@@ -99,10 +96,8 @@ def make_images(session):
         session.run("python", script, env=env)
 
 
-@nox.session
+@nox.session(py=DEFAULT_INTERPRETER)
 def update_requirements(session):
-    session.interpreter = SINGLE_INTERP
-
     if py.path.local.sysfind("git") is None:
         session.skip("`git` must be installed")
 

### 2024-09-24 noxfile.py
Added `blacken` session to `nox` and ran it.

@@ -113,3 +113,10 @@ def update_requirements(session):
             "pip-compile", "--upgrade", "--output-file", txt_name, in_name
         )
         session.run("git", "add", txt_name)
+
+
+@nox.session(py=DEFAULT_INTERPRETER)
+def blacken(session):
+    """Run black code formatter."""
+    session.install("black")
+    session.run("black", "--line-length", "79", ".")

### 2024-09-24 scripts/modify_pdf_id.py

@@ -22,7 +22,7 @@ import argparse
 
 
 SPLIT_TEXT = b"\n/ID [<"
-ID_LINE = u"{0}> <{0}>]"
+ID_LINE = "{0}> <{0}>]"
 
 
 def verify_id_snippet(id_snippet):

### 2024-09-24 noxfile.py
Address newer way in `nox` to say "no virtualenv".

@@ -59,16 +59,13 @@ def build_tex_file(session, base, new_id, extensions=()):
     session.run("python", modify_id, "--base", path, "--id", new_id)
 
 
-@nox.session(py=DEFAULT_INTERPRETER)
+@nox.session(python=False)
 def build_tex(session):
     if py.path.local.sysfind("pdflatex") is None:
         session.skip("`pdflatex` must be installed")
 
     if py.path.local.sysfind("bibtex") is None:
         session.skip("`bibtex` must be installed")
-
-    # No need to create a virtualenv.
-    session.virtualenv = False
 
     session.chdir(get_path("doc"))
 

### 2024-09-24 scripts/distort.py
Remove unused images + accompanying scripts.

@@ -1,153 +1,0 @@
-# Licensed under the Apache License, Version 2.0 (the "License");
-# you may not use this file except in compliance with the License.
-# You may obtain a copy of the License at
-#
-#     https://www.apache.org/licenses/LICENSE-2.0
-#
-# Unless required by applicable law or agreed to in writing, software
-# distributed under the License is distributed on an "AS IS" BASIS,
-# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
-# See the License for the specific language governing permissions and
-# limitations under the License.
-
-import bezier
-import matplotlib.pyplot as plt
-import numpy as np
-
-import plot_utils
-
-
-ALPHA = 0.375
-NODE_COLORS = (plot_utils.BLUE, plot_utils.PURPLE, "black")
-
-
-def point_on_characteristic(xv, yv, t):
-    yt = yv + t
-    xt = xv + (yt * yt * yt - yv * yv * yv) / 3
-    return xt, yt
-
-
-def get_title(t):
-    if t == int(t):
-        return "$t = {:d}.0$".format(int(t))
-    else:
-        return "$t = {:g}$".format(t)
-
-
-def distort_cubic_tri():
-    node1 = np.array([-0.75, 0.0])
-    node2 = np.array([2.25, -1.5])
-    node3 = np.array([1.5, 1.5])
-    control_points = np.array(
-        [
-            node1,
-            0.5 * (node1 + node2),
-            node2,
-            0.5 * (node1 + node3),
-            0.5 * (node2 + node3),
-            node3,
-        ]
-    )
-
-    figure, all_axes = plt.subplots(2, 3, sharex=True, sharey=True)
-    min_y = -1.65
-    max_y = 2.8
-    control_x = control_points[:, 0]
-    control_y = control_points[:, 1]
-    bezier_nodes = np.empty((2, len(control_x)), order="F")
-
-    # First add characteristic curves to the top row of axes.
-    for i, xv in enumerate(control_x):
-        yv = control_y[i]
-        min_t = min_y - yv
-        max_t = max_y - yv
-        t_vals = np.linspace(min_t, max_t, 100)
-        to_plot = point_on_characteristic(xv, yv, t_vals)
-        for ax in all_axes[0, :]:
[…]

### 2024-09-24 noxfile.py
Use `py=False` for consistency.

@@ -59,7 +59,7 @@ def build_tex_file(session, base, new_id, extensions=()):
     session.run("python", modify_id, "--base", path, "--id", new_id)
 
 
-@nox.session(python=False)
+@nox.session(py=False)
 def build_tex(session):
     if py.path.local.sysfind("pdflatex") is None:
         session.skip("`pdflatex` must be installed")

### 2024-09-24 noxfile.py
Remove unused `make_images` and related.
Once `distort.py` was deleted, this became deprecated.

@@ -78,42 +78,7 @@ def build_tex(session):
 
 
 @nox.session(py=DEFAULT_INTERPRETER)
-def make_images(session):
-    # Install all dependencies.
-    session.install("--requirement", "make-images-requirements.txt")
-    # Run the script(s).
-    # Make sure
-    # - Custom ``matplotlibrc`` is used
-    # - Code in ``src/`` is importable
-    # - PDFs have deterministic ``CreationDate``
-    env = {"MATPLOTLIBRC": get_path("images"), "SOURCE_DATE_EPOCH": "0"}
-    script_paths = ("distort.py",)
-    for script_path in script_paths:
-        script = get_path("scripts", script_path)
-        session.run("python", script, env=env)
-
-
-@nox.session(py=DEFAULT_INTERPRETER)
-def update_requirements(session):
-    if py.path.local.sysfind("git") is None:
-        session.skip("`git` must be installed")
-
-    # Install all dependencies.
-    session.install("pip-tools")
-
-    # Update all of the requirements file(s).
-    names = ("make-images",)
-    for name in names:
-        in_name = "{}-requirements.in".format(name)
-        txt_name = "{}-requirements.txt".format(name)
-        session.run(
-            "pip-compile", "--upgrade", "--output-file", txt_name, in_name
-        )
-        session.run("git", "add", txt_name)
-
-
-@nox.session(py=DEFAULT_INTERPRETER)
 def blacken(session):
     """Run black code formatter."""
-    session.install("black")
+    session.install("black >= 23.3.0")
     session.run("black", "--line-length", "79", ".")

### 2024-09-24 scripts/plot_utils.py

@@ -1,45 +1,0 @@
-# Licensed under the Apache License, Version 2.0 (the "License");
-# you may not use this file except in compliance with the License.
-# You may obtain a copy of the License at
-#
-#     https://www.apache.org/licenses/LICENSE-2.0
-#
-# Unless required by applicable law or agreed to in writing, software
-# distributed under the License is distributed on an "AS IS" BASIS,
-# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
-# See the License for the specific language governing permissions and
-# limitations under the License.
-
-"""Shared utilities and settings for plotting."""
-
-
-import os
-
-import seaborn
-
-
-# As of ``0.9.0``, this palette has (BLUE, ORANGE, GREEN, RED, PURPLE, BROWN).
-_COLORS = seaborn.color_palette(palette="deep", n_colors=6)
-BLUE = _COLORS[0]
-GREEN = _COLORS[2]
-PURPLE = _COLORS[4]
-del _COLORS
-TEXT_SIZE = 10
-TICK_SIZE = 7
-
-
-def set_styles():
-    """Set the styles used for plotting."""
-    seaborn.set(style="white")
-
-
-def get_path(*parts):
-    """Get a file path in the ``images/`` directory.
-
-    This assumes the script is currently in the ``scripts/``
-    directory.
-    """
-    curr_dir = os.path.abspath(os.path.dirname(__file__))
-    root_dir = os.path.dirname(curr_dir)
-    images_dir = os.path.join(root_dir, "images")
-    return os.path.join(images_dir, *parts)

### 2024-09-24 revision/cover.tex
Merge `revision/` directory in (from `revision` branch).

\documentclass{letter}
\usepackage{amssymb,amsmath}
\usepackage{graphicx}
\usepackage{scrextend}
\usepackage{bm}
\usepackage{color}

\oddsidemargin=0in
\evensidemargin=0in
\textwidth=6.5in
\topmargin=-.5in
\textheight=8.5in

\renewcommand{\rq}[1]{
\vspace{8pt}
\begin{addmargin}[2em]{2em}
\it
\color{blue}{    
  #1
}
\end{addmargin}\vspace{12pt}}

\begin{document}
\begin{letter}{}

\opening{}

Commun. Appl. Math. Comput. Sci.\\[10pt]
\textit{Manuscript}: HIGH-ORDER SOLUTION TRANSFER BETWEEN CURVED TRIANGULAR
MESHES \\[10pt]
\textbf{Revisions and Responses to Reviewers}\\[10pt]

We would like to thank all reviewers for the insightful and helpful comments.
These comments and corrections have proven to be very useful in correcting
errors and improving the quality of the manuscript.

Responses to general and specific comments are found below.

\closing{Sincerely, \\ \ \\ \ \\
\parbox{\textwidth}{
Danny Hermes\\ \ \\
Per-Olof Persson\\
Department of Mathematics,\\University of California, Berkeley,\\
Berkeley, CA, 94720-3840, USA\\
\texttt{persson@berkeley.edu}}}

\pagebreak
\clearpage

\textbf{Reviewer C.}

\textbf{General comments.}

\begin{itemize} \renewcommand\labelitemi{--}

\item \rq{
This paper presents a L2 Galerkin projection method for a globally
conservative transfer of solutions between two higher-order curvilinear
triangular meshes. The authors use B\'{e}zier curves to represent the curved
edges of the meshes. Their procedure consists of three steps: \\
\ \\
1. Finding candidate source cells that potentially intersect each target mesh
   This is done by a brute force search for the first pair and then a walking
   algorithm to find candidates for the rest of the target triangles. They
   say their method is \(\mathcal{O}\left(N_d + N_t\right)\) which is better
   than what would be obtained
   by a tree search --- \(\mathcal{O}\left(N_t \log\left(N_d\right)\right)\) for
   sufficiently large meshes depending on
   the constants.\\
\ \\
2. Computing the domains of intersection between the B\'{e}zier triangles
   This procedure detailed is the Appendix A.1 / A.2. First they use a
   subdivision of B\'{e}zier curves to localize intervals in which intersection
   of each pair of lies. They then use Newtwon's method to find the actual
   point of intersection which they point out has trouble for nearly tangential
   cases. No particular fall back solution is offered for cases where Newton's
   method has trouble.\\
\ \\
3. Computing the matrices required to solve for the target field
   This involves integrating of weak forms of the integrals over the
   intersection domains of the donor and target triangles. This is done by
   transforming the area integrals into integrals over the curved edges of the
   intersection domains.\\
 \ \\
The authors present convergence results for three fields with meshes
of different order on a square and circular domain. The results show
faithful reproduction of the expected order of convergence. Of course
the weakness of the method is the computation of the intersection of
domains which is prone to convergence issues. The second weakness is
the difficulty in extending the technique to 3D. \\
\ \\
The paper is definitely one of a handful to tackle the difficult topic
of remapping between higher order meshes. Notably, the authors have
omitted to mention the work of Anderson, Dobrev, Kolev and Rieben on
``Monotonicity oin High-Order Curviliniear Finite Element ALE Remap."
It is certainly an important topic, one that has constrained the use
of High-order elements for ALE simulations.}

  Thank you for this summary, and yes we completely agree that 3D and geometry
  robustness is left for future work. We appreciate the reference to
  monotonic remaps, we have added this and other references to the new revision.

\item \rq{
The paper is generally well written and presents a clear mathematical
description of the methods used. Only the introduction is a little
meandering and at times repeats itself --- this could use some
tightening up.}

  We agree on this, and have made a major rewrite of the entire introduction.
  In particular, we removed Fig 1.1 and shorted it by about 50\%.

\item \rq{
Suggestions for improvement:
1. Incorporate A.1 and A.2 into main text. These are essential parts of the
procedure and there is no good reason to relegate them to the Appendix.}

  We looked into this, but prefer to keep them as separate appendices.
  Although an important part of the procedure, B\'ezier intersections
  by subdivisions is a big topic with lots of prior work, and not our
  main contribution. So we think the main text gets easier to read by
  leaving these details to the end.

\item \rq{
2. Present results of remap against two different meshes of domains in addition
to convergence results for nested refinement. Some metrics could be
conservation error, and L2 norm of the approximation error.}

  Note that our nested refinement convergence study does also include
  the transfer from a different mesh, at each level of refinement, and
  the errors are in the L2 norm. So we felt that this is a fairly
  complete experimental check for correctness. We looked into adding
  conservation errors, but since they are zero analytically by design, we
  only got machine tolerance errors and used it mostly as a verification of
  our codes.

\item \rq{
3. Some discussion of bounds preservation or monotonicity of the solution
should be incorporated (important for non-physical solutions)}

  Good suggestion, we have added a discussion about this in the introduction
  with citations. Although beyond the scope of this paper, we believe it is
  likely that our techniques can be extended to other types of projections.

\item \rq{
4. Suggest reasonable fall-back strategies for when the intersection solution
runs into trouble.}

  We added a comment about this at in section A.2. In short, our implementation
  worked fine for all our tests, but in general it is of course true that one
  would need special cases and fallback strategies.

\end{itemize}

\textbf{Reviewer Y.}

\textbf{Summary:}

\begin{itemize} \renewcommand\labelitemi{--}

\item \rq{
The authors develop a methodology for mapping / interpolating data
from a given ``donor" mesh to a given ``target" mesh (with different
topologies / geometries). The proposed method is valid for 2D triangular meshes
of high-polynomial degree and for scalar fields approximated with DG basis
functions of high-polynomial degree. Such a technique is quite useful for
many applications including code-to-code coupling of solution data between
different computational meshes, embedded meshing methods and remapping methods
in arbitrary Lagrangian-Eulerian approaches. The proposed method is
conservative by design and makes use of novel techniques based on
B\'{e}zier-curves and general integration over curved polygons. While limited
in its scope (e.g., 2D, triangular topologies, scalar fields), the proposed
method is both novel and impressive. The paper is well written and clearly
explains all of its concepts / methodologies.}

Thank you very much!

\end{itemize}

\textbf{Detailed Comments:}

\begin{itemize} \renewcommand\labelitemi{--}

\item \rq{
If this technique were to be used in ALE codes for the remapping phase, there
must be some additional work done to handle the case of spatially discontinuous
fields. In ALE hydrodynamics, material contacts / interfaces can be captured
exactly during the Lagrangian phase by aligning the computational mesh with
the material discontinuity. During the ALE remap phase, this discontinuity
must be handled without violating local bounds (i.e. introducing new local
extremum / oscillations). For remapping methods which are based on solving a
transport (advection) equation from the old (or donor) to the new (or target)
mesh, this is typically handled using flux-corrected transport methods which
blend monotone 1st order methods with high order methods in a non-linear way.
One possible approach for handling this in the author's proposed method is to
use a type of limited FCT based L2 projection for calculating the overlap
integrals as proposed in [1]. In this technique, element-wise L2 projection
can be done that is guaranteed monotone even for discontinuous functions
provided a well-known monotone low order element-based solution can be found.}

  Thank you for these suggestions, and note that the previous reviewer had
  similar comments as well. We have added a paragraph of discussion of this,
  including references, but left the actual work for future extensions.

\item \rq{
The graphic depiction of figure 1.1 is useful, but it could benefit from having
different colors / markers to designate the particles associated with the
initial element for each of the time slices in the top row. For example, in the
second column, top row of the figure, the points associated with \(t = 0.5\)
should have a different color or marker than the ones associated
with \(t = 0.0\).}

  Thank you, we did at first update the figure to have more clear
  colors, but then based on suggestions from the other reviewers we
  ended up shortening the introduction and removing this figure from
  the paper!

\item \rq{
I believe the brute force search that is used in section 3.3 could be further
improved by using a binning technique which makes use of a ``spatial
acceleration data structure" (see for example [2]).}

Thank you for this helpful note. We have added a sentence to the end of the
last paragraph in section 3.3: ``Spatial binning techniques for mesh elements
could also be used to improve the initial brute-force search as
in [WZRC16]."

\item \rq{
In the numerical experiments, it is not clear from Figure 4.1 that any of the
donor / target meshes had high-degree polynomial curvature for either the
exterior or interior elements --- was this the case? If so, I believe an image
illustrating the curvature of both the donor / target meshes would be useful to
show.}

Thank you for pointing this out. The green circular region on the right has
been updated to reflect the curvature. The image was previously produced with
a ``shortcut" to reduce image size that just used linear approximations (i.e.
connect the corners) of each edge. The updated image uses 32 points (evenly
spaced in parameter space) along each edge to better reflect the curvature
while still keeping the image size small.

\item \rq{
I would be very curious to see if the authors are able to extend this technique
to 3D meshes as well as quadrilateral / hexahedral element topologies of
arbitrary polynomial degree. It would also be interesting to learn if such a
technique could be used for remapping vector valued field in the spaces
\(H^1_{d}\), \(H\left(\operatorname{curl}\right)\) and
\(H\left(\operatorname{div}\right)\). For the
\(H\left(\operatorname{curl}\right)\) and \(H\left(\operatorname{div}\right)\)
case, the notion of conservation imposes additional constraints (e.g.
preservation of divergence / curl) which might require new techniques in this
geometric based remapping approach.}

  Yes we completely agree. The vector fields and additional constrains can
  probably be incorporated into our procedure, since similar work has been
  done before. Quads are probably very similar to triangles. However, 3D
  is very complex for both tets and hexes so that might need fundamental
  new developments.

\end{itemize}

\textbf{Reviewer M.}

\textbf{Comments from PDF:}

\begin{itemize} \renewcommand\labelitemi{--}

\item \rq{Lot of repetition in Introduction}

  We agree, and the first reviewer made the same comment. We have rewritten
  and shortened it significantly.

\item \rq{
How can it ``leave" the domain? You either have boundary
conditions that prevent the nodes from going out of the domain or you
have a free boundary that moves out.}

You're right, we deleted the remark ``...if it causes the mesh to leave the
domain being analyzed...".

\item \rq{Define ALE}

  We added the definition ``Arbitrary Lagrangian-Eulerian'' at the place it
  is first mentioned.

\item \rq{Sentence structure needs to be fixed}

The sentence fragment ``Or, if two different methods use two different meshes
of the same domain." has been modified to end with ``domain, a solution may
need to be transferred across these meshes for comparison."

\item \rq{Not always. Some ALE methods don't have any mesh modification}

Done. Added caveat ``Many ALE methods modify the mesh during simulation:
when flow-based mesh distortion occurs..." to the beginning of the sentence
that previously started out ``When flow-based mesh distortion occurs...".

\item \rq{Interpolation \(\to\) interpolative?}

Done.

\item \rq{it's \(\to\) its}

Done.

\item \rq{has an invertible Jacobian everywhere}

Done.

\item \rq{CG}

Changed ``In the CG case, some coefficients will..." to ``In CG (continuous
Galerkin, as opposed to DG or discontinuous Galerkin), some coefficients
will..."

\item \rq{term \(\to\) turn}

Done.

\end{itemize}

\end{letter}

\end{document}

### 2024-12-01 doc/paper.tex
Remove commented out sections from `paper.tex`.
Made all edits from the reviewer.

@@
 
-%\newcommand{\rev}[1]{\textcolor{red}{#1}}
 \newcommand{\rev}[1]{#1}
+%%% TODO: remove \rev
 
@@
 \email{persson@berkeley.edu}
-%% \urladdr{persson.berkeley.edu}
 
@@
 \noindent The problem of solution transfer between meshes arises frequently in
-computational physics, e.g. in Lagrangian methods where remeshing
-occurs. The interpolation process must be conservative, i.e. it
+computational physics, e.g., in Lagrangian methods where remeshing
+occurs. The interpolation process must be conservative, i.e., it
 must conserve physical properties, such as mass. We extend previous
@@
 has practical applications to many methods in
-computational physics. \rev{For example, by allowing the underyling
+computational physics. \rev{For example, by allowing the underlying
 computational domain to change during a simulation, computational
@@
 requires translating the numerical solution from the old mesh to the new,
-\rev{i.e. solution transfer \cite{Babuska1978,Peraire1987,Pain2001,Iske2004}}}. As another example, Lagrangian or particle-based
+\rev{that is, solution transfer \cite{Babuska1978,Peraire1987,Pain2001,Iske2004}}}.
+As another example, Lagrangian or particle-based
 methods treat each node in the mesh as a particle and so with each timestep the
@@
 When pointwise interpolation is used to transfer a solution, quantities with
-physical meaning (e.g. mass, concentration, energy) may not be conserved.
-In many applications, the field
-must be conserved for physical reasons, e.g. mass or energy cannot leave or
-enter the system, hence this paper focuses on \emph{conservative} solution transfer
+physical meaning (for instance, mass, concentration, energy) may not be
+conserved. In many applications, the field
+must be conserved for physical reasons, e.g., mass or energy cannot leave or
+enter the system; hence we focus on \emph{conservative} solution transfer
 (typically using Galerkin or \(L_2\)-minimizing methods).
 
-%% When pointwise interpolation is used to transfer a solution, quantities with
-%% physical meaning (e.g. mass, concentration, energy) may not be conserved.
-%% To address this, there have been many explorations of
-%% \emph{conservative interpolation}. Since solution transfer is so commonly
-%% needed in physical applications, this ...
-
 The problem of conservative interpolation
-has been considered previously for straight sided meshes.
+was considered previously for straight sided meshes.
 However, both to allow for greater
-geometric flexibility and for high order of convergence, this paper
-addresses the case of curved isoparametric meshes. \rev{This is based on the
+geometric flexibility and for high order of convergence, we
+address the case of curved isoparametric meshes. \rev{This is based on the
 recent interest in so-called high-order methods \cite{Wang2013}, which have the ability to
@@
 However, these methods typically require curved meshes to obtain the high accuracy.}
-
-%% In addition, curved elements have advantages in problems that involve geometries that change over time,
-%% such as flapping flight or fluid-structure interactions.
 
@@
 
-%% Lagrangian methods treat each point in the
-%% physical domain as a ``particle'' which moves along a characteristic curve
-%% over time and then monitor values associated with the particle (heat / energy,
-%% velocity, pressure, density, concentration, etc.). They are an effective way
-%% to solve PDEs, even with higher order or non-linear terms \cite{MR3023731}.
-%% This approach transforms the numerical solution of PDEs into a family of
-%% numerical solutions to many independent ODEs. It allows the use of familiar
-%% and well understood ODE solvers. In addition, Lagrangian methods often
-%% have less restrictive conditions on time steps than Eulerian
-%% methods\footnote{In Eulerian methods, the mesh is fixed.}.
-%% When solving PDEs on unstructured meshes
-%% with Lagrangian methods, the nodes move (since they
-%% are treated like particles) and the mesh ``travels''.
-%% A flow-based change to a mesh can cause problems if it
-%% distorts the mesh until the element
-%% quality is too low in some mesh elements. Over enough time, the mesh can
-%% even tangle (i.e. elements begin to overlap).
-
-%% To deal with distortion, one can allow the mesh to adapt in between time
-%% steps. In addition to improving mesh quality, mesh
-%% adaptivity can be used to dynamically focus computational effort to resolve
-%% sensitive features of a numerical solution. From \cite{Iske2004}
-%% \begin{quote}
-%% {\small In order to balance the method's approximation quality and its
-%% computational costs effectively, adaptivity is an essential requirement,
-%% especially when modelling multiscale phenomena.}
-%% \end{quote}
-%% For more on mesh adaptivity, see \cite{Babuska1978, Peraire1987, Pain2001}.
-
-%% In either case, the change in the
-%% mesh between time steps requires transferring a known solution on the
-%% discarded mesh to the mesh produced by the remeshing process. Without
-%% the ability to change the mesh, Lagrangian methods (or, more generally,
-%% ALE\footnote{ALE, or Arbitrary Lagrangian-Eulerian methods are not constrained
-%% by a fixed computational mesh (the Eulerian approach) or a fixed fluid flow
-%% (the Lagrangian approach) and typically combine the benefits of both approaches
-%% to create composite methods} \cite{Hirt1974}) would not be useful, since after
-%% a limited time the mesh will distort.
-
-%% To allow for greater geometric flexibility and for high order of convergence,
-%% curved mesh elements can be used in the finite element method. Though the
-%% complexity of a method can steeply rise when allowing curved elements, the
-%% trade for high-order convergence can be worth it. (See \cite{Wang2013} for
-%% more on high-order CFD methods.) Curved meshes can typically
-%% represent a given geometry with far fewer elements than a straight sided mesh.
-%% The increase in accuracy also allows for the use of fewer elements, which
-%% in turn can also facilitate a reduction in the overall computation time.
-
-%% \begin{figure}
-%%   \includegraphics{element_distortion.pdf}
-%%   \centering
-%%   \captionsetup{width=.75\linewidth}
-%%   \caption{Movement of nodes in a quadratic element under distortion caused
-%%     by particle motion along the velocity field \(\left[ y^2 \; 1 \right]^T\)
-%%     from \(t = 0\) to \(t = 1\) with \(\Delta t = 1/2\). The green curves
-%%     represent the characteristics that each node travels along.}
-%%   \label{fig:element-distortion}
-%% \end{figure}
-
-%% Even if the domain has no inherent curvature, high-order (degree \(p\)) shape
-%% functions allow for order \(p + 1\) convergence, which is desirable in
-%% its own right. However, even in such cases, a Lagrangian method must either
-%% curve the mesh or information about the flow of the geometry will be lost.
-%% Figure~\ref{fig:element-distortion} shows what happens to a given
-%% quadratic element as the nodes move along the
-%% characteristics given by the velocity field
-%% \(\left[ \begin{array}{c c} y^2 & 1 \end{array}\right]^T\).
-%% This element uses the triangle vertices and edge
-%% midpoints to determine the shape functions. However, as the nodes move
-%% with the flow, the midpoints are no longer on the lines connecting
-%% the vertex nodes. To allow the mesh to more accurately represent the
-%% solution, the edges can instead curve so that the midpoint nodes remain
-%% halfway between (i.e. half of the parameter space) the vertex nodes along
-%% an edge.
-
-%% In multiphysics simulations, a problem is partitioned into physical components.
-%% This partitioning can apply to both the physical domain (e.g. separating a
-%% solid and fluid at an interface) and the simulation solution itself (e.g.
-%% solving for pressure on one mesh and velocity on another). Each (multi)physics
-%% component is solved for on its own mesh. When the components interact, the
-%% simulation solution must be transferred between those meshes.
-
-%% In a similar category of application, solution transfer enables the comparison
-%% of solutions defined on different meshes. For example, if a reference
-%% solution is known on a very fine special-purpose mesh, the error can be
-%% computed for a coarse mesh by transferring the solution from the fine
-%% mesh and taking the difference. Or, if the same method is used on
-%% different meshes of the same domain, the resulting computed solutions can
-%% be compared via solution transfer. Or, if two different methods use two
-%% different meshes of the same domain, a solution may need to be transferred
-%% across these meshes for comparison.
-
 Conservative solution transfer has been around since the advent of ALE,
@@
 modify the mesh during simulation: when flow-based
-mesh distortion occurs, elements are typically ``flipped'' (e.g. a
+mesh distortion occurs, elements are typically ``flipped'' (for example, a
 diagonal is switched in a pair of elements) or elements are subdivided
-or combined.} These operations are inherently local, hence the solution
+or combined.} These operations are inherently local; hence the solution
 transfer can be done locally across known neighbors. Typically, this
@@
 components of elements from the old mesh and ``swept regions'' from
-neighbouring elements. In \cite{Kucharik2008}, the (locally) changing
+neighboring elements. In \cite{Kucharik2008}, the (locally) changing
 connectivity of the mesh is addressed. In \cite{Garimella2007}, the
@@
 solvers. This can happen for the standard Galerkin projections that we
-consider here, which means that e.g. discontinuities such as shocks in the
+consider here, which means that e.g., discontinuities such as shocks in the
 solution could become nonphysical after our solution transfer. Various
 solutions to this have been proposed before, often referred to as limiting or
-bound/monotonicity preserving methods, see e.g. \cite{MR3302403,Anderson2018}
+bound/monotonicity preserving methods; see, for instance,
+\cite{MR3302403,Anderson2018}
 where several approaches are studied including a high-order extension of the
@@
 
-In this paper, an algorithm for conservative solution transfer between curved
+We describe an algorithm for conservative solution transfer between curved
 meshes will be described. This method applies to meshes in \(\reals^2\).
@@
 
-%%%%%%%%%%%%%%%
-%% Overlapping meshes - exclude for now
-
-%% \begin{figure}
-%%   \includegraphics{main_figure29.pdf}
-%%   \centering
-%%   \captionsetup{width=.75\linewidth}
-%%   \caption{Partially overlapping meshes on a near identical domain. Both are
-%%     linear meshes that approximate the unit disc in \(\reals^2\). The outermost
-%%     columns show how the domain of each mesh can be expanded so they agree.}
-%%   \label{fig:partially-overlapping}
-%% \end{figure}
-
-%% The case of partially overlapping meshes can be addressed in particular
-%% cases (i.e. with more information). For example, consider a problem
-%% defined on \(\Omega = \reals^2\) and solution
-%% that tends towards zero as points tend to infinity. A typical approach
-%% may be to compute the solution on a circle of large enough radius and
-%% consider the numerical solution to be zero outside the circle.
-%% Figure~\ref{fig:partially-overlapping} shows how solution transfer could be
-%% performed in such cases when the meshes partially overlap: construct a
-%% simple region containing both computational domains and then mesh the
-%% newly introduced area. However, the assumption that the numerical solution
-%% is zero in the newly introduced area is very specific and
-%% a similar approach may not apply in other cases of partial overlap.
-
-%% Some attempts (\cite{Berger1987, Chesshire1994, Cai1999}) have been
-%% made to interpolate fluxes between overlapping meshes. These perform
-%% an interpolation on the region common to both meshes and then numerically
-%% solve the PDE to determine the values on the uncovered elements.
-
-%%%%%%%%%%%%%%%
-
-%% When solving some PDEs with viscoelastic fields, additional nodes must be
-%% tracked at quadrature points. As the mesh travels, these quadrature points
-%% must be moved as well in a way that is consistent with the standard
-%% nodes that define the element. The solution transfer method described here
-%% does not provide a way either to determine quadrature points on a
-%% target mesh or to map the field onto known quadrature points.
-
 This paper is organized as follows. Section~\ref{sec:preliminaries}
@@
 \end{equation}
-When dealing with sequences with multiple indices, e.g.
+When dealing with sequences with multiple indices, for example,
 \(s_{m, n} = m + n\), we'll use bold symbols to represent
@@
 
-A \emph{B\'{e}zier triangle} (\cite[Chapter~17]{Farin2001}) is a
+A \emph{B\'{e}zier triangle} \cite[Chapter~17]{Farin2001} is a
 mapping from the unit triangle
@@
 \(\left\{\bm{p}_{i, j, k}\right\}_{i + j + k = n} \subset \reals^d\).
-A B\'{e}zier triangle is a particular kind of B\'{e}zier surface, i.e. one
+A B\'{e}zier triangle is a particular kind of B\'{e}zier surface, i.e., one
 in which there are two cartesian or three barycentric input parameters.
@@
 we'll refer to these as \emph{standard nodes}.
-Figure~\ref{fig:cubic-bezier-example} shows these standard nodes for
+Figure~\ref{fig:cubic-bezier-example} shows these standard nodes form
 a cubic triangle in \(\reals^2\). To see the correspondence,
@@
 This may make working with
-higher degree triangles prohibitively unstable.
+higher-degree triangles prohibitively unstable.
 
 A \emph{valid} B\'{e}zier triangle is one which is
-diffeomorphic to \(\utri\), i.e. \(b(s, t)\) is bijective and has
+diffeomorphic to \(\utri\), that is, \(b(s, t)\) is bijective and has
 an \rev{invertible Jacobian everywhere}. We must also have the orientation
-preserved, i.e. the Jacobian must have positive determinant. For example, in
+preserved, that is, the Jacobian must have positive determinant. For example, in
 Figure~\ref{fig:inverted-element}, the image of \(\utri\) under
@@
 has been used for Lagrangian methods where
-mesh adaptivity is needed (e.g. \cite{CardozeMOP04}). Typically curved
+mesh adaptivity is needed (e.g., \cite{CardozeMOP04}). Typically curved
 elements only have one curved side (\cite{McLeod1972}) since they are used
@@
 B\'{e}zier curves and triangles have a number of mathematical properties
-(e.g. the convex hull property) that lead to elegant geometric
+(e.g., the convex hull property) that lead to elegant geometric
 descriptions and algorithms.
@@
 Note that a B\'{e}zier triangle can be
-determined from many different sources of data (for example the control net
+determined from many different sources of data (for example, the control net
 or the standard nodes). The choice of this data may be changed to suit the
 underlying physical problem without changing the actual mapping. Conversely,
-the data can be fixed (e.g. as the control net) to avoid costly basis
+the data can be fixed (for instance, as the control net) to avoid costly basis
 conversion; once fixed, the equations of motion and other PDE terms can
@@
 
-When defining shape functions (i.e. a basis with geometric meaning) on a
+When defining shape functions (i.e., a basis with geometric meaning) on a
 curved element there are (at least) two choices. When the degree of the
@@
   \itemsep 0em
-  \item \emph{Pre-Image Basis}:
+  \item \emph{preimage basis}:
     \(\phi_{\bm{j}}\left(\bm{n}_{\bm{i}}\right) =
@@
     where \(\widehat{\phi}_{\bm{j}}\) is a canonical basis function
-    on \(\utri\), i.e.
-    \(\widehat{\phi}_{\bm{j}}\) a degree \(p\) bivariate polynomial and
+    on \(\utri\), that is,
+    \(\widehat{\phi}_{\bm{j}}\) is a degree \(p\) bivariate polynomial and
     \(\widehat{\phi}_{\bm{j}}\left(\bm{u}_{\bm{i}}\right) =
-    \delta_{\bm{i} \bm{j}}\)
-  \item \emph{Global Coordinates Basis}:
+    \delta_{\bm{i} \bm{j}}\).
+  \item \emph{global coordinates basis}:
     \(\phi_{\bm{j}}\left(\bm{n}_{\bm{i}}\right) =
-    \delta_{\bm{i} \bm{j}}\), i.e. a canonical basis function
+    \delta_{\bm{i} \bm{j}}\), that is, a canonical basis function
     on the standard nodes \(\left\{\bm{n}_{\bm{i}}\right\}\).
@@
 \end{gather}
-In the \emph{Global Coordinates Basis}, we have
+In the \emph{global coordinates basis}, we have
 \begin{equation}
@@
 \end{equation}
-For the \emph{Pre-Image Basis}, we need the inverse
+For the \emph{preimage basis}, we need the inverse
 and the canonical basis
@@
   \end{array}\right] \quad \text{and} \quad
-\widehat{\phi}_{0, 1, 1}(s, t) = 4 s t
+\widehat{\phi}_{0, 1, 1}(s, t) = 4 s t,
 \end{equation}
@@
 function; due to composition with \(b^{-1}\) we can only guarantee that
-it is algebraic (i.e. it can be defined as the zero set of polynomials
+it is algebraic (i.e., it can be defined as the zero set of polynomials
 with coefficients in \(\reals\left[x, y\right]\)).
@@
 C_1 \cup C_2 \cup C_3 \cup C_4\). Each boundary
-curve is itself a B\'{e}zier curve\footnote{A specialization of a
+curve is itself a B\'{e}zier curve:\footnote{A specialization of a
 B\'{e}zier curve \(b\left(\left[a_1, a_2\right]\right)\)
-is also a B\'{e}zier curve.}:
+is also a B\'{e}zier curve.}
 \(C_1 = b_{0, 0}\left(\left[0, 1/8\right]\right)\),
@@
 Consider a donor mesh \(\mathcal{M}_D\) with shape function basis
-\(\phi_D^{(j)}\) and a known field \(\bm{q}_D = \sum_j d_j \phi_D^{(j)}\)
+\(\phi_D^{(j)}\) and a known field
 \footnote{This is somewhat a simplification. \rev{In CG (continuous Galerkin, as
@@
 with multiple shape functions, such as the coefficient at a vertex node.}
+\(\bm{q}_D = \sum_j d_j \phi_D^{(j)}\)
 and a
@@
 \(\operatorname{supp}(\phi) = \mathcal{T}\).
-Additionally, the shape functions are polynomial degree \(p\) (see
+Additionally, the shape functions are degree-\(p\) polynomials (see
 Section~\ref{subsec:shape-functions} for a discussion of shape functions),
@@
 \min_{\bm{q} \in \mathcal{V}_T}
-\left \lVert \bm{q} - \bm{q}_D \right \rVert_2
+\left \lVert \bm{q} - \bm{q}_D \right \rVert_2,
 \end{equation}
@@
 \int_{\Omega} \bm{q}_D \phi_T^{(j)} \, dV =
-  \int_{\Omega} \bm{q}_T \phi_T^{(j)} \, dV, \qquad \text{for all } j.
+  \int_{\Omega} \bm{q}_T \phi_T^{(j)} \, dV \qquad \text{for all } j.
 \end{equation}
@@
 \(2p\) on \(\reals^2\). The domain of integration \(\mathcal{T}
-= b\left(\utri\right)\) is the image of a (degree \(p\)) map \(b(s, t)\)
+= b\left(\utri\right)\) is the image of a (degree-\(p\)) map \(b(s, t)\)
 from the unit triangle. Using substitution
@@
   \captionsetup{width=.75\linewidth}
-  \caption{All donor elements that cover a target element}
+  \caption{All donor elements that cover a target element.}
   \label{fig:target-elt-all-matching}
@@
 In order to compute \(M_{TD} \bm{d}\), we'll need to compute the
-\emph{common refinement}, i.e. an intermediate mesh that contains
+\emph{common refinement}, that is, an intermediate mesh that contains
 both the donor and target meshes. This will consist of all non-empty
@@
 layer of donor elements that don't intersect \(\mathcal{T}\) because they are
-more likely to intersect the neighbors of \(\mathcal{T}\)\footnote{In the
+more likely to intersect the neighbors of \(\mathcal{T}\).\footnote{In the
 very unlikely case that the boundary of \(\mathcal{T}\)
@@
 \(\mathcal{T}\) so the first layer of non-intersected donor
-elements must be considered.}. Using the list of intersected elements, a
+elements must be considered.} Using the list of intersected elements, a
 neighbor of \(\mathcal{T}\) can find a donor element it intersects with in
@@
 
-For special cases, e.g. ALE methods, the initial brute-force search
+For special cases such as ALE methods, the initial brute-force search
 can be reduced to \(\bigO{1}\). This could be enabled by tracking
@@
 
-First a discussion of a method not used. A somewhat simple approach would be
-be to use polygonal approximation. I.e. approximate the boundary of each
+First a discussion of a method not used. A somewhat simple approach would
+be to use polygonal approximation, that is, approximate the boundary of each
 B\'{e}zier triangle with line segments, intersect the resulting polygons,
@@
 curve \(b(s, 0)\) would be replaced by segments connecting \(b(0, 0),
-b(1/2, 0)\) and \(b(1, 0)\), i.e. \(N + 1\) equally spaced parameters.) This
+b(1/2, 0)\) and \(b(1, 0)\), i.e., \(N + 1\) equally spaced parameters.) This
 means that in order to perform as well as an \emph{exact} quadrature used in
@@
 Quadrature rules for straight sided polygons have been
-studied (\cite{Mousavi2009}) though they are not in wide use. Even
+studied \cite{Mousavi2009} though they are not in wide use. Even
 if a polygonal quadrature rule was to be employed, a map would need to be
@@
 (Figure~\ref{fig:tessellated-curved-polygon}) and then use substitution as
-in~\eqref{eq:mass-mat-subst}. However, tessellation is challenging for both
+in~\eqref{eq:mass-mat-subst}. However, tessellating is challenging for both
 theoretical and computational reasons.
-Theoretical: it's not even clear if an arbitrary curved polygon \emph{can}
-be tessellated into B\'{e}zier triangles. Computational: the placement
+Theoretically, it's not even clear if an arbitrary curved polygon \emph{can}
+be tessellated into B\'{e}zier triangles. Computationally, the placement
 of diagonals and potential introduction of interior nodes is very
 complex in cases where the curved polygon is nonconvex. What's more,
-the curved polygon is given only by the boundary, so higher degree triangles
-(i.e. cubic and above) introduced during tessellation would need to place
+the curved polygon is given only by the boundary, so higher-degree triangles
+(i.e., cubic and above) introduced during tessellation would need to place
 interior control points without causing the triangle to invert. To get a
@@
 \end{equation}
-If the shape functions are from the pre-image basis (see
+If the shape functions are from the preimage basis (see
 Section~\ref{subsec:shape-functions}), then \(\phi_0\)
@@
 \(\partial \mathcal{P}\). By applying the theorem, inverted elements may
-be used in a tessellation, for example by introducing artificial
+be used in a tessellation, for example, by introducing artificial
 diagonals from a vertex as in Figure~\ref{fig:tessellated-curved-polygon}.
@@
 \(C\) is a B\'{e}zier curve segment, the components are also polynomials.
-If the shape functions are in the pre-image basis, then \(F\) won't in general
-be polynomial, hence standard quadrature rules can't be exact.
+If the shape functions are in the preimage basis, then \(F\) won't in general
+be polynomial; hence standard quadrature rules can't be exact.
 
@@
 points on the line \(y = \beta\) for \(x\) between \(0\) and \(\alpha\). If
-the shape functions are from the pre-image basis, it may not even be possible
+the shape functions are from the preimage basis, it may not even be possible
 to evaluate \(F\) for such points. Since \(\left[\begin{array}{c c} \alpha &
@@
 assume it is on the boundary of \(\mathcal{T}_0\). Thus, for some elements
-(e.g. if the point is on the bottom of the element), points
+(e.g., if the point is on the bottom of the element), points
 \(\left[\begin{array}{c c} \nu & \beta \end{array}\right]^T\) may not be
@@
 of \(\mathcal{T}_0\) may be impossible: even though \(b_0\) is bijective on
-\(\utri\) it may be many-to-one elsewhere hence \(b_0^{-1}\) can't be
+\(\utri\) it may be many-to-one elsewhere; hence \(b_0^{-1}\) can't be
 reliably extended outside of \(\mathcal{T}_0\).
 
-Even if the shape functions are from the global coordinates basis,
+Even when the shape functions are from the global coordinates basis,
 setting \(H(0, y) \equiv 0\) may introduce quadrature points that
 are very far from \(\mathcal{P}\). This can be somewhat addressed by using
-\(H(m, y) \equiv 0\) for a suitably chosen \(m\) (e.g. the minimum
+\(H(m, y) \equiv 0\) for a suitably chosen \(m\) (for instance, the minimum
 \(x\)-value in \(\mathcal{P}\)). Then we have
@@
   \caption{Some example meshes used during the numerical
-    experiments; the donor meshs is on the left / blue and the target
-    mesh is on the right / green. These meshes are the cubic approximations
+    experiments; the donor mesh is on the left (blue) and the target
+    mesh is on the right (green). These meshes are the cubic approximations
     of each domain and have been refined twice.}
@@
 \begin{align}
-\zeta_1(x, y) &= 5 y^3 + x^2 + 2y + 3 \\
-\zeta_2(x, y) &= \exp\left(x^2\right) + 2y \\
+\zeta_1(x, y) &= 5 y^3 + x^2 + 2y + 3, \\
+\zeta_2(x, y) &= \exp\left(x^2\right) + 2y, \\
 \zeta_3(x, y) &= \sin(x) + \cos(y).
 \end{align}
-For a given mesh size \(h\), we expect that on a degree \(p\) isoparametric
+For a given mesh size \(h\), we expect that on a degree-\(p\) isoparametric
 mesh our solution transfer will have \(\bigO{h^{p + 1}}\) errors. To measure
@@
 one might expect the solution transfer on the cubic mesh to be \emph{exact}.
-This expectation would hold in the superparametric case (i.e. where the
+This expectation would hold in the superparametric case (i.e., where the
 elements are straight sided but the shape functions are higher degree).
@@
 
-This paper has described a method for conservative interpolation
+We have described a method for conservative interpolation
 between curved meshes. The transfer process conserves globally
@@
 The algorithm breaks down into three core subproblems: B\'{e}zier triangle
-intersection, a expanding front for intersecting elements and
+intersection, an expanding front for intersecting elements and
 integration on curved polygons. The inherently local nature of the
@@
 is a symptom of the method and not of the inherent problem. The
-pre-image basis has several appealing properties, for example
+preimage basis has several appealing properties, for example,
 this basis can be precomputed on \(\utri\). The problem of a
 valid tessellation of a curved polygon warrants more exploration.
-Such a tessellation algorithm would enable usage of the pre-image
+Such a tessellation algorithm would enable usage of the preimage
 basis.
@@
 
-\bibliography{paper}
-\bibliographystyle{alpha}
-
 \appendix
@@
 the intersections will either be a curve segment common to both curves (if
-they coincide) or a finite set of points (i.e. dimension zero).
-Many algorithms have been described in the literature, both
-geometric (\cite{Sederberg1986, Sederberg1990, Kim1998}) and
-algebraic (\cite{Manocha:CSD-92-698}).
-
-In the implementation for this paper, the B\'{e}zier subdivision
+they coincide) or a finite set of points (i.e., dimension zero).
+Many algorithms, both geometric \cite{Sederberg1986, Sederberg1990, Kim1998}
+and algebraic \cite{Manocha:CSD-92-698}, have been described in the literature.
+
+In our implementation, the B\'{e}zier subdivision
 algorithm is used.
-In the case of a transversal intersection (i.e. one where the
+In the case of a transversal intersection (that is, one where the
 tangents to each curve are not parallel and both are non-zero),
@@
 convergence of Newton's method slows once in a neighborhood of an
-actual intersection. Non-transversal intersections
+actual intersection. Nontransversal intersections
 have infinite condition number, but transversal intersections with
@@
 \end{equation}
-This also gives an indication why convergence issues occur at non-transveral
+This also gives an indication why convergence issues occur at nontransversal
 intersections: they are exactly the intersections where the Jacobian is
@@
 
-In the case of tangency, the intersection is non-transversal, hence has
+In the case of tangency, the intersection is nontransversal, and hence has
 infinite condition number. In the case of coincident curves, there are
@@
 \left[ \begin{array}{c}
-    8 s \\ 8 t \end{array}\right] \qquad
+    8 s \\ 8 t \end{array}\right] \quad \text{and} \quad
 b_1(s, t) =
@@
     2 (6 s + t - 1) \\
-    2 (8 s^2 + 8 s t - 8 s + 3 t + 2) \end{array}\right]
+    2 (8 s^2 + 8 s t - 8 s + 3 t + 2) \end{array}\right].
 \end{equation}
@@
 E_2'\left(\frac{7}{9}\right) \times
-E_3'\left(\frac{1}{6}\right) = 96 \\
+E_3'\left(\frac{1}{6}\right) = 96, \\
 I_2:
@@
 E_0'\left(\frac{1}{2}\right) \times
-E_3'\left(\frac{1}{2}\right) = 0 \\
+E_3'\left(\frac{1}{2}\right) = 0, \\
   I_3:
@@
   \(E_3\) until we
-  encounter another intersection: \(I_2\)
+  encounter another intersection: \(I_2\).
 \item \(I_2\) is a point of tangency since
@@
   \(E_3\left(\left[
-    \frac{1}{6}, \frac{3}{4}\right]\right)\)
+    \frac{1}{6}, \frac{3}{4}\right]\right)\).
 \item Finding no other intersections on \(E_1\)
   we continue until the end of the edge.
-  Now our (ordered) curved segments are:
+  Now our (ordered) curved segments are
   \begin{equation}
@@
   \(E_2\), moving along that curve
-  until we hit the next intersecton \(I_1\).
-  Now our (ordered) curved segments are:
+  until we hit the next intersection \(I_1\).
+  Now our (ordered) curved segments are
   \begin{equation}
@@
   Since we are now back where we started (at \(I_1\))
-  the process stops
+  the process stops.
 \end{itemize}
 We represent the boundary of the curved polygon as B\'{e}zier curves, so
-to complete the process we reparameterize (\cite[Ch.~5.4]{Farin2001}) each
+to complete the process we reparameterize \cite[Ch.~5.4]{Farin2001} each
 curve onto the relevant interval. For example,
@@
   q_0 &= E_3\left(\frac{1}{6}\right) =
-  \frac{16}{9} \left[ \begin{array}{c} 0 \\ 1 \end{array}\right] \\
-  q_1 &= (1 - \alpha) \left[(1 - \beta) p_0 + \beta p_1\right] +
-   \alpha \left[(1 - \beta) p_1 + \beta p_2\right] = \frac{1}{6} \left[
-    \begin{array}{c} 21 \\ -8 \end{array}\right] \\
+  \frac{16}{9} \left[ \begin{array}{c} 0 \\ 1 \end{array}\right], \\
+  q_1 &= (1 - \alpha) \left((1 - \beta) p_0 + \beta p_1\right) +
+   \alpha \left((1 - \beta) p_1 + \beta p_2\right) = \frac{1}{6} \left[
+    \begin{array}{c} 21 \\ -8 \end{array}\right], \\
   q_2 &= E_3\left(\frac{3}{4}\right) = \left[
@@
 \end{equation}
-we take \(\varphi(r, 0) = b_0(r)\) hence
+we take \(\varphi(r, 0) = b_0(r)\); hence
 \begin{equation}
@@
 We also have \(ds = dr\) and \(dt = 0\) due to the
-parameterization, thus
+parameterization; thus
 \begin{equation}
@@
 
+\bibliography{paper}
+\bibliographystyle{alpha}
+
 \end{document}

### 2024-12-01 doc/paper.tex
Remove `\rev` and reflow some lines.

@@
 \newcommand{\utri}{\mathcal{U}}
-
-\newcommand{\rev}[1]{#1}
-%%% TODO: remove \rev
 
@@
 has practical applications to many methods in
-computational physics. \rev{For example, by allowing the underlying
+computational physics. For example, by allowing the underlying
 computational domain to change during a simulation, computational
@@
 requires translating the numerical solution from the old mesh to the new,
-\rev{that is, solution transfer \cite{Babuska1978,Peraire1987,Pain2001,Iske2004}}}.
+that is, solution transfer \cite{Babuska1978,Peraire1987,Pain2001,Iske2004}.
 As another example, Lagrangian or particle-based
 methods treat each node in the mesh as a particle and so with each timestep the
-\rev{mesh travels \emph{with} the fluid \cite{MR3023731}.
+mesh travels \emph{with} the fluid \cite{MR3023731}.
 However, over (typically short) time the mesh
 becomes distorted and suffers a loss in element quality which eventually causes
-inaccurate solutions.} To overcome this, the
+inaccurate solutions. To overcome this, the
 domain must be remeshed or rezoned and the solution must be
-transferred (remapped) onto the new mesh configuration. \rev{A related more general
+transferred (remapped) onto the new mesh configuration. A related more general
 class of methods is the Arbitrary Lagrangian-Eulerian (ALE) method, which
@@
 by a fixed fluid flow (the Lagrangian approach) and typically combine the benefits
-of both approaches \cite{Hirt1974,MR3302403}.}
+of both approaches \cite{Hirt1974,MR3302403}.
 
@@
 geometric flexibility and for high order of convergence, we
-address the case of curved isoparametric meshes. \rev{This is based on the
+address the case of curved isoparametric meshes. This is based on the
 recent interest in so-called high-order methods \cite{Wang2013}, which have the ability to
 produce highly accurate solutions with low dissipation and low dispersion error.
-However, these methods typically require curved meshes to obtain the high accuracy.}
+However, these methods typically require curved meshes to obtain the high accuracy.
 
@@
 and as a result much of the existing literature focuses on mesh-mesh
-pairs that will occur during an ALE-based simulation. \rev{Many ALE methods
+pairs that will occur during an ALE-based simulation. Many ALE methods
 modify the mesh during simulation: when flow-based
@@
 diagonal is switched in a pair of elements) or elements are subdivided
-or combined.} These operations are inherently local; hence the solution
+or combined. These operations are inherently local; hence the solution
 transfer can be done locally across known neighbors. Typically, this
@@
 
-\rev{In addition to conservation, there are many other considerations for a
+In addition to conservation, there are many other considerations for a
 solution transfer method that are important in various applications. For
@@
 transfer scheme include the preservation of additional constraints, such
-as the divergence or the curl of the solution.}
+as the divergence or the curl of the solution.
 
@@
 target mesh is contained in the donor mesh. This ensures that the solution
-transfer is \rev{\emph{interpolative}}. In the case where all target elements are
+transfer is \emph{interpolative}. In the case where all target elements are
 partially covered, \emph{extrapolation} could be used to extend a solution
@@
 \(\left[0, 1\right]\) when \(s\) is as well. Due to this fact, the
-curve must be contained in the convex hull of \rev{its} control points.
+curve must be contained in the convex hull of its control points.
 
@@
 diffeomorphic to \(\utri\), that is, \(b(s, t)\) is bijective and has
-an \rev{invertible Jacobian everywhere}. We must also have the orientation
+an invertible Jacobian everywhere. We must also have the orientation
 preserved, that is, the Jacobian must have positive determinant. For example, in
@@
 \(\phi_D^{(j)}\) and a known field
-\footnote{This is somewhat a simplification. \rev{In CG (continuous Galerkin, as
+\footnote{This is somewhat a simplification. In CG (continuous Galerkin, as
 opposed to DG or discontinuous Galerkin)}, some coefficients will be paired
-with multiple shape functions, such as the coefficient at a vertex node.}
+with multiple shape functions, such as the coefficient at a vertex node.
 \(\bm{q}_D = \sum_j d_j \phi_D^{(j)}\)
@@
 but that is equivalent to removing some of the basis functions which may
-\rev{in turn} make the projection non-conservative. This is because the removed
+in turn make the projection non-conservative. This is because the removed
 basis functions may have been used in \(1 = \sum_j u_j \phi_{T}^{(j)}\).
@@
 elements of the target mesh, or even across shape functions
-\(\phi_T^{(j)}\). \rev{Spatial binning techniques for mesh elements could also be
-used to improve the initial brute-force search as in \cite{Weiss16_imr}.}
+\(\phi_T^{(j)}\). Spatial binning techniques for mesh elements could also be
+used to improve the initial brute-force search as in \cite{Weiss16_imr}.
 
@@
 elements are straight sided but the shape functions are higher degree).
-However, when the elements aren't straight \rev{sided} the isoparametric mapping
+However, when the elements aren't straight sided the isoparametric mapping
 changes the underlying function space.
@@
 
-\rev{In all of our experiments, we did not encounter any of these difficulties with our implementation.
-However, for fail-safe code, additional fallback strategies would be required, and we refer the reader to the extensive literature for further details on covering all possible special cases that might occur \cite{Sederberg1986,Sederberg1990,Kim1998}.}
+In all of our experiments, we did not encounter any of these difficulties with
+our implementation. However, for fail-safe code, additional fallback strategies
+would be required, and we refer the reader to the extensive literature for
+further details on covering all possible special cases that might occur
+\cite{Sederberg1986,Sederberg1990,Kim1998}.
 

### 2025-01-09 noxfile.py
Noting where the paper was published.

@@ -56,7 +56,7 @@ def build_tex_file(session, base, new_id, extensions=()):
     path = get_path("doc", base)
     remove = Remove(path, extensions)
     session.run(remove)
-    session.run("python", modify_id, "--base", path, "--id", new_id)
+    session.run("python3", modify_id, "--base", path, "--id", new_id)
 
 
 @nox.session(py=False)
